\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage[margin=1in]{geometry}

\title{Vocabulary in \textit{Allegory of the Cave}}
\author{Compiled by AcadeMe for the Homer Project}
\date{April 2016}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle
\begin{longtable}{llp{11cm}}
\textbf{foolery} & n. &  foolish or silly behavior \\
 & & \textit{an amusing bit of foolery}\\[0.08cm]
\textbf{opine} & v. &  to express an opinion about something \\
 & & \textit{Many people opine that the content of Web pages should be better regulated.}\\[0.08cm]
\textbf{potentate} & n. &  a powerful ruler \\
 & & \textit{medieval potentates}\\[0.08cm]
\textbf{gluttony} & n. &  the act or habit of eating or drinking too much\\[0.08cm]
\textbf{accustom} & v. &  to cause (someone) to become adjusted to or familiar with something + to \\
 & & \textit{trying to gradually accustom the students to their new surroundings}\\[0.08cm]
\textbf{showman} & n. &  a person who is good at entertaining people\\[0.08cm]
\textbf{firelight} & n. &  the light produced by a fire in a fireplace, stove, etc. \\
 & & \textit{The firelight gave the room a warm glow.}\\[0.08cm]
\textbf{dazzle} & v. &  to cause (someone) to be unable to see for a short time \\
 & & \textit{He was dazzled [=blinded] by the camera flash.}\\[0.08cm]
\textbf{fetter} & v. &  to prevent (someone or something) from moving or acting freely \\
 & & \textit{He found himself fettered by responsibilities.}\\[0.08cm]
\textbf{aright} & adv. &  so as to be correct \\
 & & \textit{His name was Jones, if I remember aright. [=rightly, correctly]}\\[0.08cm]
\textbf{handmade} & adj. &  made with the hands or by using hand tools \\
 & & \textit{a handmade rug}\\[0.08cm]
\textbf{prophesy} & v. &  to state that something will happen in the future :predict \\
 & & \textit{He prophesied the government's failure. = He prophesied that the government would fail.}\\[0.08cm]
\textbf{disobey} & v. &  to not do what someone or something with authority tells you to do :to refuse or fail to obey rules, laws, etc. \\
 & & \textit{If you disobey, you will be severely punished.}\\[0.08cm]
\textbf{darken} & v. &  to make (something) dark or to become dark or darker in color \\
 & & \textit{Clouds darkened the sky.}\\[0.08cm]
\textbf{leaden} & adj. &  having a dull gray color \\
 & & \textit{a leaden sky/sea}\\[0.08cm]
\textbf{contrive} & v. &  to form or think of (a plan, method, etc.) \\
 & & \textit{The prisoners contrived a way to escape.}\\[0.08cm]
\textbf{serf} & n. &  a person in the past who belonged to a low social class and who lived and worked on land owned by another person \\
 & & \textit{medieval serfs}\\[0.08cm]
\textbf{blink} & v. &  to close and then open your eyes very quickly \\
 & & \textit{She blinked when the light flashed.}\\[0.08cm]
\textbf{engender} & v. &  to be the source or cause of (something) \\
 & & \textit{The issue has engendered a considerable amount of debate.}\\[0.08cm]
\textbf{eyesight} & n. &  the ability to see :sight or vision \\
 & & \textit{He wears glasses because his eyesight is not good.}\\[0.08cm]
\textbf{surmise} & v. &  to form an opinion about something without definitely knowing the truth :guess \\
 & & \textit{We can only surmise what happened.}\\[0.08cm]
\textbf{downright} & adv. &  to the fullest degree :completely or totally \\
 & & \textit{The movie was downright stupid/bad/scary.}\\[0.08cm]
\textbf{hive} & v. &  to separate from a group \\
 & & \textit{The youngest campers hived off into another room.}\\[0.08cm]
\textbf{thither} & adv. &  to that place :there \\
 & & \textit{traveling/wandering/running hither and thither [=here and there]}\\[0.08cm]
\textbf{nurture} & v. &  to help (something or someone) to grow, develop, or succeed \\
 & & \textit{Teachers should nurture their students' creativity.}\\[0.08cm]
\textbf{ascend} & v. &  to go up :to rise or move toward the sky \\
 & & \textit{They watched their balloons slowly ascend into the sky.}\\[0.08cm]
\textbf{landless} & adj. &  not owning any land \\
 & & \textit{landless people}\\[0.08cm]
\textbf{habitation} & n. &  the act of living in a place \\
 & & \textit{The house was not fit for human habitation.}\\[0.08cm]
\textbf{prosper} & v. &  to become very successful usually by making a lot of money \\
 & & \textit{She prospered as a real estate agent.}\\[0.08cm]
\textbf{gorge} & v. &  to eat large amounts of food usually + on \\
 & & \textit{We gorged on chips and cookies.}\\[0.08cm]
\textbf{parable} & n. &  a short story that teaches a moral or spiritual lesson \\
 & & \textit{He told the children a parable about the importance of forgiveness.}\\[0.08cm]
\textbf{brilliance} & n. &  the quality or state of being brilliant \\
 & & \textit{The professor was known for his brilliance.}\\[0.08cm]
\textbf{spoil} & v. &  to have a bad effect on (something) :to damage or ruin (something) \\
 & & \textit{The fight spoiled the party.}\\[0.08cm]
\textbf{doubly} & adv. &  much more than usual or previously :to a much higher degree than usual \\
 & & \textit{We did the test again because we wanted to be doubly [=extra, especially, very] sure the results were accurate.}\\[0.08cm]
\textbf{allegory} & n. &  a story in which the characters and events are symbols that stand for ideas about human life or for a political or historical situation \\
 & & \textit{the long poem is an allegory of/about love and jealousy}\\[0.08cm]
\textbf{bearer} & n. &  a person who bears or carries something \\
 & & \textit{the bearer of a U.S. passport}\\[0.08cm]
\textbf{toil} & v. &  to work very hard for a long time \\
 & & \textit{He's been toiling (away) in his workshop.}\\[0.08cm]
\textbf{precede} & v. &  to happen, go, or come before (something or someone) \\
 & & \textit{Riots preceded the civil war.}\\[0.08cm]
\textbf{ascent} & n. &  the act or process of ascending: such as\\
 & & \textit{Fifty years ago, he made the first successful ascent of the mountain. [=he was the first person to climb the mountain]}\\[0.08cm]
\textbf{discern} & v. &  to see, hear, or notice (something) with difficulty or effort \\
 & & \textit{We could just discern [=distinguish, make out] the ship through the fog.}\\[0.08cm]
\textbf{worthless} & adj. &  having no financial value \\
 & & \textit{worthless coins/stocks}\\[0.08cm]
\textbf{descend} & v. &  to go down :to go or move from a higher to a lower place or level \\
 & & \textit{Wait for the elevator to descend.}\\[0.08cm]
\textbf{supervise} & v. &  to be in charge of (someone or something) :to watch and direct (someone or something) \\
 & & \textit{The builder supervised the construction of the house.}\\[0.08cm]
\textbf{compulsion} & n. &  a very strong desire to do something \\
 & & \textit{I gave in to one of my compulsions and ordered the chocolate dessert.}\\[0.08cm]
\textbf{infer} & v. &  to form (an opinion) from evidence :to reach (a conclusion) based on known facts \\
 & & \textit{It's difficult to infer how these changes will affect ordinary citizens.}\\[0.08cm]
\textbf{mansion} & n. &  a large and impressive house :the large house of a wealthy person \\
 & & \textit{a mansion with 10 bedrooms and an indoor swimming pool}\\[0.08cm]
\textbf{compel} & v. &  to force (someone) to do something \\
 & & \textit{Illness compelled him to stay in bed.}\\[0.08cm]
\textbf{furious} & adj. &  very angry \\
 & & \textit{She's furious at/over how slowly the investigation is proceeding.}\\[0.08cm]
\textbf{dwell} & v. &  to live in a particular place \\
 & & \textit{a cave where bats dwell}\\[0.08cm]
\textbf{folly} & n. &  the lack of good sense or judgment :foolishness \\
 & & \textit{the folly of driving fast on steep, winding roads}\\[0.08cm]
\textbf{grim} & adj. &  unpleasant or shocking to see or think about \\
 & & \textit{Hikers made a grim discovery when they came across a dead body in the woods.}\\[0.08cm]
\textbf{faction} & n. &  a group within a larger group that has different ideas and opinions than the rest of the group \\
 & & \textit{The committee soon split into factions.}\\[0.08cm]
\textbf{envy} & v. &  to feel a desire to have what someone else has :to feel envy because of (someone or something) \\
 & & \textit{I envy you for your large group of friends.}\\[0.08cm]
\textbf{contemplation} & n. &  the act of thinking deeply about something \\
 & & \textit{He made his decision after many hours of contemplation. [=thought, consideration]}\\[0.08cm]
\textbf{strive} & v. &  to try very hard to do or achieve something \\
 & & \textit{We must all strive to do better.}\\[0.08cm]
\textbf{thence} & adv. &  from that place :from there \\
 & & \textit{Their travels took them to the Bahamas, thence south to Venezuela.}\\[0.08cm]
\end{longtable}
\end{document}
