\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage[margin=1in]{geometry}

\title{Vocabulary in \textit{Goodbye to All That}}
\author{Compiled by AcadeMe for the Homer Project}
\date{February 2016}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle
\begin{longtable}{llp{12cm}}
\textbf{mirage} & n. &  an optical effect that is sometimes seen at sea, in the desert, or over a hot pavement, that may have the appearance of a pool of water or a mirror in which distant objects are seen inverted, and that is caused by the bending or reflection of rays of light by a layer of heated air of varying density\\[0.08cm]
\textbf{minutia} & n. &  the small, precise, or trivial details of something\\
 & & \textit{the minutiae of everyday life.}\\[0.08cm]
\textbf{lambent} & adj. &  shining or glowing softly \\
 & & \textit{lambent flames}\\[0.08cm]
\textbf{tureen} & n. &  a deep bowl with a cover that is used for serving food (such as soup)\\[0.08cm]
\textbf{drench} & v. &  to make (someone or something) completely wet often + with or in \\
 & & \textit{She drenched him with a bucket of cold water.}\\[0.08cm]
\textbf{jukebox} & n. &  a machine that plays music when money is put into it\\[0.08cm]
\textbf{storefront} & n. &  the front side of a store \\
 & & \textit{The storefront [=shop front] was decorated for the holidays.}\\[0.08cm]
\textbf{toot} & v. &  to make a short, high sound with a horn or whistle \\
 & & \textit{She tooted [=honked] at me as she drove past.}\\[0.08cm]
\textbf{constrict} & v. &  to make (something) narrower, smaller, or tighter \\
 & & \textit{These shoes are too small and constrict [=squeeze] my feet.}\\[0.08cm]
\textbf{paralyze} & v. &  to make (a person or animal) unable to move or feel all or part of the body \\
 & & \textit{The snake's venom paralyzed the mouse.}\\[0.08cm]
\textbf{midtown} & n. &  the part of a city or town between its downtown and uptown \\
 & & \textit{Rents in midtown are very expensive.}\\[0.08cm]
\textbf{smuggle} & v. &  to move (someone or something) from one country into another illegally and secretly \\
 & & \textit{He was arrested for smuggling drugs into the country.}\\[0.08cm]
\textbf{canker} & n. &  something that causes bad things to happen usually singular \\
 & & \textit{Poverty is the canker of this neighborhood.}\\[0.08cm]
\textbf{memento} & n. &  something that is kept as a reminder of a person, place, or thing :souvenir \\
 & & \textit{a collection of photographs and mementos}\\[0.08cm]
\textbf{sideline} & v. &  to prevent (a player) from playing in a game especially because of injury, illness, etc. usually used as (be) sidelined \\
 & & \textit{He was sidelined with a knee injury.}\\[0.08cm]
\textbf{hangover} & n. &  a sick feeling or condition that comes after drinking too much alcohol at an earlier time \\
 & & \textit{She woke up with a hangover.}\\[0.08cm]
\textbf{nightgown} & n. &  a loose dress that is worn in bed especially by women and girls \\[0.08cm]
\textbf{uptown} & adv. &  to, toward, or in the upper part of a city or town \\
 & & \textit{We walked uptown to his apartment.}\\[0.08cm]
\textbf{nimble} & adj. &  able to move quickly, easily, and lightly \\
 & & \textit{a nimble [=agile] dancer}\\[0.08cm]
\textbf{conditioner} & n. &  a thick liquid that you put on your hair after washing it to make it softer and less dry\\[0.08cm]
\textbf{cracker} & n. &  a dry, thin baked food that is made of flour and water and is often eaten with cheese \\
 & & \textit{a plate of cheese and crackers}\\[0.08cm]
\textbf{gourmet} & n. &  a person who enjoys and knows a lot about good food and wine\\[0.08cm]
\textbf{chic} & adj. &  following the current fashion or style :fashionable and appealing \\
 & & \textit{chic clothes}\\[0.08cm]
\textbf{skyline} & n. &  the outline of buildings, mountains, etc., against the background of the sky \\
 & & \textit{the New York City skyline}\\[0.08cm]
\textbf{soothe} & v. &  to cause (someone) to be calmer, less angry, etc. \\
 & & \textit{She played music to soothe [=comfort] the baby.}\\[0.08cm]
\textbf{grate} & v. &  to cut (food) into very small pieces by rubbing it against a special tool (called a grater) \\
 & & \textit{I'll beat the eggs while you grate the cheese.}\\[0.08cm]
\textbf{monochromatic} & adj. &  having or made up of one color or shades of one color \\
 & & \textit{It's a monochromatic room with a blue rug and blue furniture.}\\[0.08cm]
\textbf{glitter} & v. &  to shine brightly :to shine with bright points of light \\
 & & \textit{The sequins on her dress glittered in the sun.}\\[0.08cm]
\textbf{grill} & v. &  to cook (food) on a metal frame over fire \\
 & & \textit{We're planning to grill some chicken and burgers at the cookout.}\\[0.08cm]
\textbf{perishable} & adj. &  likely to spoil or decay quickly :not likely to stay fresh for a long time if not eaten or used \\
 & & \textit{perishable foods}\\[0.08cm]
\textbf{shin} & v. &  shinny + up or down \\
 & & \textit{The sailor shinned up the mast.}\\[0.08cm]
\textbf{nexus} & n. &  a relationship or connection between people or things often + between or of \\
 & & \textit{the nexus between teachers and students}\\[0.08cm]
\textbf{revolve} & v. &  to turn around a center point or line :rotate \\
 & & \textit{As the gear revolves, it turns the other gears.}\\[0.08cm]
\textbf{depress} & v. &  to make (someone) feel sad :to make (someone) depressed \\
 & & \textit{The news seemed to depress him a little.}\\[0.08cm]
\textbf{irrevocable} & adj. &  not capable of being changed :impossible to revoke \\
 & & \textit{She has made an irrevocable decision.}\\[0.08cm]
\textbf{tangle} & v. &  to become or cause (something) to become twisted together \\
 & & \textit{Don't tangle the yarn.}\\[0.08cm]
\textbf{colloquial} & adj. &  used when people are speaking in an informal way \\
 & & \textit{a colloquial word/expression}\\[0.08cm]
\textbf{scarf} & v. &  to eat (something) quickly \\
 & & \textit{I scarfed [=(chiefly Brit) scoffed] a big breakfast.}\\[0.08cm]
\textbf{choke} & v. &  to become unable to breathe usually because something gets stuck in your throat or because the air is not good for breathing \\
 & & \textit{Chew your food well so you don't choke.}\\[0.08cm]
\textbf{spice} & v. &  to flavor (food) with spices \\
 & & \textit{I spiced the chicken with ginger.}\\[0.08cm]
\textbf{celery} & n. &  a vegetable that is grown for its long light green stems \\
 & & \textit{a stalk of celery}\\[0.08cm]
\textbf{cherish} & v. &  to feel or show great love for (someone or something) \\
 & & \textit{She cherishes her friends/family.}\\[0.08cm]
\textbf{advertise} & v. &  to make the public aware of something (such as a product) that is being sold \\
 & & \textit{They are advertising the new edition of the book.}\\[0.08cm]
\textbf{ephemeral} & adj. &  lasting a very short time \\
 & & \textit{His fame turned out to be ephemeral. [=short-lived]}\\[0.08cm]
\textbf{glossy} & adj. &  having a shiny, smooth surface \\
 & & \textit{a glossy magazine cover}\\[0.08cm]
\textbf{aberration} & n. &  something (such as a problem or a type of behavior) that is unusual or unexpected \\
 & & \textit{For her, such a low grade on an exam was an aberration.}\\[0.08cm]
\textbf{inconvenient} & adj. &  causing trouble or problems :not convenient \\
 & & \textit{The restaurant is in an inconvenient location.}\\[0.08cm]
\textbf{inflexible} & adj. &  not flexible: such as\\
 & & \textit{an inflexible judge}\\[0.08cm]
\textbf{mattress} & n. &  a cloth case that is filled with material and used as a bed \\[0.08cm]
\textbf{brisk} & adj. &  moving or speaking quickly :quick and efficient \\
 & & \textit{a brisk, no-nonsense manager}\\[0.08cm]
\textbf{midland} & geo. &  U.S. city, Texas\\[0.08cm]
\textbf{evasion} & n. &  the act of avoiding something that you do not want to do or deal with :the act of evading something \\
 & & \textit{He was arrested for tax/draft evasion.}\\[0.08cm]
\textbf{mundane} & adj. &  dull and ordinary \\
 & & \textit{mundane chores, like washing dishes}\\[0.08cm]
\textbf{stride} & v. &  to walk with very long steps \\
 & & \textit{She strode across the room towards me.}\\[0.08cm]
\textbf{peach} & n. &  a round, sweet fruit that has white or yellow flesh, soft yellow or pink skin, and a large, hard seed at the center \\
 & & \textit{a ripe, juicy peach}\\[0.08cm]
\textbf{gorge} & v. &  to eat large amounts of food usually + on \\
 & & \textit{We gorged on chips and cookies.}\\[0.08cm]
\textbf{perfume} & v. &  to fill or cover (something) with a pleasant smell \\
 & & \textit{Roses perfumed the air.}\\[0.08cm]
\textbf{deceptive} & adj. &  intended to make someone believe something that is not true \\
 & & \textit{The article accuses the company of deceptive [=misleading] advertising.}\\[0.08cm]
\textbf{syndicate} & n. &  a group of individuals or organizations combined to promote some common interest\\
 & & \textit{A syndicate owns the company.}\\[0.08cm]
\textbf{bleak} & adj. &  not warm, friendly, cheerful, etc. \\
 & & \textit{The weather is bleak. [=cold, rainy, dark, etc.]}\\[0.08cm]
\textbf{crab} & v. &  to catch or try to catch crabs \\
 & & \textit{We crabbed in the bay on Saturday.}\\[0.08cm]
\textbf{aversion} & n. &  a strong feeling of not liking something \\
 & & \textit{deep aversions}\\[0.08cm]
\textbf{wrap} & v. &  to cover (something) by winding or folding a piece of material around it \\
 & & \textit{They were busy wrapping presents late on Christmas Eve.}\\[0.08cm]
\textbf{retrospect} & n. &  when thinking about the past or something that happened in the past \\
 & & \textit{In retrospect, I made the right decision.}\\[0.08cm]
\textbf{miraculous} & adj. &  very wonderful or amazing like a miracle \\
 & & \textit{He made a miraculous recovery after the accident.}\\[0.08cm]
\textbf{laundry} & n. &  clothes, towels, sheets, etc., that need to be washed or that have been washed \\
 & & \textit{There's a pile of dirty laundry in the laundry basket.}\\[0.08cm]
\textbf{twilight} & n. &  the light from the sky at the end of the day when night is just beginning \\
 & & \textit{The sun set and twilight fell.}\\[0.08cm]
\textbf{monastic} & adj. &  of or relating to monks or monasteries \\
 & & \textit{a monastic community}\\[0.08cm]
\textbf{cruise} & v. &  to travel on a boat or ship to a number of places as a vacation \\
 & & \textit{We cruised for a week down the Yangtze River.}\\[0.08cm]
\textbf{garbage} & n. &  things that are no longer useful or wanted and that have been thrown out :trash \\
 & & \textit{The park was littered with garbage.}\\[0.08cm]
\textbf{drawer} & n. &  a box that slides into and out of a piece of furniture (such as a desk) and that is used to store things \\
 & & \textit{the top/middle/bottom drawer of the desk/dresser}\\[0.08cm]
\textbf{heroine} & n. &  a woman who is admired for great or brave acts or fine qualities \\
 & & \textit{The town remembered her as the heroine of the flood and erected a statue in her honor.}\\[0.08cm]
\textbf{tile} & v. &  to cover (something) with tiles \\
 & & \textit{We hired him to tile the bathroom floor.}\\[0.08cm]
\textbf{bless} & v. &  to make (something or someone) holy by saying a special prayer \\
 & & \textit{The priest blessed their marriage at the wedding.}\\[0.08cm]
\textbf{albeit} & conjunction &  even though :although \\
 & & \textit{She appeared on the show, albeit briefly.}\\[0.08cm]
\textbf{exotic} & adj. &  very different, strange, or unusual \\
 & & \textit{exotic colors/flavors}\\[0.08cm]
\textbf{notorious} & adj. &  well-known or famous especially for something bad \\
 & & \textit{The coach is notorious for his violent outbursts.}\\[0.08cm]
\textbf{indefinitely} & adv. &  for a period of time that might not end \\
 & & \textit{It's foolish to think that economic growth will continue indefinitely. [=forever]}\\[0.08cm]
\textbf{democrat} & n. &  a person who believes in or supports democracy\\
 & & \textit{a lifelong Democrat}\\[0.08cm]
\textbf{morocco} & geo. &  country in Africa\\[0.08cm]
\textbf{sentimental} & adj. &  based on, showing, or resulting from feelings or emotions rather than reason or thought \\
 & & \textit{He has a sentimental attachment to his old high school.}\\[0.08cm]
\textbf{weigh} & v. &  to find how heavy (someone or something) is :to measure the weight of (someone or something) \\
 & & \textit{She weighs herself every morning.}\\[0.08cm]
\textbf{fountain} & n. &  a device or structure that sends a stream of water into the air in a garden, park, etc. \\
 & & \textit{an elaborate marble fountain}\\[0.08cm]
\textbf{headache} & n. &  an ache or pain in the head \\
 & & \textit{I'm starting to get a headache.}\\[0.08cm]
\textbf{dissolve} & v. &  to mix with a liquid and become part of the liquid \\
 & & \textit{Sugar/salt dissolves in water.}\\[0.08cm]
\textbf{terrace} & n. &  a flat area created on the side of a hill and used especially for growing crops \\
 & & \textit{rice growing in/on hillside terraces}\\[0.08cm]
\textbf{abstraction} & n. &  the act of obtaining or removing something from a source :the act of abstracting something \\
 & & \textit{abstraction of data from hospital records}\\[0.08cm]
\textbf{progression} & n. &  the process of developing over a period of time \\
 & & \textit{Doctors were surprised by the rapid progression of the disease.}\\[0.08cm]
\textbf{incorporate} & v. &  to include (something) as part of something else \\
 & & \textit{This design incorporates the best features of our earlier models.}\\[0.08cm]
\textbf{theatrical} & adj. &  of or relating to the theater \\
 & & \textit{theatrical costumes/ambitions}\\[0.08cm]
\end{longtable}
\end{document}
