\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage[margin=1in]{geometry}

\title{Vocabulary in \textit{Illiad}}
\author{Compiled by AcadeMe for the Homer Project}
\date{May 2016}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle
\begin{longtable}{llp{11cm}}
\textbf{moor} & v. &  to hold (a boat or ship) in place with ropes or cables or with an anchor \\
 & & \textit{We found a harbor and moored the boat there for the night.}\\[0.08cm]
\textbf{surge} & v. &  to move very quickly and suddenly in a particular direction \\
 & & \textit{We all surged toward the door.}\\[0.08cm]
\textbf{ripple} & v. &  to move in small waves \\
 & & \textit{Water rippled under the dock.}\\[0.08cm]
\textbf{descend} & v. &  to go down :to go or move from a higher to a lower place or level \\
 & & \textit{Wait for the elevator to descend.}\\[0.08cm]
\textbf{jam} & v. &  to fill (a place) completely \\
 & & \textit{Thousands of people jammed the hall. = The hall was jammed [=jam-packed, packed] with thousands of people.}\\[0.08cm]
\textbf{wrap} & v. &  to cover (something) by winding or folding a piece of material around it \\
 & & \textit{They were busy wrapping presents late on Christmas Eve.}\\[0.08cm]
\textbf{heartsick} & adj. &  very sad or disappointed \\
 & & \textit{They were absolutely heartsick over/about the loss of their home.}\\[0.08cm]
\textbf{sneak} & v. &  to move quietly and secretly in order to avoid being noticed \\
 & & \textit{They tried to sneak into the movie without paying.}\\[0.08cm]
\textbf{sack} & v. &  to dismiss (someone) from a job \\
 & & \textit{They sacked [=fired] her for always being late.}\\[0.08cm]
\textbf{muster} & v. &  to work hard to find or get (courage, support, etc.) \\
 & & \textit{They pushed the car with all the strength they could muster.}\\[0.08cm]
\textbf{furl} & v. &  to wrap or roll (something, such as a sail or a flag) close to or around something \\
 & & \textit{They furled the sails.}\\[0.08cm]
\textbf{seashore} & n. &  the land along the edge of the sea that is usually covered with sand or rocks \\
 & & \textit{They built a house near the seashore.}\\[0.08cm]
\textbf{boast} & v. &  to express too much pride in yourself or in something you have, have done, or are connected to in some way \\
 & & \textit{They boasted to their friends about their son's salary.}\\[0.08cm]
\textbf{appease} & v. &  to make (someone) pleased or less angry by giving or saying something desired \\
 & & \textit{They appeased the dictator by accepting his demands in an effort to avoid war.}\\[0.08cm]
\textbf{perverse} & adj. &  wrong or different in a way that others feel is strange or offensive \\
 & & \textit{their perverse cruelty to animals}\\[0.08cm]
\textbf{afar} & adv. &  from a great distance \\
 & & \textit{Their fans come from afar [=from far away] to watch them play.}\\[0.08cm]
\textbf{destine} & v. &  to decree beforehand :predetermine\\
 & & \textit{the younger son was destined for the priesthood}\\[0.08cm]
\textbf{moan} & v. &  to make a long, low sound because of pain, unhappiness, or physical pleasure \\
 & & \textit{The wounded soldier moaned in/with pain.}\\[0.08cm]
\textbf{groan} & v. &  to make a deep sound because of pain or some strong emotion (such as grief or disappointment) \\
 & & \textit{The wounded man groaned in/with pain.}\\[0.08cm]
\textbf{rot} & v. &  to slowly decay or cause (something) to decay \\
 & & \textit{The wood had rotted away.}\\[0.08cm]
\textbf{rattle} & v. &  to hit against something repeatedly and make a quick series of short, loud sounds \\
 & & \textit{The window rattled as the truck drove by.}\\[0.08cm]
\textbf{scatter} & v. &  to cause (things or people) to separate and go in different directions \\
 & & \textit{The wind scattered the pile of leaves.}\\[0.08cm]
\textbf{cascade} & v. &  to flow or hang down in large amounts \\
 & & \textit{The water cascades over the rocks.}\\[0.08cm]
\textbf{plunder} & v. &  to steal things from (a place, such as a city or town) especially by force \\
 & & \textit{The village was plundered by the invading army.}\\[0.08cm]
\textbf{foam} & v. &  to produce foam \\
 & & \textit{The soda foamed in the glass.}\\[0.08cm]
\textbf{hulk} & n. &  the main part of something (such as a ship, car, or building) that has been ruined and is no longer used \\
 & & \textit{The ship's rusting hulk is still visible on the rocks.}\\[0.08cm]
\textbf{sacral} & adj. &  of, relating to, or lying near the \\
 & & \textit{the sacral region of the spinal cord}\\[0.08cm]
\textbf{reverberation} & n. &  a sound that echoes \\
 & & \textit{the reverberations of her voice}\\[0.08cm]
\textbf{hiss} & v. &  to produce a sound like a long sù :to make a hiss \\
 & & \textit{The radiator hissed as it let off steam.}\\[0.08cm]
\textbf{summon} & v. &  to order (someone) to come to a place \\
 & & \textit{The queen summoned him back to the palace.}\\[0.08cm]
\textbf{disembark} & v. &  to leave a ship or airplane \\
 & & \textit{The plane's crew members were the last ones to disembark.}\\[0.08cm]
\textbf{armor} & n. &  special clothing that people wear to protect their bodies from weapons \\
 & & \textit{The officers are required to wear bulletproof body armor.}\\[0.08cm]
\textbf{vow} & v. &  to make a serious promise to do something or to behave in a certain way often followed by to + verb \\
 & & \textit{The mayor vowed to reduce crime.}\\[0.08cm]
\textbf{immortal} & adj. &  not capable of dying :living forever \\
 & & \textit{the immortal soul}\\[0.08cm]
\textbf{crag} & n. &  a high and very steep area of rock on a mountain or cliff \\
 & & \textit{The goat stood on the mountain crag.}\\[0.08cm]
\textbf{assent} & v. &  to agree to or approve of something (such as an idea or suggestion) especially after carefully thinking about it \\
 & & \textit{The general proposed a detailed plan and the President assented.}\\[0.08cm]
\textbf{incalculable} & adj. &  not able to be calculated: such as\\
 & & \textit{The extent of the damage is incalculable.}\\[0.08cm]
\textbf{profiteer} & n. &  the act of making money by selling things at very high prices at a time when they are hard to get \\
 & & \textit{The company was accused of profiteering during the crisis.}\\[0.08cm]
\textbf{mull} & v. &  to think about (something) slowly and carefully :ponder \\
 & & \textit{The company is mulling the offer.}\\[0.08cm]
\textbf{beachhead} & n. &  a beach on an enemy's shore that an invading army takes and controls in order to prepare for the arrival of more soldiers and supplies often used figuratively to mean a place or position that serves as a base for future action or progress \\
 & & \textit{The company established a beachhead in New York City.}\\[0.08cm]
\textbf{atrocity} & n. &  a very cruel or terrible act or action \\
 & & \textit{the atrocities of war}\\[0.08cm]
\textbf{stronghold} & n. &  an area where most people have the same beliefs, values, etc. :an area dominated by a particular group \\
 & & \textit{The area/district/state is a Republican stronghold.}\\[0.08cm]
\textbf{spear} & v. &  to push a spear or other pointed object into (something) \\
 & & \textit{spear a fish}\\[0.08cm]
\textbf{slaughter} & v. &  to kill (an animal) for food \\
 & & \textit{slaughter cattle}\\[0.08cm]
\textbf{skewer} & v. &  to push a skewer through (food) \\
 & & \textit{skewer a marshmallow}\\[0.08cm]
\textbf{fume} & v. &  to show or feel anger \\
 & & \textit{She's still fuming about/over/at not being invited to the party.}\\[0.08cm]
\textbf{spiteful} & adj. &  having or showing a desire to harm, anger, or defeat someone :having or showing spite \\
 & & \textit{She's just being spiteful.}\\[0.08cm]
\textbf{furious} & adj. &  very angry \\
 & & \textit{She's furious at/over how slowly the investigation is proceeding.}\\[0.08cm]
\textbf{ribbon} & n. &  a narrow piece of cloth (such as silk) that is used to tie things or for decoration \\
 & & \textit{She wore pink ribbons in her hair.}\\[0.08cm]
\textbf{wince} & v. &  to have an expression on your face for a very short time which shows that you are embarrassed or in pain \\
 & & \textit{She winced [=grimaced] (in pain) when she hit her elbow.}\\[0.08cm]
\textbf{bleed} & v. &  to lose or release blood because of a cut, injury, etc. \\
 & & \textit{She was bleeding from the/her face and hands.}\\[0.08cm]
\textbf{swat} & v. &  to hit (someone or something) with a quick motion \\
 & & \textit{She swatted the fly with a magazine.}\\[0.08cm]
\textbf{strew} & v. &  to spread or scatter things over or on the ground or some other surface \\
 & & \textit{She strewed the birdseed on the ground.}\\[0.08cm]
\textbf{sling} & v. &  to throw (something) with a forceful sweeping motion \\
 & & \textit{She slung the bag over her shoulder.}\\[0.08cm]
\textbf{scrub} & v. &  to rub (something) hard with a rough object or substance and often with soap in order to clean it \\
 & & \textit{She scrubbed the potatoes.}\\[0.08cm]
\textbf{spit} & v. &  to force saliva from your mouth \\
 & & \textit{She saw him spit on the sidewalk.}\\[0.08cm]
\textbf{repress} & v. &  to not allow yourself to do or express (something) \\
 & & \textit{She repressed a laugh. [=she stopped herself from laughing]}\\[0.08cm]
\textbf{affliction} & n. &  something (such as a disease) that causes pain or suffering \\
 & & \textit{She lost her sight and is now learning to live with her/the affliction.}\\[0.08cm]
\textbf{grab} & v. &  to quickly take and hold (someone or something) with your hand or arms \\
 & & \textit{She grabbed his wrist. = She grabbed him by the wrist.}\\[0.08cm]
\textbf{unambiguous} & adj. &  clearly expressed or understood :not ambiguous \\
 & & \textit{She gave a clear, unambiguous answer.}\\[0.08cm]
\textbf{shepherd} & v. &  to guide (someone or something) \\
 & & \textit{She carefully shepherded the children across the street.}\\[0.08cm]
\textbf{sprout} & v. &  to produce new leaves, buds, etc. \\
 & & \textit{seeds sprouting in the spring}\\[0.08cm]
\textbf{slacken} & v. &  to become slower or less active :to slow down \\
 & & \textit{Sales show no sign of slackening.}\\[0.08cm]
\textbf{sacrificial} & adj. &  of, relating to, or involving sacrifice \\
 & & \textit{sacrificial rites/rituals/offerings}\\[0.08cm]
\textbf{loot} & v. &  to steal things from (a place, such as a store or house) during a war or after destruction has been caused by fire, rioting, etc. \\
 & & \textit{Rioters looted the stores.}\\[0.08cm]
\textbf{clash} & v. &  to be in a situation in which you are fighting or disagreeing :to come into conflict with someone \\
 & & \textit{Police and protesters clashed yesterday.}\\[0.08cm]
\textbf{plague} & v. &  to cause constant or repeated trouble, illness, etc., for (someone or something) \\
 & & \textit{parasites that plague deer}\\[0.08cm]
\textbf{onshore} & adj. &  moving from an ocean, lake, etc., toward land \\
 & & \textit{onshore winds}\\[0.08cm]
\textbf{greet} & v. &  to meet (someone who has just arrived) with usually friendly and polite words and actions :welcome \\
 & & \textit{My husband greeted our guests at the door.}\\[0.08cm]
\textbf{mist} & v. &  to become covered with very small drops of water usually + up \\
 & & \textit{My glasses misted [=fogged] up when I came in from the cold.}\\[0.08cm]
\textbf{murky} & adj. &  very dark or foggy \\
 & & \textit{murky skies}\\[0.08cm]
\textbf{murderous} & adj. &  very violent or deadly \\
 & & \textit{murderous machine-gun fire}\\[0.08cm]
\textbf{hades} & n. &  the home of the dead in Greek mythology\\
 & & \textit{It's hotter than hades today.}\\[0.08cm]
\textbf{unload} & v. &  to remove something (such as cargo) from a truck, ship, etc. \\
 & & \textit{It took four hours to unload the truck.}\\[0.08cm]
\textbf{douse} & v. &  to cause (a fire) to stop burning by pouring or spraying water on it :to extinguish (a fire) with water \\
 & & \textit{It took firefighters 15 minutes to douse the blaze.}\\[0.08cm]
\textbf{pry} & v. &  to try to find out about other people's private lives \\
 & & \textit{I was curious, but I didn't want to pry.}\\[0.08cm]
\textbf{swear} & v. &  to state (something) very strongly and sincerely \\
 & & \textit{I swear (that) I was there. [=I was definitely there; I am telling you the truth when I say that I was there]}\\[0.08cm]
\textbf{relish} & v. &  to enjoy or take pleasure in (something) \\
 & & \textit{I relish traveling to new places.}\\[0.08cm]
\textbf{fury} & n. &  violent anger :rage \\
 & & \textit{I could see the fury in her eyes.}\\[0.08cm]
\textbf{remorse} & n. &  a feeling of being sorry for doing something bad or wrong in the past :a feeling of guilt \\
 & & \textit{I could forgive him for what he did if he showed some remorse.}\\[0.08cm]
\textbf{tripe} & n. &  the stomach of an animal (such as a cow or ox) that is eaten as food\\
 & & \textit{How can you watch this tripe? [=rubbish]}\\[0.08cm]
\textbf{provoke} & v. &  to cause the occurrence of (a feeling or action) :to make (something) happen \\
 & & \textit{His remarks provoked both tears and laughter.}\\[0.08cm]
\textbf{tremble} & v. &  to shake slightly because you are afraid, nervous, excited, etc. \\
 & & \textit{His arms and legs began to tremble.}\\[0.08cm]
\textbf{scar} & v. &  to mark (something) with a scar \\
 & & \textit{His arm was badly scarred after the accident.}\\[0.08cm]
\textbf{dishonor} & v. &  to cause (someone or something) to lose honor :to cause (someone or something) to no longer be respected \\
 & & \textit{His actions dishonored [=brought dishonor on] the family.}\\[0.08cm]
\textbf{prophetic} & adj. &  correctly stating what will happen in the future \\
 & & \textit{Her warning proved to be prophetic. [=the thing that she warned would/could happen did happen]}\\[0.08cm]
\textbf{pledge} & v. &  to formally promise to give or do (something) \\
 & & \textit{Her family pledged \$100,000 toward the construction of a new school.}\\[0.08cm]
\textbf{arrogance} & n. &  an insulting way of thinking or behaving that comes from believing that you are better, smarter, or more important than other people \\
 & & \textit{Her arrogance has earned her a lot of enemies.}\\[0.08cm]
\textbf{hem} & v. &  to sew down a folded edge of cloth on (something) :to give (something) a hem \\
 & & \textit{hem the dress/skirt/trousers}\\[0.08cm]
\textbf{whisper} & v. &  to speak very softly or quietly \\
 & & \textit{He whispered in/into my ear.}\\[0.08cm]
\textbf{weep} & v. &  to cry because you are very sad or are feeling some other strong emotion \\
 & & \textit{He wept at the news of her death.}\\[0.08cm]
\textbf{accuse} & v. &  to blame (someone) for something wrong or illegal :to say that someone is guilty of a fault or crime \\
 & & \textit{He was unjustly accused.}\\[0.08cm]
\textbf{ransom} & v. &  to pay money in order to free (a person who has been captured or kidnapped) \\
 & & \textit{He was held captive for a week before he was ransomed and returned to his family.}\\[0.08cm]
\textbf{flay} & v. &  to beat or whip (someone or something) in a very violent and severe way usually used figuratively \\
 & & \textit{He was flayed [=severely criticized] by the media for his thoughtless comments.}\\[0.08cm]
\textbf{affront} & v. &  to do or say something that shows a lack of respect for (someone or someone's feelings) usually used as (be) affronted \\
 & & \textit{He was affronted [=insulted, offended] by her rude behavior.}\\[0.08cm]
\textbf{uphold} & v. &  to support or defend (something, such as a law) \\
 & & \textit{He took an oath to uphold the Constitution.}\\[0.08cm]
\textbf{underling} & n. &  a person of low rank who works for a more powerful person :subordinate \\
 & & \textit{He takes all the credit, but most of the hard work is done by his underlings.}\\[0.08cm]
\textbf{irreversible} & adj. &  impossible to change back to a previous condition or state \\
 & & \textit{He suffered an irreversible loss of vision.}\\[0.08cm]
\textbf{stow} & v. &  to put (something that is not being used) in a place where it is available, where it can be kept safely, etc. :store \\
 & & \textit{He stowed his gear in a locker.}\\[0.08cm]
\textbf{sprinkle} & v. &  to drop or spread small pieces or amounts of something over something \\
 & & \textit{He sprinkled water on the plants.}\\[0.08cm]
\textbf{slam} & v. &  to close (something) in a forceful way that makes a loud noise \\
 & & \textit{He slammed the door in my face.}\\[0.08cm]
\textbf{sheath} & v. &  to put (something, such as a sword) into a sheath \\
 & & \textit{He sheathed his sword.}\\[0.08cm]
\textbf{seethe} & v. &  to feel or show strong emotion (such as anger) even though you try to control it \\
 & & \textit{He seethed at his brother's success.}\\[0.08cm]
\textbf{scrap} & v. &  to get rid of (something) because it is damaged, no longer useful, etc. \\
 & & \textit{He scrapped his car after the accident.}\\[0.08cm]
\textbf{savor} & v. &  to enjoy the taste or smell of (something) for as long as possible \\
 & & \textit{He savored the aroma of the baking pies.}\\[0.08cm]
\textbf{roast} & v. &  to cook (food such as chicken, potatoes, or beef) with dry heat in an oven or over a fire \\
 & & \textit{He roasted the chicken.}\\[0.08cm]
\textbf{murmur} & v. &  to say (something) in a quiet and soft voice \\
 & & \textit{He murmured something about having to get home.}\\[0.08cm]
\textbf{propitiate} & v. &  to make (someone) pleased or less angry by giving or saying something desired :appease \\
 & & \textit{He made an offering to propitiate the angry gods.}\\[0.08cm]
\textbf{surf} & v. &  to ride on ocean waves using a special board (called a surfboard) \\
 & & \textit{He learned to surf when he was living in California.}\\[0.08cm]
\textbf{bawl} & v. &  to cry very loudly \\
 & & \textit{He lay on his bed, bawling [=sobbing, wailing] uncontrollably.}\\[0.08cm]
\textbf{knot} & v. &  to tie a section of rope, string, fabric, etc., to itself or to something else so that a knot forms :to make a knot in (something) \\
 & & \textit{He knotted his tie so that both ends would be the same length.}\\[0.08cm]
\textbf{prowess} & n. &  great ability or skill \\
 & & \textit{He is known for his prowess on the football field.}\\[0.08cm]
\textbf{filth} & n. &  a large and very unpleasant amount of dirt \\
 & & \textit{He emerged from the cellar covered in filth.}\\[0.08cm]
\textbf{plead} & v. &  to ask for something in a serious and emotional way \\
 & & \textit{He begged and pleaded, but she would not change her mind.}\\[0.08cm]
\textbf{curse} & v. &  to use offensive words when you speak \\
 & & \textit{He always starts cursing [=swearing] when he gets drunk.}\\[0.08cm]
\textbf{haul} & v. &  to pull or drag (something) with effort \\
 & & \textit{Haul the ropes in. = Haul in the ropes.}\\[0.08cm]
\textbf{charcoal} & n. &  a hard black material that is made by burning wood with a small amount of air \\
 & & \textit{hamburgers cooked over charcoal}\\[0.08cm]
\textbf{disastrous} & adj. &  causing great suffering or loss \\
 & & \textit{Half the city was destroyed by a disastrous fire.}\\[0.08cm]
\textbf{confiscate} & v. &  to take (something) away from someone especially as punishment or to enforce the law or rules \\
 & & \textit{Guards confiscated knives and other weapons from the prisoners.}\\[0.08cm]
\textbf{grind} & v. &  to crush or break (something) into very small pieces by rubbing it against a rough surface or using a special machine \\
 & & \textit{Grind (up) the coffee beans into a fine powder.}\\[0.08cm]
\textbf{flush} & v. &  to cause a strong flow of water to clean (a toilet) \\
 & & \textit{flush the toilet}\\[0.08cm]
\textbf{bulwark} & n. &  something that provides protection for or against something \\
 & & \textit{democratic principles that stand as a bulwark against tyranny}\\[0.08cm]
\textbf{decency} & n. &  polite, moral, and honest behavior and attitudes that show respect for other people \\
 & & \textit{Decency, not fear of punishment, caused them to do the right thing.}\\[0.08cm]
\textbf{ballistic} & adj. &  to become very angry \\
 & & \textit{Dad went ballistic when he saw the dent in his car.}\\[0.08cm]
\textbf{oracle} & n. &  a person (such as a priestess) through whom a god was believed to speak \\
 & & \textit{consulting an oracle}\\[0.08cm]
\textbf{scud} & v. &  to move or go quickly \\
 & & \textit{Clouds scudded across the sky.}\\[0.08cm]
\textbf{billow} & v. &  to move as a large cloud or mass \\
 & & \textit{Clouds of smoke billowed (up) from the chimney.}\\[0.08cm]
\textbf{choke} & v. &  to become unable to breathe usually because something gets stuck in your throat or because the air is not good for breathing \\
 & & \textit{Chew your food well so you don't choke.}\\[0.08cm]
\textbf{yearn} & v. &  to feel a strong desire or wish for something or to do something \\
 & & \textit{captives yearning for freedom = captives yearning to be free}\\[0.08cm]
\textbf{bloat} & n. &  too much growth \\
 & & \textit{budget/bureaucratic bloat}\\[0.08cm]
\textbf{buckle} & v. &  to fasten (something, such as a belt) with a buckle \\
 & & \textit{Buckle your seat belt.}\\[0.08cm]
\textbf{thigh} & n. &  the part of your leg that is above the knee \\
 & & \textit{boneless chicken thighs}\\[0.08cm]
\textbf{stud} & v. &  to decorate or cover (something) with many small items \\
 & & \textit{Beads stud the surface of the gown.}\\[0.08cm]
\textbf{insolent} & adj. &  rude or impolite :having or showing a lack of respect for other people \\
 & & \textit{an insolent [=impudent, disrespectful] child}\\[0.08cm]
\textbf{lure} & v. &  to cause or persuade (a person or an animal) to go somewhere or to do something by offering some pleasure or gain \\
 & & \textit{advertisers trying to lure [=attract] a younger audience to their products}\\[0.08cm]
\textbf{flicker} & v. &  to burn or glow in an unsteady way :to produce an unsteady light \\
 & & \textit{A TV was flickering in the background.}\\[0.08cm]
\textbf{loom} & v. &  to appear in a large, strange, or frightening form often in a sudden way \\
 & & \textit{A ship loomed (up) out of the fog.}\\[0.08cm]
\textbf{seagoing} & adj. &  made or used for traveling on the sea \\
 & & \textit{a seagoing [=oceangoing] ship/craft/vessel}\\[0.08cm]
\textbf{warrior} & n. &  a person who fights in battles and is known for having courage and skill \\
 & & \textit{a proud and brave warrior}\\[0.08cm]
\textbf{pitiful} & adj. &  deserving or causing feelings of pity or sympathy \\
 & & \textit{a pitiful lost dog}\\[0.08cm]
\textbf{gut} & adj. &  relating to or based on emotions :not based on logic or reason \\
 & & \textit{a gut feeling/reaction}\\[0.08cm]
\textbf{gloomy} & adj. &  somewhat dark \\
 & & \textit{a gloomy hallway}\\[0.08cm]
\textbf{doom} & v. &  to make (someone or something) certain to fail, suffer, die, etc. \\
 & & \textit{A criminal record will doom your chances of becoming a politician.}\\[0.08cm]
\textbf{arena} & n. &  a building for sports and other forms of entertainment that has a large central area surrounded by seats \\
 & & \textit{a basketball/hockey arena}\\[0.08cm]
\textbf{barren} & adj. &  having very few plants :not suitable for plants \\
 & & \textit{a barren [=desolate] landscape}\\[0.08cm]
\textbf{omen} & n. &  something that is believed to be a sign or warning of something that will happen in the future \\
 & & \textit{a bad omen}\\[0.08cm]
\end{longtable}
\end{document}
