\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage[margin=1in]{geometry}

\title{Vocabulary in \textit{Seeing What Other's Don't - Chapter II }}
\author{Compiled by AcadeMe for the Homer Project}
\date{February 2016}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle
\begin{longtable}{llp{11cm}}
\textbf{preachy} & adj. &  trying to teach something (such as proper or moral behavior) in a way that is annoying or unwanted \\
 & & \textit{We were put off by the speaker's preachy tone.}\\[0.08cm]
\textbf{unnerve} & v. &  to make (someone) feel afraid or upset and unable to think clearly \\
 & & \textit{Seeing the police in there unnerved me.}\\[0.08cm]
\textbf{firefighter} & n. &  a member of a group that works to put out fires\\[0.08cm]
\textbf{miscarry} & v. &  to have a miscarriage :to experience the early and unexpected end of a pregnancy \\
 & & \textit{She miscarried at 13 weeks. = She miscarried when she was 13 weeks pregnant.}\\[0.08cm]
\textbf{scam} & v. &  to deceive and take money from (someone) \\
 & & \textit{The company scammed hundreds of people out of their life savings.}\\[0.08cm]
\textbf{devastate} & v. &  to destroy much or most of (something) :to cause great damage or harm to (something) \\
 & & \textit{The flood devastated the town.}\\[0.08cm]
\textbf{luminary} & n. &  a very famous or successful person :celebrity \\
 & & \textit{luminaries of the art world}\\[0.08cm]
\textbf{slouch} & v. &  to walk, sit, or stand lazily with your head and shoulders bent forward \\
 & & \textit{Sit up straight. Please don't slouch.}\\[0.08cm]
\textbf{lief} & adj. &  dear beloved\\[0.08cm]
\textbf{fishy} & adj. &  of or relating to fish\\
 & & \textit{a fishy odor/taste}\\[0.08cm]
\textbf{matador} & n. &  the person who has the major part in a bullfight and who kills the bull\\[0.08cm]
\textbf{excavate} & v. &  to uncover (something) by digging away and removing the earth that covers it \\
 & & \textit{They excavated an ancient city.}\\[0.08cm]
\textbf{puzzlement} & n. &  a feeling of being confused because something is difficult to understand \\
 & & \textit{The cause of the accident has been a source of puzzlement.}\\[0.08cm]
\textbf{goad} & v. &  to urge or force (someone) to do something \\
 & & \textit{He was goaded (on) by a sense of duty.}\\[0.08cm]
\textbf{troll} & v. &  to fish with a hook and line that you pull through the water \\
 & & \textit{They were trolling the ocean floor.}\\[0.08cm]
\textbf{afflict} & v. &  to cause pain or suffering to (someone or something) \\
 & & \textit{The disease afflicts an estimated two million people every year.}\\[0.08cm]
\textbf{incubate} & v. &  to sit on eggs so that they will be kept warm and will hatch \\
 & & \textit{The female bird incubates the eggs.}\\[0.08cm]
\textbf{crick} & v. &  to develop a crick in (your neck or back) \\
 & & \textit{He cricked his back sleeping on the sofa.}\\[0.08cm]
\textbf{skew} & v. &  to change (something) so that it is not true or accurate \\
 & & \textit{They were accused of skewing the facts to fit their theory.}\\[0.08cm]
\textbf{undiscovered} & adj. &  not having been found or noticed :not discovered \\
 & & \textit{undiscovered territory}\\[0.08cm]
\textbf{snapshot} & n. &  an informal photograph that is taken quickly \\
 & & \textit{family snapshots}\\[0.08cm]
\textbf{mantel} & n. &  the shelf above a fireplace \\[0.08cm]
\textbf{swirl} & v. &  to move in circles or to cause (something) to move in circles \\
 & & \textit{She swirled the drink (around) in her glass.}\\[0.08cm]
\textbf{tern} & n. &  a kind of bird that lives near the ocean, is usually black and white, and has long wings and a tail with two points\\[0.08cm]
\textbf{hindsight} & n. &  the knowledge and understanding that you have about an event only after it has happened \\
 & & \textit{It's easy for us to say that the war was wrong, but we have the advantage/benefit of hindsight.}\\[0.08cm]
\textbf{thorny} & adj. &  having a lot of thorns \\
 & & \textit{thorny bushes}\\[0.08cm]
\textbf{brew} & v. &  to make (beer, ale, etc.) \\
 & & \textit{They brew the beer on the premises.}\\[0.08cm]
\textbf{epitome} & n. &  a perfect example :an example that represents or expresses something very well usually used in the phrase the epitome of \\
 & & \textit{Your response was the epitome of good sense.}\\[0.08cm]
\textbf{stag} & n. &  an adult male deer\\[0.08cm]
\textbf{upkeep} & n. &  the process of keeping something in good condition :the care or maintenance of buildings, equipment, etc. \\
 & & \textit{Who is responsible for the upkeep of these buildings?}\\[0.08cm]
\textbf{replicate} & v. &  to repeat or copy (something) exactly \\
 & & \textit{Scientists have failed to replicate [=duplicate] the results of his experiment.}\\[0.08cm]
\textbf{bump} & v. &  to hit (something, such as part of your body) against an object in a sudden and forceful way \\
 & & \textit{I have a bruise from where I bumped my head.}\\[0.08cm]
\textbf{haunt} & v. &  to visit or live in (a place) \\
 & & \textit{Spirits haunted the house.}\\[0.08cm]
\textbf{impasse} & n. &  a situation in which no progress seems possible \\
 & & \textit{Negotations are at an impasse. = Negotations have reached/hit an impasse.}\\[0.08cm]
\textbf{clipping} & n. &  something (such as an article or a picture) that has been cut out of a newspaper or magazine \\
 & & \textit{a newspaper/magazine clipping}\\[0.08cm]
\textbf{virulent} & adj. &  full of hate or anger \\
 & & \textit{virulent racists/racism}\\[0.08cm]
\textbf{compile} & v. &  to create (a CD, book, list, etc.) by gathering things (such as songs or pieces of writing or information) \\
 & & \textit{He compiled a book of poems.}\\[0.08cm]
\textbf{mediocre} & adj. &  not very good \\
 & & \textit{The dinner was delicious, but the dessert was mediocre.}\\[0.08cm]
\textbf{fervor} & n. &  a strong feeling of excitement and enthusiasm \\
 & & \textit{The fervor surrounding her campaign continued right through election day.}\\[0.08cm]
\textbf{amine} & n. &  any of a class of basic organic compounds derived from ammonia by replacement of hydrogen with one or more monovalent hydrocarbon radicals \\[0.08cm]
\textbf{haphazard} & adj. &  having no plan, order, or direction \\
 & & \textit{We were given a haphazard tour of the city.}\\[0.08cm]
\textbf{uncover} & v. &  to remove a cover from (something) \\
 & & \textit{Uncover the pot.}\\[0.08cm]
\textbf{implant} & v. &  to put (something) in a specified place \\
 & & \textit{The police obtained permission to implant [=plant] a recording device in the suspect's home.}\\[0.08cm]
\textbf{scribe} & v. &  to make (a shape, design, mark, etc.) in something by cutting or scratching with a sharp pointed tool \\
 & & \textit{Scribe a line along the board where you will be trimming it.}\\[0.08cm]
\textbf{unambiguous} & adj. &  clearly expressed or understood :not ambiguous \\
 & & \textit{She gave a clear, unambiguous answer.}\\[0.08cm]
\textbf{stressful} & adj. &  full of or causing stress :making you feel worried or anxious \\
 & & \textit{I had a stressful day at work today.}\\[0.08cm]
\textbf{orgasm} & n. &  the point during sexual activity when sexual pleasure is strongest \\
 & & \textit{achieve/experience/reach orgasm}\\[0.08cm]
\textbf{fruitless} & adj. &  producing no good results :not successful \\
 & & \textit{They made a fruitless attempt to find a solution.}\\[0.08cm]
\textbf{novice} & n. &  a person who has just started learning or doing something \\
 & & \textit{He's a novice in cooking.}\\[0.08cm]
\textbf{flaw} & n. &  a small physical problem (such as a crack) that makes something less valuable :defect \\
 & & \textit{There was a flaw in the vase.}\\[0.08cm]
\textbf{shadowy} & adj. &  full of shade or shadows \\
 & & \textit{a shadowy lane}\\[0.08cm]
\textbf{liberate} & v. &  to free (someone or something) from being controlled by another person, group, etc. \\
 & & \textit{Rebels fought to liberate the country.}\\[0.08cm]
\textbf{discontinuous} & adj. &  not continuous :having interruptions or gaps \\
 & & \textit{discontinuous sleep}\\[0.08cm]
\textbf{helix} & n. &  the shape formed by a line that curves around and along a central line :spiral \\[0.08cm]
\textbf{transparency} & n. &  the quality of being transparent: such as\\
 & & \textit{the transparency of a piece of glass}\\[0.08cm]
\textbf{culmination} & n. &  the end or final result of something \\
 & & \textit{This study is the culmination of years of research.}\\[0.08cm]
\textbf{diction} & n. &  the clearness of a person's speech \\
 & & \textit{The actor's diction was so poor I could hardly understand what he was saying.}\\[0.08cm]
\textbf{hop} & v. &  to move by a quick jump or series of jumps \\
 & & \textit{He hopped over the hot sand.}\\[0.08cm]
\textbf{cop} & v. &  to get (something desirable) \\
 & & \textit{I managed to cop an invitation.}\\[0.08cm]
\textbf{wooded} & adj. &  covered with trees \\
 & & \textit{a wooded lot}\\[0.08cm]
\textbf{breakthrough} & n. &  a sudden increase in knowledge, understanding, etc. :an important discovery that happens after trying for a long time to understand or explain something \\
 & & \textit{Researchers say they have made/achieved a major breakthrough in cancer treatment.}\\[0.08cm]
\textbf{fraudulent} & adj. &  done to trick someone for the purpose of getting something valuable \\
 & & \textit{Corrupt leaders were chosen in a fraudulent election.}\\[0.08cm]
\textbf{outrage} & v. &  to make (someone) very angry \\
 & & \textit{His comments outraged nearly everyone in the room.}\\[0.08cm]
\textbf{desperation} & n. &  a strong feeling of sadness, fear, and loss of hope \\
 & & \textit{She felt overcome by desperation.}\\[0.08cm]
\textbf{boost} & v. &  to increase the force, power, or amount of (something) \\
 & & \textit{The farm has boosted [=increased] wheat production by 25 percent.}\\[0.08cm]
\textbf{skepticism} & n. &  an attitude of doubting the truth of something (such as a claim or statement) \\
 & & \textit{She regarded the researcher's claims with skepticism.}\\[0.08cm]
\textbf{ominous} & adj. &  suggesting that something bad is going to happen in the future \\
 & & \textit{ominous clouds}\\[0.08cm]
\textbf{protagonist} & n. &  the main character in a novel, play, movie, etc.\\
 & & \textit{She was a leading protagonist in the civil rights movement.}\\[0.08cm]
\textbf{mechanic} & n. &  a person who repairs machines (such as car engines) and keeps them running properly \\
 & & \textit{an automotive mechanic}\\[0.08cm]
\textbf{neuron} & n. &  a cell that carries messages between the brain and other parts of the body and that is the basic unit of the nervous system :nerve cell\\[0.08cm]
\textbf{naturalistic} & adj. &  looking like what appears in nature :not looking artificial or man-made \\
 & & \textit{The zoo strives to create naturalistic settings for the animals.}\\[0.08cm]
\textbf{speculate} & v. &  to think about something and make guesses about it :to form ideas or theories about something usually when there are many things not known about it \\
 & & \textit{She could only speculate about/on her friend's motives.}\\[0.08cm]
\textbf{slum} & v. &  to spend time in places or conditions that are much worse than your usual places or conditions \\
 & & \textit{She's never been one to slum around (in cheap hotels).}\\[0.08cm]
\textbf{transcript} & n. &  a written, printed, or typed copy of words that have been spoken \\
 & & \textit{a transcript of a radio program}\\[0.08cm]
\textbf{fuse} & v. &  to join or become joined because of heat or a chemical reaction \\
 & & \textit{During the reaction the atoms fuse (together).}\\[0.08cm]
\textbf{snap} & v. &  to break quickly with a short, sharp sound \\
 & & \textit{The branch snapped and fell to the ground.}\\[0.08cm]
\textbf{fluorescent} & adj. &  producing light when electricity flows through a tube that is filled with a type of gas \\
 & & \textit{a fluorescent light/lamp}\\[0.08cm]
\textbf{inspire} & v. &  to make (someone) want to do something :to give (someone) an idea about what to do or create \\
 & & \textit{He inspired generations of future scientists.}\\[0.08cm]
\textbf{ethic} & adj. &  involving questions of right and wrong behavior :relating to ethics \\
 & & \textit{ethical [=moral] principles/standards}\\[0.08cm]
\textbf{assemble} & v. &  to collect (things) or gather (people) into one place or group \\
 & & \textit{We'll need to assemble a list of songs for the concert.}\\[0.08cm]
\textbf{cod} & abbreviation &  ash on delivery; collect on delivery used to indicate that payment must be made when something is delivered \\
 & & \textit{The merchandise was shipped C.O.D.}\\[0.08cm]
\textbf{evolve} & v. &  to change or develop slowly often into a better, more complex, or more advanced state :to develop by a process of evolution \\
 & & \textit{Some believe that birds evolved from dinosaurs. = Some believe that dinosaurs evolved into birds.}\\[0.08cm]
\textbf{compel} & v. &  to force (someone) to do something \\
 & & \textit{Illness compelled him to stay in bed.}\\[0.08cm]
\textbf{disciple} & n. &  someone who accepts and helps to spread the teachings of a famous person \\
 & & \textit{a disciple of Sigmund Freud}\\[0.08cm]
\textbf{scenario} & n. &  a description of what could possibly happen \\
 & & \textit{A possible scenario would be that we move to the city.}\\[0.08cm]
\textbf{trench} & n. &  a long, narrow hole that is dug in the ground :ditch\\
 & & \textit{a brave soldier who fought in the trenches in World War I}\\[0.08cm]
\textbf{dread} & v. &  to fear something that will or might happen \\
 & & \textit{He can't swim and dreads going in the water.}\\[0.08cm]
\textbf{grim} & adj. &  unpleasant or shocking to see or think about \\
 & & \textit{Hikers made a grim discovery when they came across a dead body in the woods.}\\[0.08cm]
\textbf{erroneous} & adj. &  not correct \\
 & & \textit{We received erroneous information.}\\[0.08cm]
\textbf{nail} & v. &  to attach (something) with a nail \\
 & & \textit{Nail the picture to the wall.}\\[0.08cm]
\textbf{scrutiny} & n. &  the act of carefully examining something especially in a critical way :the act of scrutinizing something \\
 & & \textit{the close/careful scrutiny of data}\\[0.08cm]
\textbf{trigger} & v. &  to cause (something, such as an alarm) to start functioning \\
 & & \textit{Smoke triggered the fire alarm.}\\[0.08cm]
\textbf{coincidence} & n. &  a situation in which events happen at the same time in a way that is not planned or expected \\
 & & \textit{It was mere/pure/sheer coincidence that brought them together so far from Chicago.}\\[0.08cm]
\textbf{fare} & v. &  to do something well or badly \\
 & & \textit{How did you fare [=do] on your exam?}\\[0.08cm]
\textbf{fin} & n. &  a thin flat part that sticks out from the body of a fish and is used in moving or guiding the fish through water \\
 & & \textit{a fish with blue scales and spiny fins}\\[0.08cm]
\textbf{fringe} & v. &  to decorate (something) with a fringe \\
 & & \textit{a fringed leather vest}\\[0.08cm]
\end{longtable}
\end{document}
