\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage[margin=1in]{geometry}

\title{Vocabulary in \textit{Seeing What Other's Don't - Chapter IV }}
\author{Compiled by AcadeMe for the Homer Project}
\date{February 2016}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle
\begin{longtable}{llp{11cm}}
\textbf{corrugate} & v. &  to form or shape into wrinkles or folds or into alternating ridges and grooves :furrow\\[0.08cm]
\textbf{squiggle} & n. &  a short line with many curves :a short, wavy line \\
 & & \textit{His handwriting looks like a bunch of squiggles.}\\[0.08cm]
\textbf{elate} & v. &  to make (someone) very happy and excited \\
 & & \textit{The discovery has elated researchers.}\\[0.08cm]
\textbf{ostracize} & v. &  to not allow (someone) to be included in a group :to exclude (someone) from a group \\
 & & \textit{She was ostracized from/by the scientific community for many years because of her radical political beliefs.}\\[0.08cm]
\textbf{backfield} & n. &  the area of the field that is behind the line of scrimmage \\
 & & \textit{a tackle made in the backfield}\\[0.08cm]
\textbf{attune} & v. &  to cause (a person, company, etc.) to have a better understanding of what is needed or wanted by a particular person or group usually + to \\
 & & \textit{It is important to attune the company to the needs of its customers.}\\[0.08cm]
\textbf{reschedule} & v. &  to schedule (something) for a different time or date \\
 & & \textit{She called to reschedule her appointment.}\\[0.08cm]
\textbf{blip} & n. &  a bright dot on the screen of an electronic device (such as a radar) \\
 & & \textit{The approaching ship appeared as a blip on the screen.}\\[0.08cm]
\textbf{lampoon} & v. &  to publicly criticize (someone or something) in a way that causes laughter :to mock or make fun of (someone or something) \\
 & & \textit{The politician was lampooned in cartoons.}\\[0.08cm]
\textbf{miasma} & n. &  a heavy cloud of something unpleasant or unhealthy usually singular \\
 & & \textit{A miasma of smog settled over the city.}\\[0.08cm]
\textbf{fullback} & n. &  a player on offense who lines up behind the line of scrimmage and who runs with the ball and blocks\\[0.08cm]
\textbf{quasar} & n. &  a very bright object in space that is similar to a star and that is very far away from the Earth and gives off powerful radio waves\\[0.08cm]
\textbf{antacid} & n. &  medicine that prevents or lessens the pain caused by having too much acid in your stomach\\[0.08cm]
\textbf{bronco} & n. &  a wild horse of western North America \\
 & & \textit{a rodeo featuring bucking broncos}\\[0.08cm]
\textbf{pulsar} & n. &  a type of star that gives off a rapidly repeating series of radio waves\\[0.08cm]
\textbf{corkscrew} & n. &  a tool that is used to pull corks from bottles\\[0.08cm]
\textbf{pylorus} & n. &  the muscular opening from the vertebrate stomach into the intestine\\[0.08cm]
\textbf{rafter} & n. &  one of the large, long pieces of wood that support a roof usually plural \\
 & & \textit{a room with beautiful exposed rafters}\\[0.08cm]
\textbf{cardiology} & n. &  the study of the heart and of diseases that affect the heart \\
 & & \textit{a doctor who specializes in cardiology}\\[0.08cm]
\textbf{physic} & v. &  to treat with or administer medicine to\\[0.08cm]
\textbf{touchdown} & n. &  a score that is made by carrying the ball over the opponent's goal line or by catching the ball while standing in the end zone \\
 & & \textit{He scored a touchdown.}\\[0.08cm]
\textbf{swab} & v. &  to wipe or clean (something, such as a wound) with a swab \\
 & & \textit{The nurse swabbed the cut with a disinfectant.}\\[0.08cm]
\textbf{skeptic} & n. &  a person who questions or doubts something (such as a claim or statement) \\
 & & \textit{Skeptics have pointed out flaws in the researchers' methods.}\\[0.08cm]
\textbf{gulp} & v. &  to eat or swallow (something) quickly or in large amounts \\
 & & \textit{She told him not to gulp his food.}\\[0.08cm]
\textbf{redirect} & v. &  to change the path or direction of (something) \\
 & & \textit{They dug trenches near the river to redirect the flow of the water.}\\[0.08cm]
\textbf{contaminate} & v. &  to make (something) dangerous, dirty, or impure by adding something harmful or undesirable to it \\
 & & \textit{The water was contaminated [=polluted] with chemicals.}\\[0.08cm]
\textbf{gastritis} & n. &  a painful condition in which the inside surface of the stomach becomes inflamed\\[0.08cm]
\textbf{hoax} & v. &  to trick or deceive (someone) usually used as (be) hoaxed \\
 & & \textit{People were hoaxed by the Web site.}\\[0.08cm]
\textbf{antidepressant} & n. &  a drug that is used to relieve or prevent depression in a person\\[0.08cm]
\textbf{delirious} & adj. &  not able to think or speak clearly especially because of fever or other illness \\
 & & \textit{As the child's temperature went up, he became delirious and didn't know where he was.}\\[0.08cm]
\textbf{craze} & n. &  something that is very popular for a period of time \\
 & & \textit{the latest dance/fashion/music craze}\\[0.08cm]
\textbf{coincidental} & adj. &  happening because of a coincidence :not planned \\
 & & \textit{The fact that he and his boss went to the same college was purely/entirely/completely coincidental.}\\[0.08cm]
\textbf{deflect} & v. &  to cause (something that is moving) to change direction \\
 & & \textit{armor that can deflect bullets}\\[0.08cm]
\textbf{vomit} & v. &  to have the food, liquid, etc., that is in your stomach come out through your mouth because you are sick \\
 & & \textit{I feel like I am going to vomit. [=(less formally) throw up]}\\[0.08cm]
\textbf{taint} & v. &  to hurt or damage the good condition of (something) often used as (be) tainted \\
 & & \textit{The reputation of the university has been tainted [=blemished, marred] by athletic scandals.}\\[0.08cm]
\textbf{packer} & n. &  a person or company that prepares and packages products and sends them to people or stores \\
 & & \textit{She worked as a packer for a candy company.}\\[0.08cm]
\textbf{stumble} & v. &  to hit your foot on something when you are walking or running so that you fall or almost fall :trip \\
 & & \textit{I stumbled on the uneven pavement.}\\[0.08cm]
\textbf{sufferer} & n. &  a person who has a particular illness or condition \\
 & & \textit{asthma sufferers}\\[0.08cm]
\textbf{hindsight} & n. &  the knowledge and understanding that you have about an event only after it has happened \\
 & & \textit{It's easy for us to say that the war was wrong, but we have the advantage/benefit of hindsight.}\\[0.08cm]
\textbf{peritonitis} & n. &  a serious condition in which the covering of the stomach, intestines, and nearby organs becomes swollen and infected\\[0.08cm]
\textbf{pathologist} & n. &  a doctor who specializes in pathology\\[0.08cm]
\textbf{stench} & n. &  a very bad smell :stink \\
 & & \textit{the stench of rotting meat}\\[0.08cm]
\textbf{culprit} & n. &  a person who has committed a crime or done something wrong \\
 & & \textit{The police eventually located the culprits.}\\[0.08cm]
\textbf{thwart} & v. &  to prevent (someone) from doing something or to stop (something) from happening \\
 & & \textit{She did all she could to thwart his plans.}\\[0.08cm]
\textbf{pathogen} & n. &  something (such as a type of bacteria or a virus) that causes disease \\
 & & \textit{a deadly pathogen}\\[0.08cm]
\textbf{cripple} & v. &  to cause (a person or animal) to be unable to move or walk normally usually used as (be) crippled \\
 & & \textit{Thousands of people have been crippled by the disease.}\\[0.08cm]
\textbf{roentgen} & adj. &  of or relating to X-rays \\
 & & \textit{roentgen examinations}\\[0.08cm]
\textbf{credence} & n. &  belief that something is true \\
 & & \textit{I place/put little credence in statistics. [=I generally do not believe statistics]}\\[0.08cm]
\textbf{bacterium} & n. &  any one of a group of very small living things that often cause disease usually plural \\
 & & \textit{Keep the wound clean and dry to prevent the growth of bacteria.}\\[0.08cm]
\textbf{bounce} & v. &  to cause (a ball, rock, etc.) to hit against a surface and quickly move in a different and usually opposite direction \\
 & & \textit{He was bouncing a tennis ball against/off the garage door.}\\[0.08cm]
\textbf{lull} & v. &  to cause (someone) to fall asleep or become sleepy \\
 & & \textit{The music lulled him to sleep.}\\[0.08cm]
\textbf{overrun} & v. &  to enter and be present in (a place) in large numbers \\
 & & \textit{The tank divisions overran the countryside.}\\[0.08cm]
\textbf{unsure} & adj. &  not certain about something :not sure \\
 & & \textit{He was unsure whether she had reserved a room or not.}\\[0.08cm]
\textbf{quarantine} & v. &  to keep (a person or animal) away from others to prevent a disease from spreading :to put or keep (a person or animal) in quarantine \\
 & & \textit{The hospital quarantined the infected patients.}\\[0.08cm]
\textbf{crank} & v. &  to move (something) by turning a crank usually + up or down \\
 & & \textit{Will you crank up/down [=roll up/down] the window?}\\[0.08cm]
\textbf{diagnose} & v. &  to recognize (a disease, illness, etc.) by examining someone \\
 & & \textit{The test is used to help in diagnosing heart disease.}\\[0.08cm]
\textbf{concurrence} & n. &  the state of agreeing with someone or something :agreement \\
 & & \textit{The bill was passed with the full concurrence of the Senate. [=everyone in the Senate agreed to pass the bill]}\\[0.08cm]
\textbf{specialize} & v. &  to limit your business or area of study to one specific subject \\
 & & \textit{Some carpenters do a wide range of jobs, while others specialize.}\\[0.08cm]
\textbf{microbiology} & n. &  a science that studies extremely small forms of life (such as bacteria and viruses) \\
 & & \textit{a degree in microbiology}\\[0.08cm]
\textbf{irregularity} & n. &  the quality or state of being irregular \\
 & & \textit{the irregularity of his behavior}\\[0.08cm]
\textbf{halo} & n. &  a circle of light that is shown in a religious painting, drawing, etc., around the head of a holy figure (such as an angel, saint, or god) often used figuratively \\
 & & \textit{the child's halo of golden curls}\\[0.08cm]
\textbf{infect} & v. &  to cause (someone or something) to become sick or affected by disease \\
 & & \textit{If you're sick you should stay home to avoid infecting other people in the office.}\\[0.08cm]
\textbf{grind} & v. &  to crush or break (something) into very small pieces by rubbing it against a rough surface or using a special machine \\
 & & \textit{Grind (up) the coffee beans into a fine powder.}\\[0.08cm]
\textbf{flaw} & n. &  a small physical problem (such as a crack) that makes something less valuable :defect \\
 & & \textit{There was a flaw in the vase.}\\[0.08cm]
\textbf{disrupt} & v. &  to cause (something) to be unable to continue in the normal way :to interrupt the normal progress or activity of (something) \\
 & & \textit{Protesters disrupted the conference.}\\[0.08cm]
\textbf{phantom} & adj. &  coming from or associated with the world of ghosts \\
 & & \textit{People claim to have seen a phantom ship floating on the lake.}\\[0.08cm]
\textbf{crawl} & v. &  to move on your hands and knees \\
 & & \textit{Does the baby crawl yet?}\\[0.08cm]
\textbf{atypical} & adj. &  not typical :not usual or normal \\
 & & \textit{an atypical case}\\[0.08cm]
\textbf{archive} & v. &  to collect and store materials (such as recordings, documents, or computer files) so that they can be found and used when they are needed \\
 & & \textit{The organization was devoted to cataloging and archiving printed materials on the labor movement.}\\[0.08cm]
\textbf{spurious} & adj. &  not genuine, sincere, or authentic \\
 & & \textit{spurious [=fake] gems}\\[0.08cm]
\textbf{desperation} & n. &  a strong feeling of sadness, fear, and loss of hope \\
 & & \textit{She felt overcome by desperation.}\\[0.08cm]
\textbf{oddly} & adv. &  in a strange or unusual way \\
 & & \textit{the house's oddly shaped roof}\\[0.08cm]
\textbf{broth} & n. &  liquid in which food (such as meat) has been cooked \\
 & & \textit{chicken broth}\\[0.08cm]
\textbf{mosquito} & n. &  a small flying insect that bites the skin of people and animals and sucks their blood \\
 & & \textit{a swarm of mosquitoes}\\[0.08cm]
\textbf{discard} & v. &  to throw (something) away because it is useless or unwanted \\
 & & \textit{Remove and discard the stems.}\\[0.08cm]
\textbf{bust} & v. &  to break (something): such as\\
 & & \textit{He busted his watch when he fell.}\\[0.08cm]
\textbf{forge} & v. &  to form something by heating and shaping metal \\
 & & \textit{forging hooks out of pieces of iron = forging pieces of iron into hooks}\\[0.08cm]
\textbf{technician} & n. &  a person whose job relates to the practical use of machines or science in industry, medicine, etc. \\
 & & \textit{medical/X-ray/laboratory technicians}\\[0.08cm]
\textbf{leak} & v. &  to let something (such as a liquid or gas) in or out through a hole in a surface \\
 & & \textit{The roof was leaking. [=rainwater was getting into the building through the roof]}\\[0.08cm]
\textbf{speculate} & v. &  to think about something and make guesses about it :to form ideas or theories about something usually when there are many things not known about it \\
 & & \textit{She could only speculate about/on her friend's motives.}\\[0.08cm]
\textbf{impurity} & n. &  the quality or state of being impure \\
 & & \textit{the impurity of the water}\\[0.08cm]
\textbf{ridicule} & v. &  to laugh at and make jokes about (someone or something) in a cruel or harsh way :to make fun of (someone or something) \\
 & & \textit{The other kids ridiculed him for the way he dressed.}\\[0.08cm]
\textbf{barium} & n. &  a chemical element that is a soft silver-white metal\\[0.08cm]
\textbf{irresistible} & adj. &  impossible to resist especially because of strength or attractiveness \\
 & & \textit{The force of the waves was irresistible.}\\[0.08cm]
\textbf{anomaly} & n. &  something that is unusual or unexpected :something anomalous \\
 & & \textit{A storm like that is an anomaly for this area. [=a storm like that does not usually happen in this area]}\\[0.08cm]
\textbf{provoke} & v. &  to cause the occurrence of (a feeling or action) :to make (something) happen \\
 & & \textit{His remarks provoked both tears and laughter.}\\[0.08cm]
\textbf{observatory} & n. &  a special building for studying stars, planets, weather, etc. :a building from which scientists study and watch the sky \\
 & & \textit{the McDonald Observatory}\\[0.08cm]
\textbf{bizarre} & adj. &  very unusual or strange \\
 & & \textit{His behavior was bizarre.}\\[0.08cm]
\textbf{deprive} & v. &  to take something away from someone or something :to not allow (someone or something) to have or keep (something) \\
 & & \textit{The change in her status deprived her of access to classified information.}\\[0.08cm]
\textbf{tackle} & v. &  to forcefully seize (someone) and cause that person to fall to the ground \\
 & & \textit{The police officer tackled him as he tried to escape.}\\[0.08cm]
\textbf{nausea} & n. &  the feeling you have in your stomach when you think you are going to vomit \\
 & & \textit{Some people experience nausea when flying.}\\[0.08cm]
\textbf{inspect} & v. &  to look at (something) carefully in order to learn more about it, to find problems, etc. \\
 & & \textit{The border guard inspected [=examined] their passports.}\\[0.08cm]
\textbf{antibiotic} & n. &  a drug that is used to kill harmful bacteria and to cure infections\\[0.08cm]
\textbf{cod} & abbreviation &  ash on delivery; collect on delivery used to indicate that payment must be made when something is delivered \\
 & & \textit{The merchandise was shipped C.O.D.}\\[0.08cm]
\textbf{evolve} & v. &  to change or develop slowly often into a better, more complex, or more advanced state :to develop by a process of evolution \\
 & & \textit{Some believe that birds evolved from dinosaurs. = Some believe that dinosaurs evolved into birds.}\\[0.08cm]
\textbf{maiden} & adj. &  not married \\
 & & \textit{my maiden aunt}\\[0.08cm]
\textbf{infer} & v. &  to form (an opinion) from evidence :to reach (a conclusion) based on known facts \\
 & & \textit{It's difficult to infer how these changes will affect ordinary citizens.}\\[0.08cm]
\textbf{arouse} & v. &  to cause (an emotional or mental state) \\
 & & \textit{He tried to sneak past without arousing suspicion. [=without causing people to become suspicious]}\\[0.08cm]
\textbf{ulcer} & n. &  a painful, sore area inside or outside the body \\
 & & \textit{a stomach ulcer}\\[0.08cm]
\textbf{diode} & n. &  an electronic device that allows an electric current to flow in one direction only\\[0.08cm]
\textbf{ultraviolet} & adj. &  sed to describe rays of light that cannot be seen and that are slightly shorter than the rays of violet light \\
 & & \textit{ultraviolet light/radiation}\\[0.08cm]
\textbf{articulate} & adj. &  able to express ideas clearly and effectively in speech or writing \\
 & & \textit{She's an intelligent and articulate speaker.}\\[0.08cm]
\textbf{surveillance} & n. &  the act of carefully watching someone or something especially in order to prevent or detect a crime \\
 & & \textit{government surveillance of suspected terrorists}\\[0.08cm]
\textbf{gut} & adj. &  relating to or based on emotions :not based on logic or reason \\
 & & \textit{a gut feeling/reaction}\\[0.08cm]
\textbf{consume} & v. &  to eat or drink (something) \\
 & & \textit{The dogs consume [=eat] a bag of dog food each week.}\\[0.08cm]
\textbf{conclusive} & adj. &  showing that something is certainly true \\
 & & \textit{conclusive evidence/proof}\\[0.08cm]
\textbf{dismiss} & v. &  to decide not to think about or consider (something or someone) \\
 & & \textit{We dismissed his accusations.}\\[0.08cm]
\textbf{furious} & adj. &  very angry \\
 & & \textit{She's furious at/over how slowly the investigation is proceeding.}\\[0.08cm]
\textbf{nova} & n. &  a star that suddenly increases greatly in brightness and then within a few months or years becomes less bright again \\[0.08cm]
\textbf{penicillin} & n. &  a medicine that is used to kill harmful bacteria\\[0.08cm]
\textbf{knock} & v. &  to hit something (such as a door) with the knuckles of your hand or with a hard object (such as a knocker) in order to get people's attention \\
 & & \textit{I heard someone knocking (at the door).}\\[0.08cm]
\textbf{infrared} & adj. &  producing or using rays of light that cannot be seen and that are longer than rays that produce red light \\
 & & \textit{infrared radiation/beams}\\[0.08cm]
\textbf{omission} & n. &  something that has not been included or done :something that has been omitted \\
 & & \textit{There are a few omissions in the list/book.}\\[0.08cm]
\textbf{spark} & v. &  to cause (something) to start or happen \\
 & & \textit{The question sparked a debate.}\\[0.08cm]
\textbf{transmit} & v. &  to send (information, sound, etc.) in the form of electrical signals to a radio, television, computer, etc. \\
 & & \textit{The technology allows data to be transmitted by cellular phones.}\\[0.08cm]
\textbf{trigger} & v. &  to cause (something, such as an alarm) to start functioning \\
 & & \textit{Smoke triggered the fire alarm.}\\[0.08cm]
\textbf{recorder} & n. &  a device that records sounds or images or both so that they can be heard or seen again \\
 & & \textit{She works as the clerk and recorder at the county courthouse.}\\[0.08cm]
\textbf{coincidence} & n. &  a situation in which events happen at the same time in a way that is not planned or expected \\
 & & \textit{It was mere/pure/sheer coincidence that brought them together so far from Chicago.}\\[0.08cm]
\textbf{transistor} & n. &  a small device that is used to control the flow of electricity in radios, computers, etc.\\[0.08cm]
\textbf{intestine} & n. &  a long tube in the body that helps digest food after it leaves the stomach \\[0.08cm]
\textbf{mold} & v. &  to form or press (something, such as wax, plastic, clay, or dough) into a particular shape \\
 & & \textit{mold dough into loaves of bread}\\[0.08cm]
\textbf{appetite} & n. &  a physical desire for food \\
 & & \textit{He has a healthy/good/hearty appetite.}\\[0.08cm]
\textbf{expose} & v. &  to leave (something) without covering or protection \\
 & & \textit{The shingles had fallen off, exposing the wood underneath.}\\[0.08cm]
\textbf{digest} & v. &  to change (food that you have eaten) by a biological process into simpler forms that can be used by the body \\
 & & \textit{He has trouble digesting certain foods.}\\[0.08cm]
\textbf{inverse} & adj. &  sed to describe two things that are related in such a way that as one becomes larger the other becomes smaller \\
 & & \textit{The study indicates an inverse relationship between the unemployment rate and inflation. [=as the unemployment rate drops, inflation rises]}\\[0.08cm]
\textbf{spiral} & v. &  to move in a circle around a central point while getting closer to or farther away from it :to move in a spiral \\
 & & \textit{Smoke spiraled up from the chimney.}\\[0.08cm]
\end{longtable}
\end{document}
