\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage[margin=1in]{geometry}

\title{Vocabulary in \textit{Seeing What Other's Don't - Chapter III }}
\author{Compiled by AcadeMe for the Homer Project}
\date{February 2016}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle
\begin{longtable}{llp{11cm}}
\textbf{reverend} & adj. &  sed as a title for a priest or minister in the Christian church \\
 & & \textit{We welcome Reverend John Smith as our guest.}\\[0.08cm]
\textbf{squadron} & n. &  a military unit consisting of soldiers, ships, or aircraft \\
 & & \textit{a bomber/reconnaissance squadron}\\[0.08cm]
\textbf{fossil} & n. &  something (such as a leaf, skeleton, or footprint) that is from a plant or animal which lived in ancient times and that you can see in some rocks \\
 & & \textit{a dinosaur fossil}\\[0.08cm]
\textbf{fin} & n. &  a thin flat part that sticks out from the body of a fish and is used in moving or guiding the fish through water \\
 & & \textit{a fish with blue scales and spiny fins}\\[0.08cm]
\textbf{formulate} & v. &  to create, invent, or produce (something) by careful thought and effort \\
 & & \textit{A long-range plan is being formulated. [=devised]}\\[0.08cm]
\textbf{paradigm} & n. &  a model or pattern for something that may be copied \\
 & & \textit{Her recent book provides us with a new paradigm for modern biography.}\\[0.08cm]
\textbf{cliff} & n. &  a high, steep surface of rock, earth, or ice \\
 & & \textit{Standing at the edge of the cliff, we watched the waves crash on the shore far below.}\\[0.08cm]
\textbf{coincidence} & n. &  a situation in which events happen at the same time in a way that is not planned or expected \\
 & & \textit{It was mere/pure/sheer coincidence that brought them together so far from Chicago.}\\[0.08cm]
\textbf{glow} & v. &  to shine with low light and heat but usually without flame \\
 & & \textit{The coals glowed in the fireplace.}\\[0.08cm]
\textbf{memo} & n. &  a usually brief written message from one person or department in an organization, company, etc., to another :memorandum \\
 & & \textit{He sent a memo to the staff.}\\[0.08cm]
\textbf{stark} & adj. &  having a very plain and often cold or empty appearance \\
 & & \textit{a stark white room}\\[0.08cm]
\textbf{contend} & v. &  to argue or state (something) in a strong and definite way \\
 & & \textit{These people contend that they have earned the right to the land.}\\[0.08cm]
\textbf{secrecy} & n. &  the act of keeping information secret \\
 & & \textit{She swore him to secrecy. [=made him promise to keep a secret]}\\[0.08cm]
\textbf{specialty} & n. &  something that a person or place is known for making or producing very well \\
 & & \textit{Eggs are my dad's specialty. [=(Brit) speciality]}\\[0.08cm]
\textbf{devise} & v. &  to invent or plan (something that is difficult or complicated) \\
 & & \textit{They have devised a new method for converting sunlight into electricity.}\\[0.08cm]
\textbf{cultivate} & v. &  to prepare and use (soil) for growing plants \\
 & & \textit{Prehistoric peoples settled the area and began to cultivate the land.}\\[0.08cm]
\textbf{blunt} & adj. &  having a thick edge or point :not sharp \\
 & & \textit{scissors with blunt [=rounded] ends}\\[0.08cm]
\textbf{bin} & v. &  to put (something) in the trash \\
 & & \textit{binning old newspapers}\\[0.08cm]
\textbf{lace} & v. &  to pull a lace through the holes of (a shoe, boot, etc.) \\
 & & \textit{She was lacing (up) her shoes.}\\[0.08cm]
\textbf{heel} & v. &  sed as a command to tell a dog to walk next to you \\
 & & \textit{Heel! Good dog.}\\[0.08cm]
\textbf{disgust} & v. &  to cause (someone) to have a strong feeling of dislike for something especially because it has a very unpleasant appearance, taste, smell, etc. \\
 & & \textit{The greasy food they were serving disgusted [=repulsed] him.}\\[0.08cm]
\textbf{cod} & abbreviation &  ash on delivery; collect on delivery used to indicate that payment must be made when something is delivered \\
 & & \textit{The merchandise was shipped C.O.D.}\\[0.08cm]
\textbf{dictate} & v. &  to speak or read (something) to a person who writes it down or to a machine that records it \\
 & & \textit{She's dictating a letter to her secretary.}\\[0.08cm]
\textbf{reconnaissance} & n. &  military activity in which soldiers, airplanes, etc., are sent to find out information about an enemy \\
 & & \textit{There are two helicopters available for reconnaissance.}\\[0.08cm]
\textbf{fuse} & v. &  to join or become joined because of heat or a chemical reaction \\
 & & \textit{During the reaction the atoms fuse (together).}\\[0.08cm]
\textbf{extinct} & adj. &  no longer existing \\
 & & \textit{an extinct (species of) animal}\\[0.08cm]
\textbf{wreck} & v. &  to damage (something) so badly that it cannot be repaired \\
 & & \textit{I wrecked my mother's car.}\\[0.08cm]
\textbf{convoy} & v. &  to travel with and protect (someone or something) \\
 & & \textit{The tankers were convoyed by warships.}\\[0.08cm]
\textbf{dive} & v. &  to jump into water with your arms and head going in first \\
 & & \textit{She dove into the swimming pool.}\\[0.08cm]
\textbf{leak} & v. &  to let something (such as a liquid or gas) in or out through a hole in a surface \\
 & & \textit{The roof was leaking. [=rainwater was getting into the building through the roof]}\\[0.08cm]
\textbf{trajectory} & n. &  the curved path along which something (such as a rocket) moves through the air or through space \\
 & & \textit{the trajectory of the missile}\\[0.08cm]
\textbf{heed} & v. &  to pay attention to (advice, a warning, etc.) \\
 & & \textit{She failed to heed the warnings.}\\[0.08cm]
\textbf{botany} & n. &  a branch of science that deals with plant life \\
 & & \textit{She's studying botany.}\\[0.08cm]
\textbf{bomber} & n. &  a military aircraft designed for dropping bombs \\
 & & \textit{a bomber pilot}\\[0.08cm]
\textbf{desperation} & n. &  a strong feeling of sadness, fear, and loss of hope \\
 & & \textit{She felt overcome by desperation.}\\[0.08cm]
\textbf{analogue} & n. &  something that is similar to something else in design, origin, use, etc. :something that is analogous to something else \\
 & & \textit{a modern analog to what happened before}\\[0.08cm]
\textbf{vintage} & adj. &  sed to describe a wine usually of high quality that was produced in a particular year which is identified on the bottle \\
 & & \textit{The restaurant has a fine selection of vintage wines.}\\[0.08cm]
\textbf{descendant} & n. &  someone who is related to a person or group of people who lived in the past \\
 & & \textit{One of the famous inventor's descendants is also an inventor.}\\[0.08cm]
\textbf{beetle} & v. &  to move quickly \\
 & & \textit{Everyone looked very busy, beetling [=scurrying] about the office.}\\[0.08cm]
\textbf{toss} & v. &  to throw (something) with a quick, light motion \\
 & & \textit{I tossed the ball to him. = I tossed him the ball.}\\[0.08cm]
\textbf{torpedo} & v. &  to hit or sink (a ship) with a torpedo \\
 & & \textit{The submarine torpedoed the battleship.}\\[0.08cm]
\textbf{archipelago} & n. &  an expanse of water with many scattered islands\\
 & & \textit{an archipelago of small parks within the city}\\[0.08cm]
\textbf{cruiser} & n. &  police car\\[0.08cm]
\textbf{distraction} & n. &  something that makes it difficult to think or pay attention \\
 & & \textit{It was hard to work with so many distractions.}\\[0.08cm]
\textbf{dessert} & n. &  sweet food eaten after the main part of a meal \\
 & & \textit{She doesn't care for rich desserts.}\\[0.08cm]
\textbf{parson} & n. &  a minister who is in charge of a parish\\[0.08cm]
\textbf{ping} & v. &  to make the high, sharp sound of a small, hard object bouncing off metal or glass \\
 & & \textit{The engine in my car keeps pinging. [=(Brit) pinking]}\\[0.08cm]
\textbf{fateful} & adj. &  having important results \\
 & & \textit{She made the fateful [=momentous] decision to go back home to face her mother.}\\[0.08cm]
\textbf{specie} & n. &  money in coin\\[0.08cm]
\textbf{nominate} & v. &  to formally choose (someone) as a candidate for a job, position, office, etc. \\
 & & \textit{We expect the party to nominate him for president.}\\[0.08cm]
\textbf{mammal} & n. &  a type of animal that feeds milk to its young and that usually has hair or fur covering most of its skin \\
 & & \textit{Human beings, dogs, and cats are all mammals.}\\[0.08cm]
\textbf{fluent} & adj. &  able to speak a language easily and very well \\
 & & \textit{a fluent speaker}\\[0.08cm]
\textbf{pineapple} & n. &  a large fruit that grows on a tropical tree and that has thick skin and very sweet, juicy, yellow flesh \\
 & & \textit{a can of chopped pineapple}\\[0.08cm]
\textbf{coloration} & n. &  the color or patterns of color on an animal or plant \\
 & & \textit{the bird's brilliant coloration [=coloring]}\\[0.08cm]
\textbf{flop} & v. &  to fall, lie, or sit down in a sudden, awkward, or relaxed way \\
 & & \textit{He flopped down onto the bed.}\\[0.08cm]
\textbf{refine} & v. &  to remove the unwanted substances in (something) \\
 & & \textit{refine oil/sugar}\\[0.08cm]
\textbf{distract} & v. &  to cause (someone) to stop thinking about or paying attention to someone or something and to think about or pay attention to someone or something else instead \\
 & & \textit{You sneak into his room while I distract him.}\\[0.08cm]
\textbf{firsthand} & adj. &  coming directly from actually experiencing or seeing something \\
 & & \textit{He gave a firsthand account of the battle.}\\[0.08cm]
\textbf{hoard} & v. &  to collect and hide a large amount of (something valuable) \\
 & & \textit{hoarding money/food}\\[0.08cm]
\textbf{fieldwork} & n. &  the work of gathering information by going into the field (sense 4) \\
 & & \textit{an anthropologist who has done fieldwork in the South Pacific}\\[0.08cm]
\textbf{battleship} & n. &  a large ship that has many big guns and is used in fighting wars\\[0.08cm]
\textbf{cripple} & v. &  to cause (a person or animal) to be unable to move or walk normally usually used as (be) crippled \\
 & & \textit{Thousands of people have been crippled by the disease.}\\[0.08cm]
\textbf{rapture} & n. &  a state or feeling of great happiness, pleasure, or love \\
 & & \textit{We listened with rapture as the orchestra played.}\\[0.08cm]
\textbf{mislead} & v. &  to cause (someone) to believe something that is not true \\
 & & \textit{We believe that her comments were deliberately meant to mislead the public.}\\[0.08cm]
\textbf{anvil} & n. &  a heavy iron block on which heated metal is shaped by hitting it with a hammer\\[0.08cm]
\textbf{rout} & v. &  to defeat (someone) easily and completely in a game or contest \\
 & & \textit{The reigning champion routed the contender.}\\[0.08cm]
\textbf{deploy} & v. &  to organize and send out (people or things) to be used for a particular purpose \\
 & & \textit{The troops were deployed for battle.}\\[0.08cm]
\textbf{warship} & n. &  a military ship that has many weapons and is used for fighting in wars\\[0.08cm]
\textbf{deflect} & v. &  to cause (something that is moving) to change direction \\
 & & \textit{armor that can deflect bullets}\\[0.08cm]
\textbf{posse} & n. &  a group of people who were gathered together by a sheriff in the past to help search for a criminal \\
 & & \textit{The sheriff and his posse rode out to look for the bandits.}\\[0.08cm]
\textbf{goldfish} & n. &  a small usually orange fish that people often keep in ponds or in fishbowls or tanks as a pet\\[0.08cm]
\textbf{prim} & adj. &  very formal and proper \\
 & & \textit{a prim manner}\\[0.08cm]
\textbf{cracker} & n. &  a dry, thin baked food that is made of flour and water and is often eaten with cheese \\
 & & \textit{a plate of cheese and crackers}\\[0.08cm]
\textbf{beagle} & n. &  a type of small dog used for hunting that has smooth black, brown, and white fur \\[0.08cm]
\textbf{presto} & interj. &  suddenly as if by magic \\
 & & \textit{A wave of the hand and, presto [=(Brit) hey presto], it's gone.}\\[0.08cm]
\textbf{swordfish} & n. &  a very large fish that lives in the ocean, that has a long, pointed upper jaw which looks like a sword, and that is eaten as food\\[0.08cm]
\textbf{unformed} & adj. &  not fully or completely developed \\
 & & \textit{an unformed thought/idea}\\[0.08cm]
\textbf{knockout} & adj. &  causing someone to become unconscious \\
 & & \textit{a knockout punch/blow}\\[0.08cm]
\textbf{outlast} & v. &  to last longer than (someone or something) :to continue to exist, be active, etc., longer than (someone or something) \\
 & & \textit{We watched him outlast his opponent in one of the greatest boxing matches of all time.}\\[0.08cm]
\textbf{kirsch} & n. &  a dry colorless brandy distilled from the fermented juice of the black morello cherry\\[0.08cm]
\textbf{eventuate} & v. &  to come out finally :result come about\\[0.08cm]
\textbf{mockingbird} & n. &  a North American bird that sings loudly and copies the songs of other birds \\[0.08cm]
\textbf{devastate} & v. &  to destroy much or most of (something) :to cause great damage or harm to (something) \\
 & & \textit{The flood devastated the town.}\\[0.08cm]
\textbf{fixate} & v. &  to look at or think about something constantly :to give all of your attention to something usually + on or upon \\
 & & \textit{Why do journalists fixate on scandals?}\\[0.08cm]
\textbf{galvanize} & v. &  to cause (people) to become so excited or concerned about an issue, idea, etc., that they want to do something about it \\
 & & \textit{an issue that galvanized the public (to take action)}\\[0.08cm]
\textbf{seashell} & n. &  the hard, empty shell of a small sea creature (such as a clam) \\
 & & \textit{She collects seashells.}\\[0.08cm]
\textbf{trivialize} & v. &  to make (something) seem less important or serious than it actually is \\
 & & \textit{The news story trivialized the problem.}\\[0.08cm]
\textbf{nosedive} & n. &  a sudden sharp drop made by an airplane with its front end pointing toward the ground \\
 & & \textit{The plane went into a nosedive.}\\[0.08cm]
\textbf{yucky} & adj. &  causing discomfort, disgust, or a strong feeling of dislike :unpleasant and disgusting \\
 & & \textit{The water was dirty and smelled yucky.}\\[0.08cm]
\end{longtable}
\end{document}
