\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage[margin=1in]{geometry}

\title{Vocabulary in \textit{Melian Dialogue}}
\author{Compiled by AcadeMe for the Homer Project}
\date{March 2016}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle
\begin{longtable}{llp{11cm}}
\textbf{encamp} & v. &  to set up and use a camp \\
 & & \textit{Napoleon's troops encamped there.}\\[0.08cm]
\textbf{embitter} & v. &  to cause bitter feelings in (someone) \\
 & & \textit{The soldier was embittered by the war.}\\[0.08cm]
\textbf{weakling} & n. &  a weak person \\
 & & \textit{a 90-pound weakling}\\[0.08cm]
\textbf{venturesome} & adj. &  willing to take risks :daring \\
 & & \textit{a venturesome sea captain}\\[0.08cm]
\textbf{islander} & n. &  a person born or living on an island \\
 & & \textit{Pacific islanders}\\[0.08cm]
\textbf{comforter} & n. &  someone who helps you to feel less worried, upset, frightened, etc. :someone who comforts you \\
 & & \textit{He was her longtime confidant and comforter.}\\[0.08cm]
\textbf{discus} & n. &  a heavy disk (as of wood or plastic) that is thicker in the center than at the perimeter and that is hurled for distance as a track-and-field event\\[0.08cm]
\textbf{incontrovertible} & adj. &  not able to be doubted or questioned :indisputable \\
 & & \textit{incontrovertible evidence/proof}\\[0.08cm]
\textbf{despondent} & adj. &  very sad and without hope \\
 & & \textit{I had never seen them looking so despondent.}\\[0.08cm]
\textbf{spar} & v. &  to box with someone as a form of training or practice \\
 & & \textit{He's been sparring with his trainer.}\\[0.08cm]
\textbf{enumerate} & v. &  to name (things) one after another in a list \\
 & & \textit{Let me enumerate my reasons for doing this.}\\[0.08cm]
\textbf{kinsman} & n. &  a male relative \\
 & & \textit{honoring a dead kinsman}\\[0.08cm]
\textbf{unconnected} & adj. &  not related or connected \\
 & & \textit{The question is completely unconnected with/to the discussion.}\\[0.08cm]
\textbf{irrevocable} & adj. &  not capable of being changed :impossible to revoke \\
 & & \textit{She has made an irrevocable decision.}\\[0.08cm]
\textbf{adversity} & n. &  a difficult situation or condition :misfortune or tragedy \\
 & & \textit{He showed courage in the face of adversity.}\\[0.08cm]
\textbf{spartan} & adj. &  very bare and simple :lacking the things that make life comfortable or more pleasant \\
 & & \textit{They lived in spartan conditions.}\\[0.08cm]
\textbf{seduction} & n. &  the act of persuading someone to have sex with you \\
 & & \textit{The book describes his seductions of young women.}\\[0.08cm]
\textbf{congratulate} & v. &  to tell (someone) that you are happy because of his or her success or good luck \\
 & & \textit{congratulate the winner}\\[0.08cm]
\textbf{relinquish} & v. &  to give up (something) :to give (something, such as power, control, or possession) to another person or group \\
 & & \textit{I will not relinquish my rights.}\\[0.08cm]
\textbf{astray} & adv. &  off the right path or route usually used with go \\
 & & \textit{They marked the trail so hikers wouldn't go astray. [=become lost]}\\[0.08cm]
\textbf{endanger} & v. &  to cause (someone or something) to be in a dangerous place or situation \\
 & & \textit{Parents feared that the dog could endanger their children.}\\[0.08cm]
\textbf{recur} & v. &  to happen or appear again :to occur again \\
 & & \textit{There is only a slight chance that the disease will recur.}\\[0.08cm]
\textbf{preponderance} & n. &  a greater amount or number of something \\
 & & \textit{A preponderance of the evidence [=most of the evidence] shows that the accused is guilty.}\\[0.08cm]
\textbf{treachery} & n. &  harmful things that are done usually secretly to a friend, your own country, etc. \\
 & & \textit{a tale of treachery and revenge}\\[0.08cm]
\textbf{hop} & v. &  to move by a quick jump or series of jumps \\
 & & \textit{He hopped over the hot sand.}\\[0.08cm]
\textbf{coward} & n. &  someone who is too afraid to do what is right or expected :someone who is not at all brave or courageous \\
 & & \textit{a proven coward who had deserted his troops}\\[0.08cm]
\textbf{precaution} & n. &  something that is done to prevent possible harm or trouble from happening in the future \\
 & & \textit{Be sure to follow the usual safety precautions when cooking outdoors.}\\[0.08cm]
\textbf{scanty} & adj. &  very small in size or amount \\
 & & \textit{The cheerleaders wore scanty outfits.}\\[0.08cm]
\textbf{archer} & n. &  a person who shoots with a bow and arrow\\[0.08cm]
\textbf{oracle} & n. &  a person (such as a priestess) through whom a god was believed to speak \\
 & & \textit{consulting an oracle}\\[0.08cm]
\textbf{intercept} & v. &  to stop and take someone or something that is going from one place to another place before that person or thing gets there \\
 & & \textit{Detectives have been intercepting her mail.}\\[0.08cm]
\textbf{betray} & v. &  to give information about (a person, group, country, etc.) to an enemy \\
 & & \textit{They betrayed their country by selling its secrets to other governments.}\\[0.08cm]
\textbf{arrogant} & adj. &  having or showing the insulting attitude of people who believe that they are better, smarter, or more important than other people :having or showing arrogance \\
 & & \textit{an arrogant young attorney}\\[0.08cm]
\textbf{deference} & n. &  a way of behaving that shows respect for someone or something \\
 & & \textit{Her relatives treat one another with deference.}\\[0.08cm]
\textbf{doubly} & adv. &  much more than usual or previously :to a much higher degree than usual \\
 & & \textit{We did the test again because we wanted to be doubly [=extra, especially, very] sure the results were accurate.}\\[0.08cm]
\textbf{reckless} & adj. &  not showing proper concern about the possible bad results of your actions \\
 & & \textit{He is a wild and reckless young man.}\\[0.08cm]
\textbf{commence} & v. &  to begin \\
 & & \textit{The festivities will commence with a parade.}\\[0.08cm]
\textbf{moderation} & n. &  the quality or state of being reasonable and avoiding behavior, speech, etc., that is extreme or that goes beyond what is normal or acceptable \\
 & & \textit{She expressed her opinions with moderation. = She showed moderation in the expression of her opinions. [=she expressed her opinions moderately]}\\[0.08cm]
\textbf{indulge} & v. &  to allow (yourself) to have or do something as a special pleasure \\
 & & \textit{It's my birthday. I'm going to indulge myself and eat whatever I want to eat.}\\[0.08cm]
\textbf{cam} & n. &  a part of a machine (such as an engine) that changes circular motion into another type of motion (such as forward motion)\\[0.08cm]
\textbf{vengeance} & n. &  the act of doing something to hurt someone because that person did something that hurt you or someone else \\
 & & \textit{The fire was set as an act of vengeance.}\\[0.08cm]
\textbf{confine} & v. &  to keep (someone or something) within limits :to prevent (someone or something) from going beyond a particular limit, area, etc. usually + to \\
 & & \textit{Please confine [=restrict, limit] your comments to 200 words.}\\[0.08cm]
\textbf{troop} & v. &  to walk somewhere in a group \\
 & & \textit{We all trooped back inside.}\\[0.08cm]
\textbf{compel} & v. &  to force (someone) to do something \\
 & & \textit{Illness compelled him to stay in bed.}\\[0.08cm]
\textbf{blockade} & v. &  to place a blockade on (a port or country) :to stop people or supplies from entering or leaving (a port or country) especially during a war \\
 & & \textit{They blockaded the country's ports.}\\[0.08cm]
\textbf{folly} & n. &  the lack of good sense or judgment :foolishness \\
 & & \textit{the folly of driving fast on steep, winding roads}\\[0.08cm]
\textbf{coincide} & v. &  to happen at the same time as something else \\
 & & \textit{The earthquakes coincided.}\\[0.08cm]
\textbf{envy} & v. &  to feel a desire to have what someone else has :to feel envy because of (someone or something) \\
 & & \textit{I envy you for your large group of friends.}\\[0.08cm]
\textbf{recourse} & n. &  an opportunity or choice to use or do something in order to deal with a problem or situation \\
 & & \textit{His only recourse [=the only thing he can do] is to file a complaint with the management.}\\[0.08cm]
\textbf{prophecy} & n. &  a statement that something will happen in the future :prediction \\
 & & \textit{The prophecies of the author have all come true.}\\[0.08cm]
\textbf{refrain} & v. &  to stop yourself from doing something that you want to do \\
 & & \textit{I was going to make a joke but I refrained.}\\[0.08cm]
\textbf{siege} & n. &  a situation in which soldiers or police officers surround a city, building, etc., in order to try to take control of it \\
 & & \textit{the siege of Paris}\\[0.08cm]
\textbf{ally} & v. &  to join (yourself) with another person, group, etc., in order to get or give support often + with or to \\
 & & \textit{She's allied herself with the moderates on this issue.}\\[0.08cm]
\end{longtable}
\end{document}
