\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage[margin=1in]{geometry}

\title{Vocabulary in \textit{The Prince}}
\author{Compiled by AcadeMe for the Homer Project}
\date{April 2016}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle
\begin{longtable}{llp{11cm}}
\textbf{bethink} & v. &  remember recall\\[0.08cm]
\textbf{gainsay} & v. &  to deny or disagree with (something) :to show or say that (something) is not true used in negative statements \\
 & & \textit{There is no gainsaying such evidence. [=the truth of such evidence cannot be denied]}\\[0.08cm]
\textbf{devastate} & v. &  to destroy much or most of (something) :to cause great damage or harm to (something) \\
 & & \textit{The flood devastated the town.}\\[0.08cm]
\textbf{guileless} & adj. &  very innocent :naive \\
 & & \textit{a guileless person/smile}\\[0.08cm]
\textbf{rapine} & n. &  pillage plunder\\[0.08cm]
\textbf{miserly} & adj. &  hating to spend money \\
 & & \textit{The team's miserly [=stingy, tightfisted] owner refused to pay for new equipment.}\\[0.08cm]
\textbf{flinch} & v. &  to move suddenly because you are afraid of being hit or hurt \\
 & & \textit{He flinched when I tapped him on the shoulder.}\\[0.08cm]
\textbf{lascivious} & adj. &  filled with or showing sexual desire \\
 & & \textit{lascivious acts/thoughts}\\[0.08cm]
\textbf{confiscate} & v. &  to take (something) away from someone especially as punishment or to enforce the law or rules \\
 & & \textit{Guards confiscated knives and other weapons from the prisoners.}\\[0.08cm]
\textbf{discus} & n. &  a heavy disk (as of wood or plastic) that is thicker in the center than at the perimeter and that is hurled for distance as a track-and-field event\\[0.08cm]
\textbf{centaur} & n. &  a creature in Greek mythology that is part human and part horse\\[0.08cm]
\textbf{faithless} & adj. &  not able to be trusted \\
 & & \textit{a faithless friend/employee/servant}\\[0.08cm]
\textbf{effeminate} & adj. &  having or showing qualities that are considered more suited to women than to men :not manly \\
 & & \textit{an effeminate manner}\\[0.08cm]
\textbf{fickle} & adj. &  changing often \\
 & & \textit{fickle weather}\\[0.08cm]
\textbf{patrimony} & n. &  property that you receive from your father when he dies :inheritance\\
 & & \textit{These historic landmarks are an important part of our cultural patrimony.}\\[0.08cm]
\textbf{leeway} & n. &  freedom to do something the way you want to do it \\
 & & \textit{They give/allow their students leeway to try new things.}\\[0.08cm]
\textbf{defenseless} & adj. &  not able to defend yourself, your country, etc. \\
 & & \textit{Without weapons of any kind, the people of the town were completely defenseless.}\\[0.08cm]
\textbf{crafty} & adj. &  clever in usually a deceptive or dishonest way \\
 & & \textit{a crafty schemer/plotter}\\[0.08cm]
\textbf{praiseworthy} & adj. &  deserving praise :worthy of praise \\
 & & \textit{praiseworthy efforts to develop an AIDS vaccine}\\[0.08cm]
\textbf{posse} & n. &  a group of people who were gathered together by a sheriff in the past to help search for a criminal \\
 & & \textit{The sheriff and his posse rode out to look for the bandits.}\\[0.08cm]
\textbf{principality} & n. &  a small area or country that is ruled by a prince\\[0.08cm]
\textbf{presumptuous} & adj. &  too confident especially in a way that is rude \\
 & & \textit{It would be presumptuous (of me) to tell the manager how to do things.}\\[0.08cm]
\textbf{laudable} & adj. &  deserving praise \\
 & & \textit{She has shown a laudable [=praiseworthy, commendable] devotion to her children.}\\[0.08cm]
\textbf{ungrateful} & adj. &  not feeling or showing thanks for favors, gifts, etc. :not grateful \\
 & & \textit{an ungrateful child}\\[0.08cm]
\textbf{lenient} & adj. &  allowing a lot of freedom and not punishing bad behavior in a strong way :not harsh, severe, or strict \\
 & & \textit{a teacher who is lenient with students who have misbehaved}\\[0.08cm]
\textbf{enumerate} & v. &  to name (things) one after another in a list \\
 & & \textit{Let me enumerate my reasons for doing this.}\\[0.08cm]
\textbf{benefactor} & n. &  someone who helps another person, group, etc., by giving money \\
 & & \textit{With the help of a rich benefactor he set up a charity.}\\[0.08cm]
\textbf{chaste} & adj. &  not having sex \\
 & & \textit{a chaste young woman}\\[0.08cm]
\textbf{cowardly} & adj. &  afraid in a way that makes you unable to do what is right or expected :lacking courage \\
 & & \textit{He insisted on avoiding a cowardly retreat.}\\[0.08cm]
\textbf{shun} & v. &  to avoid (someone or something) \\
 & & \textit{He shuns parties and social events.}\\[0.08cm]
\textbf{dissension} & n. &  disagreement that causes the people in a group to argue about something that is important to them \\
 & & \textit{The incident has caused a lot of dissension within/in the police department.}\\[0.08cm]
\textbf{precept} & n. &  a rule that says how people should behave \\
 & & \textit{the basic/moral precepts of a religion}\\[0.08cm]
\textbf{abstain} & v. &  to choose not to do or have something usually + from \\
 & & \textit{He abstained from taking part in the discussion.}\\[0.08cm]
\textbf{allegation} & n. &  a statement saying that someone has done something wrong or illegal \\
 & & \textit{The police are investigating allegations that the mayor has accepted bribes.}\\[0.08cm]
\textbf{liar} & n. &  a person who tells lies \\
 & & \textit{She called him a dirty liar.}\\[0.08cm]
\textbf{frighten} & v. &  to cause (someone) to become afraid \\
 & & \textit{The story really frightened me.}\\[0.08cm]
\textbf{frivolous} & adj. &  not important :not deserving serious attention \\
 & & \textit{She thinks window shopping is a frivolous activity.}\\[0.08cm]
\textbf{inhuman} & adj. &  very fierce or cruel \\
 & & \textit{inhuman [=savage] punishment}\\[0.08cm]
\textbf{plunder} & v. &  to steal things from (a place, such as a city or town) especially by force \\
 & & \textit{The village was plundered by the invading army.}\\[0.08cm]
\textbf{courteous} & adj. &  very polite in a way that shows respect \\
 & & \textit{The clerks were helpful and courteous.}\\[0.08cm]
\textbf{deviate} & v. &  to do something that is different or to be different from what is usual or expected usually + from \\
 & & \textit{He almost never deviates from his usual routine.}\\[0.08cm]
\textbf{incur} & v. &  to cause yourself to have or experience (something unpleasant or unwanted) \\
 & & \textit{incur expenses/debt}\\[0.08cm]
\textbf{greedy} & adj. &  having or showing a selfish desire to have more of something (such as money or food) :having greed \\
 & & \textit{He was a ruthless and greedy businessman.}\\[0.08cm]
\textbf{unbearable} & adj. &  too bad, harsh, or extreme to be accepted or endured :not bearable \\
 & & \textit{unbearable [=intolerable, unendurable] pain}\\[0.08cm]
\textbf{deem} & v. &  to think of (someone or something) in a particular way \\
 & & \textit{The building was deemed [=considered, judged] unsafe after the fire.}\\[0.08cm]
\textbf{precaution} & n. &  something that is done to prevent possible harm or trouble from happening in the future \\
 & & \textit{Be sure to follow the usual safety precautions when cooking outdoors.}\\[0.08cm]
\textbf{mutiny} & n. &  a situation in which a group of people (such as sailors or soldiers) refuse to obey orders and try to take control away from the person who commands them \\
 & & \textit{The mutiny was led by the ship's cook.}\\[0.08cm]
\textbf{devout} & adj. &  deeply religious :devoted to a particular religion \\
 & & \textit{They are devout Catholics.}\\[0.08cm]
\textbf{deceive} & v. &  to make (someone) believe something that is not true \\
 & & \textit{Her parents punished her for trying to deceive them.}\\[0.08cm]
\textbf{reproach} & v. &  to speak in an angry and critical way to (someone) :to express disapproval or disappointment to (someone) often + for \\
 & & \textit{She reproached her daughter for her selfishness.}\\[0.08cm]
\textbf{spoil} & v. &  to have a bad effect on (something) :to damage or ruin (something) \\
 & & \textit{The fight spoiled the party.}\\[0.08cm]
\textbf{allegory} & n. &  a story in which the characters and events are symbols that stand for ideas about human life or for a political or historical situation \\
 & & \textit{the long poem is an allegory of/about love and jealousy}\\[0.08cm]
\textbf{abide} & v. &  to accept or bear (someone or something bad, unpleasant, etc.) usually used in negative constructions \\
 & & \textit{I can't abide his bad moods. [=(more commonly) I can't stand his bad moods; I hate his bad moods]}\\[0.08cm]
\textbf{pretext} & n. &  a reason that you give to hide your real reason for doing something :pretense \\
 & & \textit{The leaders used a minor clash at the border as a pretext for war. [=as a reason/excuse for starting a war]}\\[0.08cm]
\textbf{courageous} & adj. &  very brave :having or showing courage \\
 & & \textit{a courageous soldier}\\[0.08cm]
\textbf{indulge} & v. &  to allow (yourself) to have or do something as a special pleasure \\
 & & \textit{It's my birthday. I'm going to indulge myself and eat whatever I want to eat.}\\[0.08cm]
\textbf{omit} & v. &  to leave out (someone or something) :to not include (someone or something) \\
 & & \textit{Please don't omit any details.}\\[0.08cm]
\textbf{cunning} & adj. &  getting what is wanted in a clever and often deceptive way \\
 & & \textit{a cunning criminal}\\[0.08cm]
\textbf{dictate} & v. &  to speak or read (something) to a person who writes it down or to a machine that records it \\
 & & \textit{She's dictating a letter to her secretary.}\\[0.08cm]
\textbf{prudence} & n. &  careful good judgment that allows someone to avoid danger or risks \\
 & & \textit{act with ordinary/reasonable prudence}\\[0.08cm]
\textbf{rash} & adj. &  done or made quickly and without thought about what will happen as a result \\
 & & \textit{He later regretted having made such a rash [=hasty] promise.}\\[0.08cm]
\textbf{conquer} & v. &  to take control of (a country, city, etc.) through the use of force \\
 & & \textit{The city was conquered by the ancient Romans.}\\[0.08cm]
\textbf{stubborn} & adj. &  refusing to change your ideas or to stop doing something \\
 & & \textit{She's wrong, but she's too stubborn to admit it.}\\[0.08cm]
\textbf{virtuous} & adj. &  morally good :having or showing virtue \\
 & & \textit{a virtuous man/woman}\\[0.08cm]
\textbf{condemn} & v. &  to say in a strong and definite way that someone or something is bad or wrong \\
 & & \textit{We strongly condemn this attack against our allies.}\\[0.08cm]
\textbf{swear} & v. &  to state (something) very strongly and sincerely \\
 & & \textit{I swear (that) I was there. [=I was definitely there; I am telling you the truth when I say that I was there]}\\[0.08cm]
\textbf{imitate} & v. &  to make or do something the same way as (something else) \\
 & & \textit{Their competitors soon imitated [=copied] the idea.}\\[0.08cm]
\textbf{defiance} & n. &  a refusal to obey something or someone :the act of defying someone or something \\
 & & \textit{acts of defiance}\\[0.08cm]
\textbf{prudent} & adj. &  having or showing careful good judgment \\
 & & \textit{He always listened to her prudent advice.}\\[0.08cm]
\textbf{troop} & v. &  to walk somewhere in a group \\
 & & \textit{We all trooped back inside.}\\[0.08cm]
\textbf{deception} & n. &  the act of making someone believe something that is not true :the act of deceiving someone \\
 & & \textit{She accuses the company of willful deception in its advertising.}\\[0.08cm]
\textbf{impress} & v. &  to cause (someone) to feel admiration or interest \\
 & & \textit{He's trying to impress her. [=he is trying to win her admiration; he wants her to like him]}\\[0.08cm]
\textbf{wretched} & adj. &  very unhappy, ill, etc. \\
 & & \textit{The slums were filled with poor, wretched children.}\\[0.08cm]
\textbf{legion} & adj. &  very many or numerous \\
 & & \textit{Her admirers/fans are legion. [=she has a very large number of admirers/fans]}\\[0.08cm]
\textbf{dread} & v. &  to fear something that will or might happen \\
 & & \textit{He can't swim and dreads going in the water.}\\[0.08cm]
\textbf{safeguard} & v. &  to make (someone or something) safe or secure :protect \\
 & & \textit{laws that safeguard the rights of citizens}\\[0.08cm]
\textbf{preach} & v. &  to make a speech about religion in a church or other public place :to deliver a sermon \\
 & & \textit{Have you ever heard that minister preach?}\\[0.08cm]
\textbf{condemnation} & n. &  a statement or expression of very strong and definite criticism or disapproval \\
 & & \textit{The plan has drawn condemnation from both sides.}\\[0.08cm]
\textbf{endeavor} & v. &  to seriously or continually try to do (something) \\
 & & \textit{The school endeavors to teach students to be good citizens.}\\[0.08cm]
\textbf{conceal} & v. &  to hide (something or someone) from sight \\
 & & \textit{The sunglasses conceal her eyes.}\\[0.08cm]
\textbf{recourse} & n. &  an opportunity or choice to use or do something in order to deal with a problem or situation \\
 & & \textit{His only recourse [=the only thing he can do] is to file a complaint with the management.}\\[0.08cm]
\textbf{punish} & v. &  to make (someone) suffer for a crime or for bad behavior \\
 & & \textit{I think that murderers should be punished by/with life imprisonment.}\\[0.08cm]
\textbf{cruelty} & n. &  a desire to cause others to suffer :the quality or state of being cruel \\
 & & \textit{a dictator/tyrant known for his cruelty}\\[0.08cm]
\textbf{admirable} & adj. &  deserving to be admired :very good \\
 & & \textit{The film does an admirable [=excellent] job of depicting life in the 1940s.}\\[0.08cm]
\textbf{compassion} & n. &  a feeling of wanting to help someone who is sick, hungry, in trouble, etc. \\
 & & \textit{He felt compassion for the lost child.}\\[0.08cm]
\textbf{seize} & v. &  to use legal or official power to take (something) \\
 & & \textit{Police seized [=confiscated] the weapons and drugs.}\\[0.08cm]
\textbf{innumerable} & adj. &  too many to be counted :very many \\
 & & \textit{the innumerable [=countless] stars in the sky}\\[0.08cm]
\textbf{corrupt} & v. &  to cause (someone or something) to become dishonest, immoral, etc. \\
 & & \textit{He believes that violence on television and film is corrupting our children. [=teaching bad beliefs and behaviors to our children]}\\[0.08cm]
\end{longtable}
\end{document}
