\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage[margin=1in]{geometry}

\title{Vocabulary in \textit{Republic}}
\author{Compiled by AcadeMe for the Homer Project}
\date{April 2016}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle
\begin{longtable}{llp{11cm}}
\textbf{exploit} & v. &  to get value or use from (something) \\
 & & \textit{He has never fully exploited his talents.}\\[0.08cm]
\textbf{shepherd} & v. &  to guide (someone or something) \\
 & & \textit{She carefully shepherded the children across the street.}\\[0.08cm]
\textbf{tolerate} & v. &  to allow (something that is bad, unpleasant, etc.) to exist, happen, or be done \\
 & & \textit{Our teacher will not tolerate bad grammar.}\\[0.08cm]
\textbf{unjust} & adj. &  not fair or deserved :not just \\
 & & \textit{The convict received an unjust sentence.}\\[0.08cm]
\textbf{lawful} & adj. &  allowed by the law \\
 & & \textit{lawful conduct}\\[0.08cm]
\textbf{stature} & n. &  the level of respect that people have for a successful person, organization, etc. \\
 & & \textit{We are honored to be working with a writer of his stature. [=a writer who is so highly respected]}\\[0.08cm]
\textbf{isolate} & v. &  to put or keep (someone or something) in a place or situation that is separate from others \\
 & & \textit{These policies will only serve to isolate the country politically and economically.}\\[0.08cm]
\textbf{din} & n. &  a loud, confusing mixture of noises that lasts for a long time \\
 & & \textit{It was hard to hear anything above/over the din in the restaurant.}\\[0.08cm]
\textbf{behold} & v. &  to look at (something) :to see (something) \\
 & & \textit{Those who have beheld the beauty of the desert never forget it.}\\[0.08cm]
\textbf{flock} & v. &  to gather or move in a crowd \\
 & & \textit{Thousands of people flocked to the beach each weekend.}\\[0.08cm]
\textbf{wretched} & adj. &  very unhappy, ill, etc. \\
 & & \textit{The slums were filled with poor, wretched children.}\\[0.08cm]
\textbf{prudent} & adj. &  having or showing careful good judgment \\
 & & \textit{He always listened to her prudent advice.}\\[0.08cm]
\textbf{descend} & v. &  to go down :to go or move from a higher to a lower place or level \\
 & & \textit{Wait for the elevator to descend.}\\[0.08cm]
\textbf{whereupon} & conjunction &  at which time used to say that something happens directly after something else and often as a result of it \\
 & & \textit{He graduated from high school in 1986, whereupon he immediately joined the navy.}\\[0.08cm]
\textbf{rack} & v. &  to cause (someone or something) to suffer pain or damage usually used as (be) racked \\
 & & \textit{He was racked with/by jealousy [=he was very jealous] when he saw his ex-wife with another man.}\\[0.08cm]
\textbf{precede} & v. &  to happen, go, or come before (something or someone) \\
 & & \textit{Riots preceded the civil war.}\\[0.08cm]
\textbf{revive} & v. &  to make (someone or something) strong, healthy, or active again \\
 & & \textit{The doctors were trying to revive the patient. [=to make the unconscious patient conscious again]}\\[0.08cm]
\textbf{reckon} & v. &  to think or suppose (something) :to believe that (something) is true or possible \\
 & & \textit{I reckon that we'll have to leave early.}\\[0.08cm]
\textbf{divert} & v. &  to change the direction or use of (something) \\
 & & \textit{Police diverted traffic to a side street.}\\[0.08cm]
\textbf{censure} & v. &  to officially criticize (someone or something) strongly and publicly \\
 & & \textit{He was censured by the committee for his failure to report the problem.}\\[0.08cm]
\textbf{deem} & v. &  to think of (someone or something) in a particular way \\
 & & \textit{The building was deemed [=considered, judged] unsafe after the fire.}\\[0.08cm]
\textbf{myriad} & adj. &  very many \\
 & & \textit{The old system's problems were myriad.}\\[0.08cm]
\textbf{idiot} & n. &  a very stupid or foolish person \\
 & & \textit{Don't be such an idiot!}\\[0.08cm]
\textbf{refute} & v. &  to prove that (something) is not true \\
 & & \textit{The lawyer refuted the testimony of the witness.}\\[0.08cm]
\textbf{antagonist} & n. &  a person who opposes another person \\
 & & \textit{He faced his antagonist [=(more commonly) opponent, adversary] in a series of debates.}\\[0.08cm]
\textbf{marvel} & v. &  to feel great surprise, wonder, or admiration \\
 & & \textit{The audience marveled at the magician's skill.}\\[0.08cm]
\textbf{inwardly} & adv. &  in a way that is not openly shown or stated :on the inside \\
 & & \textit{He chuckled/smiled/cursed inwardly.}\\[0.08cm]
\textbf{whither} & adv. &  to what place \\
 & & \textit{He grew up in New York City whither his family had immigrated in the early 1920s.}\\[0.08cm]
\textbf{dedicate} & v. &  to officially make (something) a place for honoring or remembering a person, event, etc. \\
 & & \textit{The new park was dedicated today.}\\[0.08cm]
\textbf{scourge} & v. &  to cause a lot of trouble or suffering for (someone or something) \\
 & & \textit{a neighborhood scourged by crime}\\[0.08cm]
\textbf{stoop} & v. &  to bend down or over \\
 & & \textit{She stooped down to hug the child.}\\[0.08cm]
\textbf{brazen} & adj. &  acting or done in a very open and shocking way without shame or embarrassment \\
 & & \textit{He exhibited a brazen disregard for other people's feelings.}\\[0.08cm]
\textbf{posse} & n. &  a group of people who were gathered together by a sheriff in the past to help search for a criminal \\
 & & \textit{The sheriff and his posse rode out to look for the bandits.}\\[0.08cm]
\textbf{seduce} & v. &  to persuade (someone) to have sex with you \\
 & & \textit{He tried to seduce her.}\\[0.08cm]
\textbf{contrive} & v. &  to form or think of (a plan, method, etc.) \\
 & & \textit{The prisoners contrived a way to escape.}\\[0.08cm]
\textbf{infamy} & n. &  the condition of being known for having done bad things or for being evil \\
 & & \textit{He never escaped the infamy his crimes had earned him.}\\[0.08cm]
\textbf{restate} & v. &  to say (something) again or in a different way especially to make the meaning clearer \\
 & & \textit{She needs to restate her arguments.}\\[0.08cm]
\textbf{conspire} & v. &  to secretly plan with someone to do something that is harmful or illegal often followed by to + verb \\
 & & \textit{They were accused of conspiring to overthrow the government.}\\[0.08cm]
\textbf{ordain} & v. &  to officially make (someone) a minister, priest, rabbi, etc. \\
 & & \textit{He was ordained (as) a priest.}\\[0.08cm]
\textbf{narrate} & v. &  to tell (a story) \\
 & & \textit{The author narrates her story in great detail.}\\[0.08cm]
\textbf{uttermost} & adj. &  utmost \\
 & & \textit{a matter of the uttermost importance}\\[0.08cm]
\textbf{gymnastic} & n. &  physical exercises for developing strength and balance \\
 & & \textit{They limbered up by practicing some gymnastics on the mat.}\\[0.08cm]
\textbf{pugnacious} & adj. &  showing a readiness or desire to fight or argue \\
 & & \textit{There's one pugnacious member on the committee who won't agree to anything.}\\[0.08cm]
\textbf{perplex} & v. &  to confuse (someone) very much \\
 & & \textit{Her attitude perplexes me. = I am perplexed by her attitude.}\\[0.08cm]
\textbf{impale} & v. &  to cause a pointed object to go into or through (someone or something) often + on \\
 & & \textit{He slipped and impaled his leg on a metal spike.}\\[0.08cm]
\textbf{dissatisfy} & v. &  to fail to make (someone) happy or pleased \\
 & & \textit{Their final decision dissatisfied [=displeased] everyone.}\\[0.08cm]
\end{longtable}
\end{document}
