\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage[margin=1in]{geometry}

\title{Vocabulary in \textit{The Subjection of Women}}
\author{Compiled by AcadeMe for the Homer Project}
\date{April 2016}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle
\begin{longtable}{llp{11cm}}
\textbf{wive} & v. &  to marry a woman\\[0.08cm]
\textbf{protract} & v. &  delay defer\\[0.08cm]
\textbf{ennoble} & v. &  to make (someone or something) better or more worthy of admiration \\
 & & \textit{a life ennobled by suffering}\\[0.08cm]
\textbf{overstep} & v. &  to go beyond what is proper or allowed by (something) \\
 & & \textit{The judges overstepped their authority. [=the judges did something that they are not allowed to do]}\\[0.08cm]
\textbf{civilize} & v. &  to teach (a person or group of people) to behave in a way that you think is more polite and gentle \\
 & & \textit{Her parents hoped that boarding school might civilize her some.}\\[0.08cm]
\textbf{avow} & v. &  to declare or state (something) in an open and public way \\
 & & \textit{She avowed her innocence. = She avowed that she was innocent.}\\[0.08cm]
\textbf{outlast} & v. &  to last longer than (someone or something) :to continue to exist, be active, etc., longer than (someone or something) \\
 & & \textit{We watched him outlast his opponent in one of the greatest boxing matches of all time.}\\[0.08cm]
\textbf{pillory} & v. &  to publicly criticize (someone) in a very harsh way \\
 & & \textit{The press pilloried the judge for her decision.}\\[0.08cm]
\textbf{interdict} & v. &  to lay under or prohibit by an interdict\\
 & & \textit{interdict drug shipments}\\[0.08cm]
\textbf{kidnap} & v. &  to take away (someone) by force usually in order to keep the person as a prisoner and demand money for returning the person \\
 & & \textit{She had been kidnapped (from her home).}\\[0.08cm]
\textbf{ordain} & v. &  to officially make (someone) a minister, priest, rabbi, etc. \\
 & & \textit{He was ordained (as) a priest.}\\[0.08cm]
\textbf{plebeian} & n. &  a member of the common people of ancient Rome\\[0.08cm]
\textbf{irrepressible} & adj. &  impossible to hold back, stop, or control \\
 & & \textit{He has irrepressible curiosity.}\\[0.08cm]
\textbf{serf} & n. &  a person in the past who belonged to a low social class and who lived and worked on land owned by another person \\
 & & \textit{medieval serfs}\\[0.08cm]
\textbf{unfettered} & adj. &  not controlled or restricted \\
 & & \textit{unfettered [=free] access}\\[0.08cm]
\textbf{rivet} & v. &  to attract and hold all of someone's attention usually used as (be) riveted \\
 & & \textit{I was riveted by her story. [=her story was so interesting that I was giving all of my attention to it]}\\[0.08cm]
\textbf{patrician} & n. &  a person who is a member of the highest social class :aristocrat\\[0.08cm]
\textbf{diametrically} & adv. &  completely or entirely \\
 & & \textit{His position on the issue is diametrically opposed to that of his partner. [=his position is the exact opposite of his partner's position]}\\[0.08cm]
\textbf{culprit} & n. &  a person who has committed a crime or done something wrong \\
 & & \textit{The police eventually located the culprits.}\\[0.08cm]
\textbf{discordant} & adj. &  harsh or unpleasant in sound \\
 & & \textit{discordant music}\\[0.08cm]
\textbf{frustrate} & v. &  to cause (someone) to feel angry, discouraged, or upset because of not being able to do something \\
 & & \textit{It frustrated him to miss so many games because of injuries.}\\[0.08cm]
\textbf{regal} & adj. &  of, relating to, or suitable for a king or queen \\
 & & \textit{He has a regal bearing. [=he is very dignified, authoritative, etc.]}\\[0.08cm]
\textbf{inexorable} & adj. &  not able to be stopped or changed \\
 & & \textit{an inexorable conclusion}\\[0.08cm]
\textbf{weighty} & adj. &  having a lot of weight :heavy \\
 & & \textit{She grabbed a weighty book off the shelf.}\\[0.08cm]
\textbf{commoner} & n. &  a person who is not a member of the nobility \\
 & & \textit{a prince who married a commoner}\\[0.08cm]
\textbf{mischievous} & adj. &  causing or tending to cause annoyance or minor harm or damage \\
 & & \textit{a mischievous puppy/child}\\[0.08cm]
\textbf{relic} & n. &  something that is from a past time, place, culture, etc. often + of or from \\
 & & \textit{relics of ancient China}\\[0.08cm]
\textbf{specie} & n. &  money in coin\\[0.08cm]
\textbf{elevate} & v. &  to lift (something) up \\
 & & \textit{The doctor told her to elevate [=raise] her leg.}\\[0.08cm]
\textbf{nobleman} & n. &  a man who is a member of the nobility\\[0.08cm]
\textbf{blacksmith} & n. &  a person who makes or repairs things made of iron (such as horseshoes)\\[0.08cm]
\textbf{infallible} & adj. &  not capable of being wrong or making mistakes :not fallible \\
 & & \textit{I never claimed to be infallible.}\\[0.08cm]
\textbf{inflict} & v. &  to cause someone to experience or be affected by (something unpleasant or harmful) \\
 & & \textit{These insects are capable of inflicting a painful sting.}\\[0.08cm]
\textbf{hindrance} & n. &  a person or thing that makes a situation difficult :a person or thing that hinders someone or something \\
 & & \textit{She wanted to sign up for the class, but the cost was a hindrance. [=the class cost too much]}\\[0.08cm]
\textbf{grind} & v. &  to crush or break (something) into very small pieces by rubbing it against a rough surface or using a special machine \\
 & & \textit{Grind (up) the coffee beans into a fine powder.}\\[0.08cm]
\textbf{industrious} & adj. &  working very hard :not lazy \\
 & & \textit{He is an industrious worker.}\\[0.08cm]
\textbf{detriment} & n. &  something that will cause damage or injury to something or someone usually singular often + to \\
 & & \textit{He saw the new regulations as a detriment to progress.}\\[0.08cm]
\textbf{deem} & v. &  to think of (someone or something) in a particular way \\
 & & \textit{The building was deemed [=considered, judged] unsafe after the fire.}\\[0.08cm]
\textbf{unrestricted} & adj. &  not controlled or limited in any way :not restricted \\
 & & \textit{I was granted unrestricted access to the documents.}\\[0.08cm]
\textbf{unfit} & adj. &  not proper, suitable, or acceptable often + for \\
 & & \textit{The movie is unfit for children. [=children should not watch the movie]}\\[0.08cm]
\textbf{tyrant} & n. &  a ruler who has complete power over a country and who is cruel and unfair \\
 & & \textit{The country was ruled by a corrupt tyrant [=despot] for decades.}\\[0.08cm]
\textbf{forbid} & v. &  to order (someone) not to do something \\
 & & \textit{I forbid you to go!}\\[0.08cm]
\textbf{beforehand} & adv. &  in advance :at an earlier or previous time \\
 & & \textit{They'd agreed beforehand [=ahead of time] to leave early.}\\[0.08cm]
\textbf{yoke} & v. &  to connect (two animals) by a yoke \\
 & & \textit{The two oxen were yoked together.}\\[0.08cm]
\textbf{precede} & v. &  to happen, go, or come before (something or someone) \\
 & & \textit{Riots preceded the civil war.}\\[0.08cm]
\textbf{incompetent} & adj. &  not competent: such as\\
 & & \textit{an incompetent worker/doctor}\\[0.08cm]
\textbf{procure} & v. &  to get (something) by some action or effort :obtain \\
 & & \textit{She managed to procure a ticket to the concert.}\\[0.08cm]
\textbf{presume} & v. &  to think that (something) is true without knowing that it is true \\
 & & \textit{I presume [=assume, expect] (that) you'll fly to Chicago rather than drive.}\\[0.08cm]
\textbf{bondage} & n. &  the state of being a slave :slavery \\
 & & \textit{He delivered the slaves from bondage. [=he freed the slaves]}\\[0.08cm]
\textbf{oppressive} & adj. &  very cruel or unfair \\
 & & \textit{The country is ruled by an oppressive regime.}\\[0.08cm]
\textbf{impartial} & adj. &  treating all people and groups equally :not partial or biased \\
 & & \textit{an impartial analysis of the case}\\[0.08cm]
\textbf{deprive} & v. &  to take something away from someone or something :to not allow (someone or something) to have or keep (something) \\
 & & \textit{The change in her status deprived her of access to classified information.}\\[0.08cm]
\textbf{prescribe} & v. &  to officially tell someone to use (a medicine, therapy, diet, etc.) as a remedy or treatment \\
 & & \textit{My doctor prescribed this medicine. = This medicine was prescribed by my doctor.}\\[0.08cm]
\textbf{condemn} & v. &  to say in a strong and definite way that someone or something is bad or wrong \\
 & & \textit{We strongly condemn this attack against our allies.}\\[0.08cm]
\textbf{disclose} & v. &  to make (something) known to the public \\
 & & \textit{He refused to disclose the source of his information.}\\[0.08cm]
\textbf{avail} & v. &  to be useful or helpful to (someone or something) \\
 & & \textit{Our best efforts availed [=gained] us nothing.}\\[0.08cm]
\textbf{indignation} & n. &  anger caused by something that is unfair or wrong \\
 & & \textit{The decision to close the factory has aroused the indignation of the townspeople.}\\[0.08cm]
\textbf{dispose} & v. &  to cause (someone) to be likely to do or have something + to or toward \\
 & & \textit{His upbringing disposes him to question authority.}\\[0.08cm]
\textbf{guild} & n. &  an organized group of people who have joined together because they share the same job or interest \\
 & & \textit{the local artists' guild}\\[0.08cm]
\textbf{practicable} & adj. &  able to be done or used \\
 & & \textit{There's no practicable [=feasible] way to do the experiment with the current technology.}\\[0.08cm]
\textbf{presumption} & n. &  a belief that something is true even though it has not been proved often + that \\
 & & \textit{The presumption is that the thief had a key to the store.}\\[0.08cm]
\textbf{motif} & n. &  something (such as an important idea or subject) that is repeated throughout a book, story, etc.\\
 & & \textit{The wallpaper has a flower motif.}\\[0.08cm]
\textbf{suffrage} & n. &  the right to vote in an election \\
 & & \textit{women who fought for suffrage}\\[0.08cm]
\end{longtable}
\end{document}
