\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage[margin=1in]{geometry}

\title{Vocabulary in \textit{Swann's Way}}
\author{Compiled by AcadeMe for the Homer Project}
\date{March 2016}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle
\begin{longtable}{llp{11cm}}
\textbf{palpitate} & v. &  to beat quickly and strongly and often in a way that is not regular because of excitement, nervousness, etc. \\
 & & \textit{My heart began to palpitate when I was announced as the winner.}\\[0.08cm]
\textbf{importune} & v. &  to ask (someone) for something or to do something in a repeated or annoying way :beg \\
 & & \textit{He stood on the street corner, importuning passersby for help/money.}\\[0.08cm]
\textbf{vicissitude} & n. &  the quality or state of being changeable :mutability\\
 & & \textit{the vicissitudes of daily life}\\[0.08cm]
\textbf{wainscot} & v. &  to line with or as if with boards or paneling\\[0.08cm]
\textbf{unfaltering} & adj. &  not wavering or weakening :firm \\
 & & \textit{unfaltering loyalty}\\[0.08cm]
\textbf{engrave} & v. &  to cut or carve lines, letters, designs, etc., onto or into a hard surface \\
 & & \textit{They will engrave your initials on the ring for free.}\\[0.08cm]
\textbf{unsubstantial} & adj. &  not substantial :lacking substance, firmness, or strength \\
 & & \textit{unsubstantial shadows}\\[0.08cm]
\textbf{impalpable} & adj. &  incapable of being felt by touch :intangible \\
 & & \textit{the impalpable aura of power that emanated from him }\\[0.08cm]
\textbf{paramour} & n. &  a person with whom someone is having a romantic or sexual relationship and especially a secret or improper relationship \\
 & & \textit{Her husband found a love letter from her paramour. [=lover]}\\[0.08cm]
\textbf{cud} & n. &  the food that an animal (such as a cow) brings back up from its stomach into its mouth to be chewed again \\
 & & \textit{a cow chewing its cud}\\[0.08cm]
\textbf{embed} & v. &  to place or set (something) firmly in something else \\
 & & \textit{embed a post in concrete}\\[0.08cm]
\textbf{illumine} & v. &  illuminate \\
 & & \textit{streets illumined by gaslight}\\[0.08cm]
\textbf{punctuate} & v. &  to use punctuation marks in (a piece of writing) \\
 & & \textit{Do you know how to punctuate a sentence correctly?}\\[0.08cm]
\textbf{outgrow} & v. &  to grow too large for (someone or something) \\
 & & \textit{Kids outgrow their clothes so quickly.}\\[0.08cm]
\textbf{scallop} & n. &  a type of shellfish that has a flat, round shell with two parts and that is often eaten as food \\[0.08cm]
\textbf{thrall} & n. &  in a state of being controlled or strongly influenced by someone or something \\
 & & \textit{He was completely in thrall to her. = He was completely in her thrall.}\\[0.08cm]
\textbf{creak} & v. &  to make a long, high sound :to make a sound like the sound made by an old door when it opens or closes \\
 & & \textit{The door creaked open. = The door made a creaking sound as it opened.}\\[0.08cm]
\textbf{kaleidoscope} & n. &  a tube that has mirrors and loose pieces of colored glass or plastic inside at one end so that you see many different patterns when you turn the tube while looking in through the other end\\
 & & \textit{The landscape was a kaleidoscope of changing colors.}\\[0.08cm]
\textbf{assuage} & v. &  to make (something, such as an unpleasant feeling) less painful, severe, etc. \\
 & & \textit{The company tried to assuage [=soothe, calm, ease] investors' fears.}\\[0.08cm]
\textbf{allure} & n. &  power to attract :a quality that attracts people \\
 & & \textit{These rare books hold special allure for collectors.}\\[0.08cm]
\textbf{crumb} & n. &  a very small piece of food \\
 & & \textit{He swept the crumbs from under the table.}\\[0.08cm]
\textbf{dissect} & v. &  to cut (a plant or dead animal) into separate parts in order to study it \\
 & & \textit{We dissected a frog in science class.}\\[0.08cm]
\textbf{savor} & v. &  to enjoy the taste or smell of (something) for as long as possible \\
 & & \textit{He savored the aroma of the baking pies.}\\[0.08cm]
\textbf{morsel} & n. &  a small piece of food \\
 & & \textit{tender morsels of beef}\\[0.08cm]
\textbf{undress} & v. &  to take your clothes off \\
 & & \textit{She undressed and climbed into bed.}\\[0.08cm]
\textbf{restful} & adj. &  peaceful and quiet in a way that makes you relax \\
 & & \textit{It's restful by the stream.}\\[0.08cm]
\textbf{mouthful} & n. &  as much as a mouth will hold \\
 & & \textit{a mouthful of food/water}\\[0.08cm]
\textbf{retrace} & v. &  to go back along the same course, path, etc., that you or someone else has taken earlier \\
 & & \textit{retrace a path/route}\\[0.08cm]
\textbf{glimmer} & v. &  to shine in a weak, faint, or unsteady way \\
 & & \textit{Candles glimmered in the windows of the inn.}\\[0.08cm]
\textbf{medley} & n. &  a musical piece made up of parts of other musical works \\
 & & \textit{a medley of show tunes}\\[0.08cm]
\textbf{obliterate} & v. &  to destroy (something) completely so that nothing is left \\
 & & \textit{The tide eventually obliterated [=wiped out] all evidence of our sand castles.}\\[0.08cm]
\textbf{elapse} & v. &  to pass by \\
 & & \textit{Weeks elapsed [=passed] before he returned home.}\\[0.08cm]
\textbf{reincarnation} & n. &  the idea or belief that people are born again with a different body after death \\
 & & \textit{Many people believe in reincarnation.}\\[0.08cm]
\textbf{whirl} & v. &  to move or go in a circle or curve especially with force or speed \\
 & & \textit{The cars were whirling around the track.}\\[0.08cm]
\textbf{unaccustomed} & adj. &  not usual or common :not customary \\
 & & \textit{They responded to our request with unaccustomed speed.}\\[0.08cm]
\textbf{subsist} & v. &  to exist or continue to exist \\
 & & \textit{The author's right to royalties shall subsist for the term of the copyright.}\\[0.08cm]
\textbf{detach} & v. &  to separate (something) from something larger \\
 & & \textit{Detach the upper part of the form and return it with your payment.}\\[0.08cm]
\textbf{snatch} & v. &  to take (something) quickly or eagerly \\
 & & \textit{She snatched [=grabbed] the ball out of the air and ran down the court.}\\[0.08cm]
\textbf{errand} & n. &  a short journey that you take to do or get something \\
 & & \textit{He was sent out on an urgent errand.}\\[0.08cm]
\textbf{innocuous} & adj. &  not likely to bother or offend anyone :inoffensive \\
 & & \textit{He told a few innocuous jokes.}\\[0.08cm]
\textbf{shudder} & v. &  to shake because of fear, cold, etc. often + with \\
 & & \textit{He shuddered [=quivered, trembled] with fear when he heard the scream.}\\[0.08cm]
\textbf{poise} & v. &  to hold (something) in a balanced and steady position \\
 & & \textit{She poised her pencil above the paper and waited for the signal to begin writing.}\\[0.08cm]
\textbf{dispel} & v. &  to make (something, such as a belief, feeling, or idea) go away or end \\
 & & \textit{This report should dispel any doubts you have about the plan.}\\[0.08cm]
\textbf{pastry} & n. &  dough that is used to make pies and other baked goods \\
 & & \textit{He worked on the filling while I prepared the pastry.}\\[0.08cm]
\textbf{soak} & v. &  to put (something) in a liquid for a period of time \\
 & & \textit{Soak the beans overnight (in water).}\\[0.08cm]
\textbf{reappear} & v. &  to appear again after not being seen, felt, etc., for a period of time \\
 & & \textit{We watched the fireflies in the field vanish and then reappear.}\\[0.08cm]
\textbf{ponder} & v. &  to think about or consider (something) carefully \\
 & & \textit{He pondered the question before he answered.}\\[0.08cm]
\textbf{unintelligible} & adj. &  impossible to understand :not intelligible \\
 & & \textit{He left an unintelligible message on my voice mail.}\\[0.08cm]
\textbf{oblige} & v. &  to force or require (someone or something) to do something because of a law or rule or because it is necessary \\
 & & \textit{The law obliges the government to release certain documents to the public.}\\[0.08cm]
\textbf{brevity} & n. &  the quality of being brief: such as\\
 & & \textit{I've omitted certain passages for the sake of brevity. [=because I want to be brief]}\\[0.08cm]
\textbf{mediocre} & adj. &  not very good \\
 & & \textit{The dinner was delicious, but the dessert was mediocre.}\\[0.08cm]
\textbf{tremble} & v. &  to shake slightly because you are afraid, nervous, excited, etc. \\
 & & \textit{His arms and legs began to tremble.}\\[0.08cm]
\textbf{plump} & v. &  to sit, fall, or lie down in a sudden, awkward, or relaxed way :plop \\
 & & \textit{He came home and plumped [=flopped] down on the couch.}\\[0.08cm]
\textbf{distraction} & n. &  something that makes it difficult to think or pay attention \\
 & & \textit{It was hard to work with so many distractions.}\\[0.08cm]
\textbf{inanimate} & adj. &  not living :not capable of life \\
 & & \textit{Stones are inanimate.}\\[0.08cm]
\textbf{recapture} & v. &  to catch (someone or something that has escaped) \\
 & & \textit{The guards recaptured the escaped prisoner.}\\[0.08cm]
\textbf{illuminate} & v. &  to supply (something) with light :to shine light on (something) \\
 & & \textit{Candles illuminate [=light] the church.}\\[0.08cm]
\textbf{spasm} & n. &  a sudden uncontrolled and often painful tightening of a muscle \\
 & & \textit{violent back spasms}\\[0.08cm]
\textbf{magnetism} & n. &  the property of attracting certain metals :the attracting property of a magnet\\
 & & \textit{Much of his success as a politician can be attributed to his personal magnetism.}\\[0.08cm]
\textbf{extraneous} & adj. &  not forming a necessary part of something \\
 & & \textit{She sped up the process by eliminating all extraneous steps.}\\[0.08cm]
\textbf{pavilion} & n. &  a building in a park or garden that usually has open sides and is used for parties, concerts, or other events\\
 & & \textit{The World's Fair had numerous pavilions.}\\[0.08cm]
\textbf{streak} & v. &  to make long lines of a different color on or in (something) \\
 & & \textit{Tears streaked her face.}\\[0.08cm]
\textbf{hop} & v. &  to move by a quick jump or series of jumps \\
 & & \textit{He hopped over the hot sand.}\\[0.08cm]
\textbf{glaze} & v. &  to give a smooth and shiny coating to (something) \\
 & & \textit{The storm glazed the trees with ice.}\\[0.08cm]
\textbf{transcend} & v. &  to rise above or go beyond the normal limits of (something) \\
 & & \textit{music that transcends cultural boundaries}\\[0.08cm]
\textbf{dormant} & adj. &  not doing anything at this time :not active but able to become active \\
 & & \textit{a dormant volcano}\\[0.08cm]
\textbf{precaution} & n. &  something that is done to prevent possible harm or trouble from happening in the future \\
 & & \textit{Be sure to follow the usual safety precautions when cooking outdoors.}\\[0.08cm]
\textbf{incomprehensible} & adj. &  impossible to understand :not comprehensible \\
 & & \textit{I found his behavior utterly incomprehensible.}\\[0.08cm]
\textbf{deter} & v. &  to cause (someone) to decide not to do something \\
 & & \textit{Some potential buyers will be deterred by the price.}\\[0.08cm]
\textbf{luncheon} & n. &  a usually formal lunch that occurs as part of a meeting or for entertaining a guest \\
 & & \textit{a company luncheon}\\[0.08cm]
\textbf{plunge} & v. &  to fall or jump suddenly from a high place \\
 & & \textit{Her car plunged off a bridge.}\\[0.08cm]
\textbf{sensual} & adj. &  relating to, devoted to, or producing physical or sexual pleasure \\
 & & \textit{sensual desires/pursuits/excesses}\\[0.08cm]
\textbf{traverse} & v. &  to move across (an area) \\
 & & \textit{The candidates traversed the state throughout the campaign.}\\[0.08cm]
\textbf{quartet} & n. &  a group of four singers or musicians who perform together \\
 & & \textit{He is a member of a jazz quartet.}\\[0.08cm]
\textbf{stray} & v. &  to go in a direction that is away from a group or from the place where you should be \\
 & & \textit{Two cows strayed [=wandered] into the woods.}\\[0.08cm]
\textbf{hue} & n. &  a color or a shade of a color \\
 & & \textit{We decorated the room in hues of blue and green.}\\[0.08cm]
\textbf{vanish} & v. &  to disappear entirely without a clear explanation \\
 & & \textit{My keys mysteriously vanished.}\\[0.08cm]
\textbf{revive} & v. &  to make (someone or something) strong, healthy, or active again \\
 & & \textit{The doctors were trying to revive the patient. [=to make the unconscious patient conscious again]}\\[0.08cm]
\textbf{invade} & v. &  to enter (a place, such as a foreign country) in order to take control by military force \\
 & & \textit{invade a country}\\[0.08cm]
\textbf{pilgrim} & n. &  someone who travels to a holy place \\
 & & \textit{Thousands of Muslim pilgrims traveled to Mecca.}\\[0.08cm]
\textbf{momentary} & adj. &  lasting a very short time :lasting only a moment \\
 & & \textit{There was a momentary [=brief] pause between songs.}\\[0.08cm]
\textbf{whistle} & v. &  to make a high sound by blowing air through your lips or teeth \\
 & & \textit{He was whistling as he walked down the street.}\\[0.08cm]
\textbf{signify} & v. &  to be a sign of (something) :to mean (something) \\
 & & \textit{Black clothing signifies mourning.}\\[0.08cm]
\textbf{surround} & v. &  to be on every side of (someone or something) \\
 & & \textit{A wall surrounds the old city.}\\[0.08cm]
\textbf{luminous} & adj. &  producing or seeming to produce light :shining \\
 & & \textit{luminous stars/galaxies}\\[0.08cm]
\textbf{scatter} & v. &  to cause (things or people) to separate and go in different directions \\
 & & \textit{The wind scattered the pile of leaves.}\\[0.08cm]
\textbf{recollection} & n. &  the act of remembering something or the ability to remember something \\
 & & \textit{Her recollection of the accident is very different from mine.}\\[0.08cm]
\textbf{flute} & n. &  a musical instrument that is shaped like a thin pipe and that is played by blowing across a hole near one end \\[0.08cm]
\textbf{radiant} & adj. &  having or showing an attractive quality of happiness, love, health, etc. \\
 & & \textit{a radiant smile}\\[0.08cm]
\textbf{palate} & n. &  the top part of the inside of your mouth :the roof of your mouth \\
 & & \textit{The restaurant serves Korean food adapted for the American palate.}\\[0.08cm]
\textbf{bury} & v. &  to put (a dead person or animal) in a grave \\
 & & \textit{He was buried with full military honors.}\\[0.08cm]
\textbf{exquisite} & adj. &  finely done or made \\
 & & \textit{exquisite workmanship}\\[0.08cm]
\textbf{stare} & v. &  to look at someone or something for a long time often with your eyes wide open \\
 & & \textit{She was staring straight ahead. = Her eyes were staring straight ahead.}\\[0.08cm]
\textbf{porcelain} & n. &  a hard, white substance that is very delicate and that is made by baking clay \\
 & & \textit{The bowl is made of/from porcelain.}\\[0.08cm]
\textbf{captive} & adj. &  captured and kept in a prison, cage, etc. \\
 & & \textit{The captive soldiers planned their escape.}\\[0.08cm]
\textbf{fragile} & adj. &  easily broken or damaged \\
 & & \textit{the flower's fragile petals}\\[0.08cm]
\textbf{avail} & v. &  to be useful or helpful to (someone or something) \\
 & & \textit{Our best efforts availed [=gained] us nothing.}\\[0.08cm]
\textbf{futile} & adj. &  having no result or effect :pointless or useless \\
 & & \textit{All our efforts proved futile.}\\[0.08cm]
\textbf{compel} & v. &  to force (someone) to do something \\
 & & \textit{Illness compelled him to stay in bed.}\\[0.08cm]
\textbf{pyramid} & n. &  a very large structure built especially in ancient Egypt that has a square base and four triangular sides which form a point at the top \\
 & & \textit{the ancient pyramids of Egypt}\\[0.08cm]
\textbf{scenery} & n. &  the walls, furniture, trees, etc., that are used on a stage during a play or other performance to show where the action is taking place \\
 & & \textit{She designed the scenery for the play.}\\[0.08cm]
\textbf{morrow} & n. &  morning \\
 & & \textit{äóìGood-night, good-night! parting is such sweet sorrow / That I shall say good-night till it be morrow.äóù }\\[0.08cm]
\textbf{dwell} & v. &  to live in a particular place \\
 & & \textit{a cave where bats dwell}\\[0.08cm]
\textbf{tray} & n. &  a thin, flat, and often rectangular piece of plastic, metal, wood, etc., that has a low rim and that is used for carrying things \\
 & & \textit{She carried the tray of food to our table.}\\[0.08cm]
\textbf{dip} & v. &  to put (something) into a liquid and pull it out again quickly usually + in or into \\
 & & \textit{Lightly dip the paintbrush into the paint.}\\[0.08cm]
\textbf{rivalry} & n. &  a state or situation in which people or groups are competing with each other \\
 & & \textit{There is a bitter/friendly rivalry between the two groups.}\\[0.08cm]
\textbf{melt} & v. &  to change or to cause (something) to change from a solid to a liquid usually because of heat \\
 & & \textit{The butter melted in the frying pan.}\\[0.08cm]
\textbf{weary} & adj. &  lacking strength, energy, or freshness because of a need for rest or sleep :tired \\
 & & \textit{I need to rest my weary eyes.}\\[0.08cm]
\textbf{comprise} & v. &  to be made up of (something) :to include or consist of (something) \\
 & & \textit{Each army division comprised 4,500 troops.}\\[0.08cm]
\textbf{amid} & preposition &  in or into the middle of (something) \\
 & & \textit{It was hard to hear amid all the cheering.}\\[0.08cm]
\textbf{whence} & adv. &  from where \\
 & & \textit{They returned to the land whence they came.}\\[0.08cm]
\textbf{endure} & v. &  to continue to exist in the same state or condition \\
 & & \textit{This tradition has endured [=lasted] for centuries.}\\[0.08cm]
\end{longtable}
\end{document}
