\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage[margin=1in]{geometry}

\title{Vocabulary in \textit{Under the Influence}}
\author{Compiled by AcadeMe for the Homer Project}
\date{March 2016}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle
\begin{longtable}{llp{11cm}}
\textbf{heedless} & adj. &  not paying careful attention \\
 & & \textit{They remain heedless of their own safety.}\\[0.08cm]
\textbf{rumple} & v. &  to make (something) messy or wrinkled \\
 & & \textit{He rumpled her hair affectionately.}\\[0.08cm]
\textbf{swelter} & v. &  to be very hot and uncomfortable \\
 & & \textit{We were sweltering in the summer heat.}\\[0.08cm]
\textbf{flophouse} & n. &  a very inexpensive hotel for poor people who do not have anywhere else to live \\
 & & \textit{a crowded flophouse}\\[0.08cm]
\textbf{fluster} & v. &  to make (someone) nervous and confused \\
 & & \textit{The interruption flustered the speaker.}\\[0.08cm]
\textbf{smolder} & v. &  to burn slowly without flames but usually with smoke \\
 & & \textit{The remains of the campfire smoldered.}\\[0.08cm]
\textbf{wino} & n. &  a person who has no place to live and who is often drunk\\[0.08cm]
\textbf{sneaker} & n. &  a shoe with a rubber sole that is designed for people to wear while running, playing sports, etc. \\[0.08cm]
\textbf{ratty} & adj. &  in very bad condition \\
 & & \textit{a ratty [=shabby] old sweater}\\[0.08cm]
\textbf{bewilder} & v. &  to confuse (someone) very much \\
 & & \textit{His decision bewildered [=puzzled, perplexed] her.}\\[0.08cm]
\textbf{slink} & v. &  to move in a way that does not attract attention especially because you are embarrassed, afraid, or doing something wrong \\
 & & \textit{I thought I saw someone slinking [=sneaking] around outside.}\\[0.08cm]
\textbf{drivel} & v. &  to talk in a very foolish or silly way \\
 & & \textit{What is he driveling about now?}\\[0.08cm]
\textbf{cower} & v. &  to move back or bend your body down because you are afraid \\
 & & \textit{They cowered at the sight of the gun.}\\[0.08cm]
\textbf{redden} & v. &  to make something red or to become red \\
 & & \textit{First-degree burns redden the skin.}\\[0.08cm]
\textbf{shelve} & v. &  to put (something) on a shelf \\
 & & \textit{He shelved the books/products.}\\[0.08cm]
\textbf{riddance} & n. &  sed to say that you are glad that someone is leaving or that something has gone \\
 & & \textit{‚ÄúDid you hear? Jack is leaving for a new job.‚Äù ‚ÄúWell, good riddance (to him)! We'll be better off without him!‚Äù}\\[0.08cm]
\textbf{metamorphose} & v. &  to change in an important and obvious way into something that is very different :to undergo metamorphosis usually + into \\
 & & \textit{This once-small company has metamorphosed into an industrial giant.}\\[0.08cm]
\textbf{swig} & v. &  to drink (something) quickly and in large amounts :to swallow a lot of (a drink) \\
 & & \textit{She was swigging [=gulping] water from a bottle after her workout.}\\[0.08cm]
\textbf{stun} & v. &  to surprise or upset (someone) very much \\
 & & \textit{a theft that stunned [=shocked] the art world}\\[0.08cm]
\textbf{werewolf} & n. &  a person who sometimes changes into a wolf especially when the moon is full\\[0.08cm]
\textbf{rummage} & v. &  to search for something especially by moving and looking through the contents of a place \\
 & & \textit{He rummaged through the attic for his baseball card collection.}\\[0.08cm]
\textbf{peddle} & v. &  to sell (something) usually in small amounts and often by traveling to different places \\
 & & \textit{They peddled fruits and vegetables out of their truck on the side of the road.}\\[0.08cm]
\textbf{minefield} & n. &  an area of land or water that contains mines (sense 2)\\
 & & \textit{This issue is a political minefield.}\\[0.08cm]
\textbf{incriminate} & v. &  to cause (someone) to appear guilty of or responsible for something (such as a crime) \\
 & & \textit{Material found at the crime scene incriminates the defendant.}\\[0.08cm]
\textbf{gnaw} & v. &  to bite or chew (something) repeatedly \\
 & & \textit{The dog was gnawing a bone.}\\[0.08cm]
\textbf{tipsy} & adj. &  unsteady or foolish from drinking :slightly drunk \\
 & & \textit{I got a little tipsy at the party last night.}\\[0.08cm]
\textbf{squander} & v. &  to use (something) in a foolish or wasteful way \\
 & & \textit{She squandered her inheritance/allowance.}\\[0.08cm]
\textbf{terrify} & v. &  to cause (someone) to be extremely afraid :to frighten (someone) very much \\
 & & \textit{Big dogs terrify me.}\\[0.08cm]
\textbf{prowl} & v. &  to move quietly through an area while hunting \\
 & & \textit{a tiger prowling in the jungle}\\[0.08cm]
\textbf{swagger} & v. &  to walk in a very confident way :to walk with a swagger \\
 & & \textit{He swaggered [=strutted] into the shop like he owned the place.}\\[0.08cm]
\textbf{telltale} & adj. &  indicating that something exists or has occurred \\
 & & \textit{The sauce had the telltale odor of garlic.}\\[0.08cm]
\textbf{balk} & v. &  to suddenly show that you do not want to do something :to refuse to do what someone else wants you to do \\
 & & \textit{If this witness balks [=refuses to cooperate in court], our lawyers will not have enough evidence to win the case.}\\[0.08cm]
\textbf{smuggle} & v. &  to move (someone or something) from one country into another illegally and secretly \\
 & & \textit{He was arrested for smuggling drugs into the country.}\\[0.08cm]
\textbf{crackle} & v. &  to make a series of short, sharp noises \\
 & & \textit{The logs crackled in the fire.}\\[0.08cm]
\textbf{binge} & v. &  to eat, drink, etc., too much in a short period of time :to go on a binge often + on \\
 & & \textit{He binges on beer now and then.}\\[0.08cm]
\textbf{grisly} & adj. &  causing horror or fear :very shocking \\
 & & \textit{a grisly [=gruesome] murder}\\[0.08cm]
\textbf{throb} & n. &  a feeling of pain in a series of regular beats\\
 & & \textit{}\\[0.08cm]
\textbf{engulf} & v. &  to flow over and cover (someone or something) \\
 & & \textit{The valley was engulfed in a thick fog.}\\[0.08cm]
\textbf{lurch} & v. &  to make a sudden sideways or forward motion \\
 & & \textit{The boat lurched in the rough seas.}\\[0.08cm]
\textbf{dazzle} & v. &  to cause (someone) to be unable to see for a short time \\
 & & \textit{He was dazzled [=blinded] by the camera flash.}\\[0.08cm]
\textbf{coax} & v. &  to influence or persuade (a person or animal) to do something by talking in a gentle and friendly way \\
 & & \textit{It took almost an hour to coax the cat down from the tree.}\\[0.08cm]
\textbf{waver} & v. &  to go back and forth between choices or opinions :to be uncertain about what you think about something or someone \\
 & & \textit{people who are still wavering between the two candidates}\\[0.08cm]
\textbf{seep} & v. &  to flow or pass slowly through small openings in something \\
 & & \textit{Blood was seeping through the bandage.}\\[0.08cm]
\textbf{surly} & adj. &  rude and unfriendly \\
 & & \textit{surly customers}\\[0.08cm]
\textbf{huddle} & v. &  to come close together in a group \\
 & & \textit{People were huddling (together) in doorways to get out of the rain.}\\[0.08cm]
\textbf{sweaty} & adj. &  causing you to sweat \\
 & & \textit{sweaty work}\\[0.08cm]
\textbf{flounder} & v. &  to move in an awkward way with a lot of difficulty and effort :struggle \\
 & & \textit{The horses were floundering through the deep snow.}\\[0.08cm]
\textbf{stagger} & v. &  to move or cause (someone) to move unsteadily from side to side \\
 & & \textit{The drunk staggered away/off.}\\[0.08cm]
\textbf{scold} & v. &  to speak in an angry or critical way to (someone who has done something wrong) \\
 & & \textit{He scolded [=reprimanded] the children for making a mess.}\\[0.08cm]
\textbf{growl} & v. &  to make a deep threatening sound \\
 & & \textit{I could hear a dog growling behind me.}\\[0.08cm]
\textbf{bruise} & v. &  to cause a bruise on (part of a person's body, a piece of fruit, etc.) \\
 & & \textit{She bruised her knee when she fell.}\\[0.08cm]
\textbf{thump} & v. &  to hit or beat something or someone and make a loud, deep sound \\
 & & \textit{Someone was thumping [=pounding] loudly on the door.}\\[0.08cm]
\textbf{grunt} & v. &  to make a short, low sound :to make a grunt \\
 & & \textit{The workers were grunting with effort as they lifted the heavy furniture.}\\[0.08cm]
\textbf{sniff} & v. &  to take air into your nose in short breaths that are loud enough to be heard \\
 & & \textit{She sniffed and wiped her nose with a tissue.}\\[0.08cm]
\textbf{furtive} & adj. &  done in a quiet and secret way to avoid being noticed \\
 & & \textit{He cast a furtive glance in our direction.}\\[0.08cm]
\textbf{crunch} & v. &  to make the loud sound of something being crushed \\
 & & \textit{The snow crunched underfoot.}\\[0.08cm]
\textbf{jovial} & adj. &  full of happiness and joy :cheerful \\
 & & \textit{The audience was in a jovial mood.}\\[0.08cm]
\textbf{hurl} & v. &  to throw (something) with force \\
 & & \textit{Someone hurled a rock through the window.}\\[0.08cm]
\textbf{disappoint} & v. &  to make (someone) unhappy by not being as good as expected or by not doing something that was hoped for or expected \\
 & & \textit{The team disappointed its fans.}\\[0.08cm]
\textbf{stalwart} & adj. &  very loyal and dedicated \\
 & & \textit{stalwart fans/supporters}\\[0.08cm]
\textbf{dutiful} & adj. &  doing what is expected of you \\
 & & \textit{a dutiful servant/daughter/father}\\[0.08cm]
\textbf{distraught} & adj. &  very upset :so upset that you are not able to think clearly or behave normally \\
 & & \textit{Distraught relatives are waiting for news of the missing children.}\\[0.08cm]
\textbf{quiver} & v. &  to shake because of fear, cold, nervousness, etc. :tremble \\
 & & \textit{Her lips quivered when she heard the bad news.}\\[0.08cm]
\textbf{twitch} & v. &  to make a slight, sudden movement that is not controlled or deliberate \\
 & & \textit{His left leg twitched.}\\[0.08cm]
\textbf{posse} & n. &  a group of people who were gathered together by a sheriff in the past to help search for a criminal \\
 & & \textit{The sheriff and his posse rode out to look for the bandits.}\\[0.08cm]
\textbf{blink} & v. &  to close and then open your eyes very quickly \\
 & & \textit{She blinked when the light flashed.}\\[0.08cm]
\textbf{phony} & adj. &  not true, real, or genuine :intended to make someone think something that is not true \\
 & & \textit{He gave a phony name to the police. = The name he gave the police was phony.}\\[0.08cm]
\textbf{stupor} & n. &  a condition in which someone is not able to think normally because of being drunk, drugged, tired, etc. \\
 & & \textit{He fell into a drunken stupor.}\\[0.08cm]
\textbf{taint} & v. &  to hurt or damage the good condition of (something) often used as (be) tainted \\
 & & \textit{The reputation of the university has been tainted [=blemished, marred] by athletic scandals.}\\[0.08cm]
\textbf{sob} & v. &  to cry noisily while taking in short, sudden breaths \\
 & & \textit{He began to sob uncontrollably.}\\[0.08cm]
\textbf{chore} & n. &  a small job that is done regularly \\
 & & \textit{The children were each assigned different household chores.}\\[0.08cm]
\textbf{heave} & v. &  to lift or pull (something) with effort \\
 & & \textit{We heaved the box (up) onto the table.}\\[0.08cm]
\textbf{nag} & v. &  to annoy (someone) by often complaining about his or her behavior, appearance, etc. \\
 & & \textit{My wife nags me about my busy work schedule.}\\[0.08cm]
\textbf{banish} & v. &  to force (someone) to leave a country as punishment :exile \\
 & & \textit{He was banished for life.}\\[0.08cm]
\textbf{umpire} & n. &  an official who watches a game or match closely to enforce the rules; a referee\\
 & & \textit{}\\[0.08cm]
\textbf{pang} & n. &  a sudden, strong feeling of physical or emotional pain \\
 & & \textit{hunger pangs}\\[0.08cm]
\textbf{oversee} & v. &  to watch and direct (an activity, a group of workers, etc.) in order to be sure that a job is done correctly :supervise \\
 & & \textit{He was hired to oversee design and construction of the new facility.}\\[0.08cm]
\textbf{iniquity} & n. &  the quality of being unfair or evil \\
 & & \textit{a system plagued by corruption and iniquity [=injustice]}\\[0.08cm]
\textbf{forsake} & v. &  to give up or leave (someone or something) entirely \\
 & & \textit{All my friends have forsaken [=abandoned] me.}\\[0.08cm]
\textbf{postcard} & n. &  a card on which a message may be sent by mail without an envelope and that often has a picture on one side \\[0.08cm]
\textbf{budge} & v. &  to move slightly usually used in negative statements \\
 & & \textit{Their horses refused to budge.}\\[0.08cm]
\textbf{brew} & v. &  to make (beer, ale, etc.) \\
 & & \textit{They brew the beer on the premises.}\\[0.08cm]
\textbf{devour} & v. &  to quickly eat all of (something) especially in a way that shows that you are very hungry \\
 & & \textit{He devoured everything on his plate.}\\[0.08cm]
\textbf{gasp} & v. &  to breathe in suddenly and loudly with your mouth open because of surprise, shock, or pain \\
 & & \textit{Mom gasped in/with surprise at the sight of my sister's new haircut.}\\[0.08cm]
\textbf{sneak} & v. &  to move quietly and secretly in order to avoid being noticed \\
 & & \textit{They tried to sneak into the movie without paying.}\\[0.08cm]
\textbf{stoop} & v. &  to bend down or over \\
 & & \textit{She stooped down to hug the child.}\\[0.08cm]
\textbf{scourge} & v. &  to cause a lot of trouble or suffering for (someone or something) \\
 & & \textit{a neighborhood scourged by crime}\\[0.08cm]
\textbf{clump} & v. &  to form a mass or clump \\
 & & \textit{The virus causes the cells to clump (together).}\\[0.08cm]
\textbf{frenzied} & adj. &  very excited or upset \\
 & & \textit{frenzied dancing}\\[0.08cm]
\textbf{snout} & n. &  the long nose of some animals (such as pigs) \\
 & & \textit{The dog raised his snout and sniffed.}\\[0.08cm]
\textbf{grieve} & v. &  to cause (someone) to feel sad or unhappy \\
 & & \textit{It grieves me to see my brother struggling like this.}\\[0.08cm]
\textbf{sling} & v. &  to throw (something) with a forceful sweeping motion \\
 & & \textit{She slung the bag over her shoulder.}\\[0.08cm]
\textbf{tumble} & v. &  to fall down suddenly and quickly \\
 & & \textit{He tripped and tumbled to the ground.}\\[0.08cm]
\textbf{errand} & n. &  a short journey that you take to do or get something \\
 & & \textit{He was sent out on an urgent errand.}\\[0.08cm]
\textbf{wrench} & v. &  to twist and pull with a sudden violent motion \\
 & & \textit{I tried to wrench free from his grip.}\\[0.08cm]
\textbf{camouflage} & v. &  to hide (something) by covering it up or making it harder to see \\
 & & \textit{The swimming pool was camouflaged [=hidden] by a hedge.}\\[0.08cm]
\textbf{blunder} & v. &  to move in an awkward or confused way \\
 & & \textit{We blundered along through the woods until we finally found the trail.}\\[0.08cm]
\textbf{unsteady} & adj. &  not steady: such as\\
 & & \textit{The stool/ladder is unsteady.}\\[0.08cm]
\textbf{bump} & v. &  to hit (something, such as part of your body) against an object in a sudden and forceful way \\
 & & \textit{I have a bruise from where I bumped my head.}\\[0.08cm]
\textbf{lash} & v. &  to hit (a person or animal) with a whip, stick, or something similar \\
 & & \textit{The sailor was lashed for disobeying the captain.}\\[0.08cm]
\textbf{washer} & n. &  a thin, flat ring that is made of metal, plastic, or rubber and that is used to make something (such as a bolt) fit tightly or to prevent rubbing \\
 & & \textit{the clothes washer}\\[0.08cm]
\textbf{stab} & v. &  to wound (someone or something) with a pointed weapon (such as a knife) \\
 & & \textit{He stabbed her with a dagger.}\\[0.08cm]
\textbf{lunatic} & adj. &  designed for insane people \\
 & & \textit{a lunatic asylum}\\[0.08cm]
\textbf{wavy} & adj. &  having the curving shape of a wave or of many waves \\
 & & \textit{She has wavy blond hair.}\\[0.08cm]
\textbf{distract} & v. &  to cause (someone) to stop thinking about or paying attention to someone or something and to think about or pay attention to someone or something else instead \\
 & & \textit{You sneak into his room while I distract him.}\\[0.08cm]
\textbf{toad} & n. &  a small animal that looks like a frog but has dry skin and lives on land \\
 & & \textit{He's such a mean little toad.}\\[0.08cm]
\textbf{driveway} & n. &  a short private road from a street to a house or other building where cars can usually be parked \\
 & & \textit{A long driveway led to the mansion.}\\[0.08cm]
\textbf{boxer} & n. &  someone who participates in the sport of boxing\\[0.08cm]
\textbf{flicker} & v. &  to burn or glow in an unsteady way :to produce an unsteady light \\
 & & \textit{A TV was flickering in the background.}\\[0.08cm]
\textbf{addict} & n. &  a person who is not able to stop taking drugs :a person who is addicted to drugs \\
 & & \textit{The clinic provides counseling for (drug) addicts.}\\[0.08cm]
\textbf{linger} & v. &  to stay somewhere beyond the usual or expected time \\
 & & \textit{The tourists didn't linger very long.}\\[0.08cm]
\textbf{jerk} & v. &  to push, pull, or twist (something) with a quick movement \\
 & & \textit{I jerked the door open.}\\[0.08cm]
\textbf{dizzy} & adj. &  feeling that you are turning around in circles and are going to fall even though you are standing still \\
 & & \textit{The children were dizzy after spinning in circles.}\\[0.08cm]
\textbf{yell} & v. &  to say (something) very loudly especially because you are angry, surprised, or are trying to get someone's attention \\
 & & \textit{We saw people yelling for help.}\\[0.08cm]
\textbf{haunt} & v. &  to visit or live in (a place) \\
 & & \textit{Spirits haunted the house.}\\[0.08cm]
\textbf{smash} & v. &  to break (something) into many pieces :to shatter or destroy (something) \\
 & & \textit{He smashed the vase with a hammer.}\\[0.08cm]
\textbf{nap} & v. &  to sleep for a short period of time especially during the day \\
 & & \textit{He's napping [=dozing] on the couch.}\\[0.08cm]
\textbf{gleam} & v. &  to shine brightly \\
 & & \textit{The sun gleamed on the water.}\\[0.08cm]
\textbf{slump} & v. &  to sit or fall down suddenly and heavily \\
 & & \textit{She fainted and slumped to the floor.}\\[0.08cm]
\textbf{tremor} & n. &  a shaking movement of the ground before or after an earthquake \\
 & & \textit{Small tremors were still being felt several days after the earthquake.}\\[0.08cm]
\textbf{corrosive} & adj. &  causing corrosion: such as\\
 & & \textit{highly corrosive chemicals/gases/liquids}\\[0.08cm]
\textbf{delirium} & n. &  a mental state in which you are confused and not able to think or speak clearly usually because of fever or some other illness \\
 & & \textit{In her delirium, nothing she said made any sense.}\\[0.08cm]
\textbf{undo} & v. &  to open or release (something) :to unfasten or loosen (something) \\
 & & \textit{undo a belt/button/zipper}\\[0.08cm]
\textbf{dart} & n. &  a small pointed missile that can be thrown\\
 & & \textit{a poisoned dart}\\[0.08cm]
\textbf{curl} & v. &  to twist or form (something) into a round or curved shape \\
 & & \textit{The boy curled [=wound] the spaghetti around his fork.}\\[0.08cm]
\textbf{tremble} & v. &  to shake slightly because you are afraid, nervous, excited, etc. \\
 & & \textit{His arms and legs began to tremble.}\\[0.08cm]
\textbf{starve} & v. &  to suffer or die from lack of food :to suffer extreme hunger \\
 & & \textit{Without food they would starve.}\\[0.08cm]
\textbf{burgundy} & geo. &  region of France\\[0.08cm]
\textbf{batter} & v. &  to hit (something or someone) forcefully many times in a way that causes much damage or injury \\
 & & \textit{Storms battered the shore.}\\[0.08cm]
\textbf{reassure} & v. &  to make (someone) feel less afraid, upset, or doubtful \\
 & & \textit{Experts reassured the public that the accident wouldn't happen again.}\\[0.08cm]
\textbf{erase} & v. &  to remove (something that has been recorded) from a tape (such as a videotape or audiotape) or a computer disk \\
 & & \textit{The recording can be erased and the tape used again.}\\[0.08cm]
\textbf{perilous} & adj. &  full of danger :dangerous \\
 & & \textit{a perilous journey across the mountains}\\[0.08cm]
\textbf{bunker} & n. &  an underground shelter, typically for use in wartime\\
 & & \textit{}\\[0.08cm]
\textbf{redeem} & v. &  to make (something that is bad, unpleasant, etc.) better or more acceptable \\
 & & \textit{The exciting ending partially redeems what is otherwise a very dull movie.}\\[0.08cm]
\textbf{ache} & v. &  to produce a dull continuous pain :to hurt in a way that is constant but not severe \\
 & & \textit{Her muscles were aching from shoveling snow.}\\[0.08cm]
\textbf{buddy} & v. &  to become friendly especially in order to get help or some advantage often + with \\
 & & \textit{New students are encouraged to buddy up with older students.}\\[0.08cm]
\textbf{rusty} & adj. &  covered with rust \\
 & & \textit{a rusty old car}\\[0.08cm]
\textbf{blaze} & v. &  to burn very brightly and intensely \\
 & & \textit{A fire blazed in the stove.}\\[0.08cm]
\textbf{tug} & v. &  to pull something with a quick, forceful movement \\
 & & \textit{I felt someone tugging on/at my sleeve.}\\[0.08cm]
\textbf{grind} & v. &  to crush or break (something) into very small pieces by rubbing it against a rough surface or using a special machine \\
 & & \textit{Grind (up) the coffee beans into a fine powder.}\\[0.08cm]
\textbf{relentless} & adj. &  continuing without becoming weaker, less severe, etc. \\
 & & \textit{Her relentless optimism held the team together.}\\[0.08cm]
\textbf{inhabit} & v. &  to live in (a place) :to have a home in (a place) \\
 & & \textit{Several hundred species of birds inhabit the island.}\\[0.08cm]
\textbf{desolate} & adj. &  lacking the people, plants, animals, etc., that make people feel welcome in a place \\
 & & \textit{a landscape as desolate [=barren, lifeless] as the moon}\\[0.08cm]
\textbf{summon} & v. &  to order (someone) to come to a place \\
 & & \textit{The queen summoned him back to the palace.}\\[0.08cm]
\textbf{arsenal} & n. &  a collection of weapons \\
 & & \textit{the nation's nuclear arsenal [=the nuclear weapons that the nation has]}\\[0.08cm]
\textbf{rag} & n. &  old or torn clothes\\
 & & \textit{The child is dressed in†rags.}\\[0.08cm]
\textbf{metamorphosis} & n. &  a major change in the appearance or character of someone or something \\
 & & \textit{We have watched her metamorphosis from a shy schoolgirl into a self-confident businesswoman.}\\[0.08cm]
\textbf{hop} & v. &  to move by a quick jump or series of jumps \\
 & & \textit{He hopped over the hot sand.}\\[0.08cm]
\textbf{uplift} & v. &  to make (someone) happy or hopeful \\
 & & \textit{music that uplifts the soul}\\[0.08cm]
\textbf{vintage} & adj. &  sed to describe a wine usually of high quality that was produced in a particular year which is identified on the bottle \\
 & & \textit{The restaurant has a fine selection of vintage wines.}\\[0.08cm]
\textbf{flare} & v. &  to shine or burn suddenly and briefly \\
 & & \textit{A match flared (up) in the darkness.}\\[0.08cm]
\textbf{trash} & v. &  to throw away (something) \\
 & & \textit{a computer program that trashes useless files}\\[0.08cm]
\textbf{forearm} & v. &  to arm in advance :prepare\\[0.08cm]
\textbf{vow} & v. &  to make a serious promise to do something or to behave in a certain way often followed by to + verb \\
 & & \textit{The mayor vowed to reduce crime.}\\[0.08cm]
\textbf{uphold} & v. &  to support or defend (something, such as a law) \\
 & & \textit{He took an oath to uphold the Constitution.}\\[0.08cm]
\textbf{swine} & n. &  pig \\
 & & \textit{methods of raising swine}\\[0.08cm]
\textbf{weep} & v. &  to cry because you are very sad or are feeling some other strong emotion \\
 & & \textit{He wept at the news of her death.}\\[0.08cm]
\textbf{nasty} & adj. &  very unpleasant to see, smell, taste, etc. \\
 & & \textit{She has a nasty habit of biting her fingernails.}\\[0.08cm]
\textbf{pinch} & v. &  to squeeze (someone's skin) between your thumb and finger often in a painful way \\
 & & \textit{My little brother is always trying to pinch me.}\\[0.08cm]
\textbf{shrink} & v. &  to become smaller in amount, size, or value \\
 & & \textit{The sweater shrank when it was washed.}\\[0.08cm]
\textbf{dump} & v. &  to put (something) somewhere in a quick and careless way \\
 & & \textit{You can dump the coats on the bed.}\\[0.08cm]
\textbf{tilt} & v. &  to lift or move (something) so that one side is higher than another side \\
 & & \textit{Tilt the glass as you pour in the beer.}\\[0.08cm]
\textbf{mechanic} & n. &  a person who repairs machines (such as car engines) and keeps them running properly \\
 & & \textit{an automotive mechanic}\\[0.08cm]
\textbf{crescent} & n. &  the shape of the visible part of the moon when it is less than half full \\
 & & \textit{the crescent moon}\\[0.08cm]
\textbf{statistic} & n. &  a number that represents a piece of information (such as information about how often something is done, how common something is, etc.) \\
 & & \textit{One statistic that stuck out is that 40 percent of those surveyed did not have college degrees.}\\[0.08cm]
\textbf{leak} & v. &  to let something (such as a liquid or gas) in or out through a hole in a surface \\
 & & \textit{The roof was leaking. [=rainwater was getting into the building through the roof]}\\[0.08cm]
\textbf{whiskey} & n. &  a strong alcoholic drink made from a grain (such as rye, corn, or barley) \\
 & & \textit{He ordered a whiskey and soda. [=whiskey mixed with soda water]}\\[0.08cm]
\textbf{scream} & v. &  to suddenly cry out in a loud and high voice because of pain, surprise, etc. \\
 & & \textit{She screamed when the door suddenly slammed shut.}\\[0.08cm]
\textbf{basketball} & n. &  a game in which two teams of five players bounce a ball and try to score points by throwing the ball through one of the raised nets at each end of a rectangular court \\
 & & \textit{She plays basketball.}\\[0.08cm]
\textbf{roar} & v. &  to make the loud sound of a wild animal (such as a lion) \\
 & & \textit{We heard a lion roar in the distance.}\\[0.08cm]
\textbf{sway} & v. &  to move slowly back and forth \\
 & & \textit{branches swaying in the breeze}\\[0.08cm]
\textbf{accusation} & n. &  a claim that someone has done something wrong or illegal :a charge that someone has committed a fault or crime \\
 & & \textit{Investigators have made/brought/leveled accusations of corruption against a group of former officials.}\\[0.08cm]
\textbf{fetch} & v. &  to go after and bring back (someone or something) \\
 & & \textit{Wait here while I fetch [=get] the doctor.}\\[0.08cm]
\textbf{cruise} & v. &  to travel on a boat or ship to a number of places as a vacation \\
 & & \textit{We cruised for a week down the Yangtze River.}\\[0.08cm]
\textbf{addiction} & n. &  a strong and harmful need to regularly have something (such as a drug) or do something (such as gamble) \\
 & & \textit{He has a drug addiction.}\\[0.08cm]
\textbf{perennial} & adj. &  living for several years or for many years :having a life cycle that is more than two years long \\
 & & \textit{a perennial plant}\\[0.08cm]
\textbf{disgust} & v. &  to cause (someone) to have a strong feeling of dislike for something especially because it has a very unpleasant appearance, taste, smell, etc. \\
 & & \textit{The greasy food they were serving disgusted [=repulsed] him.}\\[0.08cm]
\textbf{ditch} & v. &  to stop having or using (something you no longer want or need) :to get rid of (something) \\
 & & \textit{The thief ditched the purse in an alley.}\\[0.08cm]
\textbf{careless} & adj. &  not using care :not careful \\
 & & \textit{He is a careless worker.}\\[0.08cm]
\textbf{disguise} & v. &  to change the usual appearance, sound, taste, etc., of (someone or something) so that people will not recognize that person or thing \\
 & & \textit{He tried to disguise his voice on the phone but I could tell it was him.}\\[0.08cm]
\textbf{spy} & v. &  to try secretly to get information about a country, organization, etc. :to act as a spy \\
 & & \textit{They were accused of spying for a foreign government.}\\[0.08cm]
\textbf{announce} & v. &  to make (something) known in a public or formal way :to officially tell people about (something) \\
 & & \textit{The government announced a cut in taxes.}\\[0.08cm]
\textbf{whip} & v. &  to hit (a person or animal) with a whip or with something that is like a whip \\
 & & \textit{The sailor was whipped [=flogged] for disobeying orders.}\\[0.08cm]
\textbf{garage} & n. &  a building for housing a motor vehicle or vehicles\\
 & & \textit{she took her car to the garage}\\[0.08cm]
\textbf{lump} & n. &  a compact mass of a substance, especially one without a definite or regular shape\\
 & & \textit{there was a†lump of†ice floating in the milk}\\[0.08cm]
\textbf{mutation} & n. &  a change in the genes of a plant or animal that causes physical characteristics that are different from what is normal \\
 & & \textit{The cat's short tail is the result of mutation.}\\[0.08cm]
\textbf{futile} & adj. &  having no result or effect :pointless or useless \\
 & & \textit{All our efforts proved futile.}\\[0.08cm]
\textbf{swallow} & v. &  to take (something) into your stomach through your mouth and throat \\
 & & \textit{He swallowed the grape whole.}\\[0.08cm]
\textbf{consume} & v. &  to eat or drink (something) \\
 & & \textit{The dogs consume [=eat] a bag of dog food each week.}\\[0.08cm]
\textbf{clash} & v. &  to be in a situation in which you are fighting or disagreeing :to come into conflict with someone \\
 & & \textit{Police and protesters clashed yesterday.}\\[0.08cm]
\textbf{dread} & v. &  to fear something that will or might happen \\
 & & \textit{He can't swim and dreads going in the water.}\\[0.08cm]
\textbf{malaria} & n. &  a serious disease that causes chills and fever and that is passed from one person to another by the bite of mosquitoes\\[0.08cm]
\textbf{interrupt} & v. &  to ask questions or say things while another person is speaking :to do or say something that causes someone to stop speaking \\
 & & \textit{Please don't interrupt me (while I'm talking).}\\[0.08cm]
\textbf{sober} & adj. &  not drunk \\
 & & \textit{I'm driving, so I have to stay sober tonight.}\\[0.08cm]
\textbf{brutal} & adj. &  extremely cruel or harsh \\
 & & \textit{a brutal military dictatorship}\\[0.08cm]
\textbf{bliss} & n. &  complete happiness \\
 & & \textit{Their religion promises eternal bliss [=joy] in heaven.}\\[0.08cm]
\textbf{uneasy} & adj. &  worried or unhappy about something \\
 & & \textit{Rain made the crew uneasy.}\\[0.08cm]
\textbf{lid} & n. &  a cover on a box, can, jar, etc., that can be lifted or removed \\[0.08cm]
\textbf{conceal} & v. &  to hide (something or someone) from sight \\
 & & \textit{The sunglasses conceal her eyes.}\\[0.08cm]
\textbf{duck} & v. &  to lower your head or body suddenly to avoid being seen or hit \\
 & & \textit{The ceiling was so low I had to duck.}\\[0.08cm]
\textbf{threaten} & v. &  to say that you will harm someone or do something unpleasant or unwanted especially in order to make someone do what you want \\
 & & \textit{The mugger threatened him with a gun.}\\[0.08cm]
\textbf{atlas} & n. &  a book of maps \\
 & & \textit{a world atlas}\\[0.08cm]
\textbf{penny} & n. &  a coin or a unit of money equal to \\
 & & \textit{We got the car for just pennies. [=it didn't cost very much]}\\[0.08cm]
\textbf{barn} & n. &  a building on a farm that is used for storing grain and hay and for housing farm animals or equipment\\
 & & \textit{They live in a big barn of a house.}\\[0.08cm]
\textbf{miniature} & adj. &  very small :tiny \\
 & & \textit{a collection of miniature books}\\[0.08cm]
\textbf{cliff} & n. &  a high, steep surface of rock, earth, or ice \\
 & & \textit{Standing at the edge of the cliff, we watched the waves crash on the shore far below.}\\[0.08cm]
\textbf{compassion} & n. &  a feeling of wanting to help someone who is sick, hungry, in trouble, etc. \\
 & & \textit{He felt compassion for the lost child.}\\[0.08cm]
\textbf{pretend} & v. &  to act as if something is true when it is not true \\
 & & \textit{She pretended (that) she didn't care what other people said about her.}\\[0.08cm]
\textbf{supposedly} & adv. &  according to what someone has said or what is generally believed to be true or real \\
 & & \textit{These detergents are supposedly better for the environment.}\\[0.08cm]
\textbf{confess} & v. &  to admit that you did something wrong or illegal \\
 & & \textit{He confessed after being questioned for many hours.}\\[0.08cm]
\textbf{odds} & n. &  the possibility that something will happen :the chance that one thing will happen instead of a different thing \\
 & & \textit{She wanted to improve her odds [=chances] of winning.}\\[0.08cm]
\end{longtable}
\end{document}
