\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage[margin=1in]{geometry}

\title{Vocabulary in \textit{What is a Homosexual}}
\author{Compiled by AcadeMe for the Homer Project}
\date{March 2016}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle
\begin{longtable}{llp{11cm}}
\textbf{wonk} & adj. &  having or showing a lot of interest in and knowledge about the details of a particular subject :having the qualities of a wonk \\
 & & \textit{a wonky bureaucrat in the State Department}\\[0.08cm]
\textbf{traumatize} & v. &  to cause (someone) to become very upset in a way that often leads to serious emotional problems :to cause (someone) to suffer emotional trauma \\
 & & \textit{He was traumatized by the experience.}\\[0.08cm]
\textbf{marginalize} & v. &  to put or keep (someone) in a powerless or unimportant position within a society or group \\
 & & \textit{We are protesting policies that marginalize women. [=that do not allow women to have important or powerful positions in a society]}\\[0.08cm]
\textbf{netherworld} & n. &  the world of the dead :hell\\
 & & \textit{The book describes the author's journey into the netherworld of drug dealers.}\\[0.08cm]
\textbf{foible} & n. &  a minor fault in someone's character or behavior usually plural \\
 & & \textit{We all have our little foibles.}\\[0.08cm]
\textbf{attune} & v. &  to cause (a person, company, etc.) to have a better understanding of what is needed or wanted by a particular person or group usually + to \\
 & & \textit{It is important to attune the company to the needs of its customers.}\\[0.08cm]
\textbf{unlearn} & v. &  to forget and stop doing (something, such as a habit) in a deliberate way because it is bad or incorrect \\
 & & \textit{It is hard to unlearn bad habits.}\\[0.08cm]
\textbf{dignify} & v. &  to cause (something) to have more serious and important quality :to give dignity or importance to (something) \\
 & & \textit{She felt that formal clothing would help dignify the occasion.}\\[0.08cm]
\textbf{flaunt} & v. &  to show (something) in a very open way so that other people will notice \\
 & & \textit{She liked to flaunt her wealth by wearing furs and jewelry.}\\[0.08cm]
\textbf{terrify} & v. &  to cause (someone) to be extremely afraid :to frighten (someone) very much \\
 & & \textit{Big dogs terrify me.}\\[0.08cm]
\textbf{inhere} & v. &  to be a natural part of (someone or something) \\
 & & \textit{He believes that liberty inheres in [=(more commonly) is inherent in] humanity as a natural right.}\\[0.08cm]
\textbf{parliamentarian} & n. &  a member of a parliament\\[0.08cm]
\textbf{schoolwork} & n. &  work that is done in classes in a school or given to students to be done at home \\[0.08cm]
\textbf{slovenly} & adj. &  messy or untidy \\
 & & \textit{slovenly clothes}\\[0.08cm]
\textbf{discus} & n. &  a heavy disk (as of wood or plastic) that is thicker in the center than at the perimeter and that is hurled for distance as a track-and-field event\\[0.08cm]
\textbf{patronize} & v. &  to give money or support to (someone or something) \\
 & & \textit{The family patronizes the arts/symphony.}\\[0.08cm]
\textbf{mimesis} & n. &  imitation mimicry\\[0.08cm]
\textbf{mannerism} & n. &  a person's particular way of talking or moving \\
 & & \textit{The actor can mimic the President's mannerisms perfectly.}\\[0.08cm]
\textbf{quirk} & n. &  an unusual habit or way of behaving \\
 & & \textit{Everyone has their little quirks.}\\[0.08cm]
\textbf{dint} & n. &  because of (something) :by means of (something) \\
 & & \textit{They succeeded by dint of hard work.}\\[0.08cm]
\textbf{jock} & n. &  someone who is very involved in sports :athlete \\
 & & \textit{She was a jock in high school and led her basketball team to the state championship.}\\[0.08cm]
\textbf{promiscuous} & adj. &  having or involving many sexual partners \\
 & & \textit{a promiscuous man/woman}\\[0.08cm]
\textbf{otherness} & n. &  the quality of being different or unusual \\
 & & \textit{As an American growing up in Africa, I always felt a sense of otherness.}\\[0.08cm]
\textbf{lamentable} & adj. &  deserving to be criticized or regretted \\
 & & \textit{The region has a long and lamentable [=regrettable] history of ethnic fighting.}\\[0.08cm]
\textbf{brazen} & adj. &  acting or done in a very open and shocking way without shame or embarrassment \\
 & & \textit{He exhibited a brazen disregard for other people's feelings.}\\[0.08cm]
\textbf{stunt} & v. &  to stop (someone or something) from growing or developing \\
 & & \textit{Poor soil can stunt a plant's growth.}\\[0.08cm]
\textbf{anathema} & n. &  someone or something that is very strongly disliked usually + to \\
 & & \textit{ideas that are anathema to me [=ideas that I strongly dislike]}\\[0.08cm]
\textbf{banal} & adj. &  boring or ordinary :not interesting \\
 & & \textit{He made some banal remarks about the weather.}\\[0.08cm]
\textbf{veracity} & n. &  truth or accuracy \\
 & & \textit{We questioned the veracity of his statements.}\\[0.08cm]
\textbf{sameness} & n. &  the quality or state of being alike or of not changing \\
 & & \textit{the sameness of the two methods}\\[0.08cm]
\textbf{clothe} & v. &  to provide (someone) with clothes \\
 & & \textit{the cost of feeding and clothing your children}\\[0.08cm]
\textbf{trump} & v. &  to beat (another card) by playing a card from the suit that beats the other suits :to play a trump card to beat (another card) \\
 & & \textit{She trumped my ace to win the trick.}\\[0.08cm]
\textbf{embarrass} & v. &  to make (someone) feel confused and foolish in front of other people \\
 & & \textit{Unexpected laughter embarrassed the speaker.}\\[0.08cm]
\textbf{forlorn} & adj. &  sad and lonely \\
 & & \textit{a forlorn old widow}\\[0.08cm]
\textbf{inflection} & n. &  a rise or fall in the sound of a person's voice :a change in the pitch or tone of a person's voice \\
 & & \textit{She spoke with no inflection.}\\[0.08cm]
\textbf{subculture} & n. &  a group that has beliefs and behaviors that are different from the main groups within a culture or society \\
 & & \textit{a subculture of local painters/writers}\\[0.08cm]
\textbf{rebuke} & v. &  to speak in an angry and critical way to (someone) often + for \\
 & & \textit{She was rebuked [=reprimanded] for being late.}\\[0.08cm]
\textbf{locker} & n. &  a cupboard or cabinet that has a door which can be locked and that is used to store personal items (such as books, clothes, shoes, etc.) \\
 & & \textit{a school locker}\\[0.08cm]
\textbf{breathless} & adj. &  unable to take enough air into your lungs :breathing very hard because you are trying to get more air \\
 & & \textit{The workout left me breathless. [=(more commonly) out of breath]}\\[0.08cm]
\textbf{interchangeable} & adj. &  capable of being used in place of each other \\
 & & \textit{These words have similar meanings but they're not (freely) interchangeable (with each other).}\\[0.08cm]
\textbf{deceit} & n. &  dishonest behavior :behavior that is meant to fool or trick someone \\
 & & \textit{He achieved his goals through lies and (a web of) deceit. [=deception]}\\[0.08cm]
\textbf{shameful} & adj. &  very bad :bad enough to make someone ashamed \\
 & & \textit{There is no excuse for such shameful behavior.}\\[0.08cm]
\textbf{intensify} & v. &  to become stronger or more extreme :to become more intense \\
 & & \textit{We could hear the wind howling outside as the storm intensified.}\\[0.08cm]
\textbf{marvel} & v. &  to feel great surprise, wonder, or admiration \\
 & & \textit{The audience marveled at the magician's skill.}\\[0.08cm]
\textbf{upbringing} & n. &  the way a child is raised :the care and teaching given to a child by parents or other people usually singular \\
 & & \textit{My wife had a very sheltered upbringing.}\\[0.08cm]
\textbf{stereotype} & v. &  to believe unfairly that all people or things with a particular characteristic are the same \\
 & & \textit{It's not fair to stereotype a whole group of people based on one person you don't like.}\\[0.08cm]
\textbf{repressive} & adj. &  controlling people by force \\
 & & \textit{a repressive government}\\[0.08cm]
\textbf{wary} & adj. &  not having or showing complete trust in someone or something that could be dangerous or cause trouble \\
 & & \textit{The store owner kept a wary eye on him.}\\[0.08cm]
\textbf{predicament} & n. &  a difficult or unpleasant situation \\
 & & \textit{The governor has gotten himself into quite a predicament.}\\[0.08cm]
\textbf{heterosexual} & adj. &  sexually attracted to people of the opposite sex \\
 & & \textit{a heterosexual male}\\[0.08cm]
\textbf{divert} & v. &  to change the direction or use of (something) \\
 & & \textit{Police diverted traffic to a side street.}\\[0.08cm]
\textbf{obsession} & n. &  a state in which someone thinks about someone or something constantly or frequently especially in a way that is not normal \\
 & & \textit{He was fascinated by the actress and tracking her every move had become an obsession.}\\[0.08cm]
\textbf{doom} & v. &  to make (someone or something) certain to fail, suffer, die, etc. \\
 & & \textit{A criminal record will doom your chances of becoming a politician.}\\[0.08cm]
\textbf{trajectory} & n. &  the curved path along which something (such as a rocket) moves through the air or through space \\
 & & \textit{the trajectory of the missile}\\[0.08cm]
\textbf{wrap} & v. &  to cover (something) by winding or folding a piece of material around it \\
 & & \textit{They were busy wrapping presents late on Christmas Eve.}\\[0.08cm]
\textbf{retrospect} & n. &  when thinking about the past or something that happened in the past \\
 & & \textit{In retrospect, I made the right decision.}\\[0.08cm]
\textbf{crush} & v. &  to press or squeeze (something) so hard that it breaks or loses its shape \\
 & & \textit{Unfortunately some of the flowers got crushed when we were moving them.}\\[0.08cm]
\textbf{lesbian} & n. &  a woman who is sexually attracted to other women :a female homosexual \\
 & & \textit{lesbians and gay men}\\[0.08cm]
\textbf{closet} & adj. &  hiding the fact that you are a particular type of person \\
 & & \textit{She's a closet racist. [=she does not want people to know that she is a racist]}\\[0.08cm]
\textbf{surround} & v. &  to be on every side of (someone or something) \\
 & & \textit{A wall surrounds the old city.}\\[0.08cm]
\textbf{reflective} & adj. &  causing light, sound, or heat to move away :reflecting light, sound, or heat \\
 & & \textit{The material is highly reflective. [=it easily reflects light]}\\[0.08cm]
\textbf{unavoidable} & adj. &  not able to be prevented or avoided \\
 & & \textit{The accident was unavoidable.}\\[0.08cm]
\textbf{ethic} & adj. &  involving questions of right and wrong behavior :relating to ethics \\
 & & \textit{ethical [=moral] principles/standards}\\[0.08cm]
\textbf{cod} & abbreviation &  ash on delivery; collect on delivery used to indicate that payment must be made when something is delivered \\
 & & \textit{The merchandise was shipped C.O.D.}\\[0.08cm]
\textbf{tolerant} & adj. &  willing to accept feelings, habits, or beliefs that are different from your own \\
 & & \textit{a tolerant society/community}\\[0.08cm]
\textbf{disguise} & v. &  to change the usual appearance, sound, taste, etc., of (someone or something) so that people will not recognize that person or thing \\
 & & \textit{He tried to disguise his voice on the phone but I could tell it was him.}\\[0.08cm]
\textbf{manifold} & adj. &  many and various \\
 & & \textit{the country's manifold problems}\\[0.08cm]
\textbf{deception} & n. &  the act of making someone believe something that is not true :the act of deceiving someone \\
 & & \textit{She accuses the company of willful deception in its advertising.}\\[0.08cm]
\textbf{conclusive} & adj. &  showing that something is certainly true \\
 & & \textit{conclusive evidence/proof}\\[0.08cm]
\textbf{traumatic} & adj. &  causing someone to become very upset in a way that can lead to serious mental and emotional problems \\
 & & \textit{She had a traumatic childhood.}\\[0.08cm]
\textbf{envy} & v. &  to feel a desire to have what someone else has :to feel envy because of (someone or something) \\
 & & \textit{I envy you for your large group of friends.}\\[0.08cm]
\textbf{torture} & v. &  to cause (someone) to experience severe physical pain especially as a form of punishment or to force that person to do or say something \\
 & & \textit{The report revealed that prisoners had been repeatedly tortured.}\\[0.08cm]
\textbf{aspiration} & n. &  something that a person wants very much to achieve \\
 & & \textit{I've never had any aspiration to become famous. [=I've never wanted to become famous]}\\[0.08cm]
\textbf{homosexual} & adj. &  sexually attracted to people of the same sex \\
 & & \textit{a homosexual man}\\[0.08cm]
\textbf{suppress} & v. &  to end or stop (something) by force \\
 & & \textit{Political dissent was brutally suppressed.}\\[0.08cm]
\textbf{reinforce} & v. &  to strengthen (a group of people) with new supplies or more people \\
 & & \textit{The captain sent out another squad to reinforce the troops.}\\[0.08cm]
\textbf{journalism} & n. &  the activity or job of collecting, writing, and editing news stories for newspapers, magazines, television, or radio \\
 & & \textit{investigative/broadcast journalism}\\[0.08cm]
\textbf{amateur} & n. &  a person who does something (such as a sport or hobby) for pleasure and not as a job \\
 & & \textit{She played soccer as an amateur before turning professional.}\\[0.08cm]
\textbf{masculine} & adj. &  of, relating to, or suited to men or boys \\
 & & \textit{a masculine voice/perspective/name}\\[0.08cm]
\textbf{definitive} & adj. &  not able to be argued about or changed :final and settled \\
 & & \textit{We need a definitive answer to this question.}\\[0.08cm]
\textbf{prone} & adj. &  likely to do, have, or suffer from something usually + to \\
 & & \textit{They are prone to (making) errors/mistakes. = They are error-prone/mistake-prone. [=they make many errors/mistakes]}\\[0.08cm]
\textbf{arena} & n. &  a building for sports and other forms of entertainment that has a large central area surrounded by seats \\
 & & \textit{a basketball/hockey arena}\\[0.08cm]
\textbf{handful} & n. &  an amount that you can hold in your hand \\
 & & \textit{The children collected seashells by the handful.}\\[0.08cm]
\textbf{ridiculous} & adj. &  extremely silly or unreasonable \\
 & & \textit{She looks ridiculous in that outfit.}\\[0.08cm]
\textbf{substantive} & adj. &  important, real, or meaningful \\
 & & \textit{substantive issues/matters}\\[0.08cm]
\textbf{exploit} & v. &  to get value or use from (something) \\
 & & \textit{He has never fully exploited his talents.}\\[0.08cm]
\textbf{proximity} & n. &  the state of being near \\
 & & \textit{People are attracted to the area by the proximity [=nearness] of several beaches.}\\[0.08cm]
\textbf{odds} & n. &  the possibility that something will happen :the chance that one thing will happen instead of a different thing \\
 & & \textit{She wanted to improve her odds [=chances] of winning.}\\[0.08cm]
\end{longtable}
\end{document}
